%\input{bmamble.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2015/05/04/an-honest-resume-personal-statement/}{An Honest Resume Personal Statement}}
\addcontentsline{toc}{subsection}{An Honest Resume Personal Statement}


\noindent\emph{Posted: 05 May 2015 02:59:11}
\vspace{6pt}

\emph{While updating an online version of my resume a nagging web page
advised me to include a personal statement: apparently the personal
statement is my chance to stand out, make that all-important first
impression, and firmly affix my lips to succulent corporate ass.}

\emph{Being programmer oriented, the web page suggested I write about my
first computer. This is just conniving HR speak for, ``How old are you?'' HR
cannot directly ask so they'll probe circuitously. Sorry gals, (HR is a
female ghetto), I'm on to you. I am excellent actor and liar. I can play
your little game but I am no longer interested. Still your little page
made we wonder what my personal statement would be like if I was telling
the truth and not spinning like a millisecond pulsar. I think it would
look something like this:}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

I want to~solve problems: not create them. You would be surprised how
many software organizations cannot tell the difference.

Ask yourself:

\begin{enumerate}
\itemsep2pt\parskip0pt\parsep0pt
\item
  Does your organization think the orthodox application of trendy
  project management
  ``methodologies''\footnote{I loathe the word ``methodologies.'' The correct word is ``methods.''
  Wanton syllable inflation is a reliable bullshit tell.} %\hyperdef{}{fnref1}{}{\hyperref[fn1]{\textsuperscript{1}}}
  like agile is a substitute for real insight and work?
\item
  Do you bind yourself in SOX inspired straitjackets and wonder why
  programmer morale and productivity has plummeted?
\item
  Do you have an antiquated remote work policy and insist staff show up
  for periodic management brow beatings and pointless brain numbing
  meetings?
\item
  Are you wedded to standard software tools merely because they are
  standard?
\item
  Are you afraid of iconoclastic viewpoints and meekly seek a lowest
  common denominator consensus?
\item
  Finally, do you follow industry trends or set them?
\end{enumerate}

Perhaps my bad attitude shocks you.

``Who would hire this guy?'' you ask.

It's a fair question. I've had my fill of ``Software Theater.'' I will
no longer act like I agree with bad ideas just to get along. From now on
I am going to tell people what I really think, not what they yearn to
hear.

To work with me your organization must be:

\begin{enumerate}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Located somewhere I want to live to or have an enlightened
  21\textsuperscript{st} century remote work policy.
\end{enumerate}

I am tired of wasting my life in humdrum hellholes because that's where
an employer is located. This is inexcusable for 21\textsuperscript{st}
century software developers. If you haven't figured out how to manage
geographically dispersed remote workers your organization is hidebound,
myopic and doomed!

\begin{enumerate}
\setcounter{enumi}{1}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Have a positive attitude about novel approaches to problems and
  encourage programmer autonomy.
\end{enumerate}

I have often solved problems with nonstandard tools and techniques only
to be told to do it again using a standard tool. Sometimes this makes
sense but usually it's motivated by pure organizational fear.

``Oh my God we won't be able to find someone to support this!''

Or even worse, ``We'll have to learn something new!''

Companies make a big show about ``thinking outside the box'' while
huddling like bed wetting cowards in the corner of one.

\begin{enumerate}
\setcounter{enumi}{2}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Accept the simple fact that work is small part of life and stop trying
  to manage employees outside of the workplace.
\end{enumerate}

It's amazing what some companies think they can get away with! Would you
believe
\href{http://mashable.com/2012/04/08/employer-facebook-password}{asking
recruits for Facebook and Twitter passwords?} Don't try this with me; I
might punch you! Most companies know that asking for passwords crosses
all sorts of inappropriate boundaries but even more enlightened
organizations often have a ``velvet fist'' social media policy that
basically tells employees not to involve the company in their personal
jackassery. This is a reasonable request but it's usually seen as
bullying. Most will shut up: not me! Freedom of speech is fundamental
and absolute. Companies that try to silence employees should be ashamed
of themselves.

If you're still reading and think, \emph{I like the cut of this guy's
jib. We have enough kowtowing eunuchs on payroll: a few ballsy shitheads
may spruce this joint up.} I'd suggest you look over my attached resume,
peruse my~\href{https://github.com/bakerjd99}{public GitHub
repositories}, read my blog, browse my
\href{https://conceptcontrol.smugmug.com}{extensive photos}, and check
out what I'm
\href{https://www.goodreads.com/review/list/5664087-john?utf8=\%E2\%9C\%93\&shelf=read\&sort=date_read\&order=d}{reading}.
You'll get a pretty accurate sense of who I am, what turns my crank, how
I approach problems, and how I deal with difficulties. Unspoken social
conventions demand that we suppress ourselves to work. I will no longer
do this. \emph{I am what I am; I do what do; I will not change for you.}

%\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
%
%\begin{enumerate}
%\item
%  \hyperdef{}{fn1}{}
%
%  I loathe the word ``methodologies.'' The correct word is ``methods.''
%  Wanton syllable inflation is a reliable bullshit
%  tell.\hyperref[fnref1]{↩}
%\end{enumerate}



%\end{document}