%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2023/05/25/a-note-on-the-writers-strike/}{A Note on the Writer's Strike}}
\addcontentsline{toc}{subsection}{A Note on the Writer's Strike}


\noindent\emph{Posted: 25 May 2023 17:21:53}
\vspace{6pt}

For the last few weeks, the Hollywood
\href{https://parade.com/entertainment/2023-wga-writers-strike}{writers
have been on strike}. I won't bore you with the details. Like all
strikes it boils down to money. The writers feel they aren't getting
what's owed to them, and the production companies want to hold onto as
much sweet moola as possible. Normally I'm indifferent to strikes, but
in this case, I am urging both sides to fight to the death. The writers
shouldn't give up a single commie cent and the production companies
should drive the most rapacious bargain possible. If things go my way
both sides lose and the entire industry self-destructs.

I know what's lurking in your teeny tiny brain. How could I be so cruel?
How could I drool at the prospect of media creatures losing their silly
little jobs?

It's easy. The current entertainment industry is a garbage industry.
\emph{A garbage industry is one that we would be better off
without.}\footnote{Ironically the people that pick up your curbside trash are not running
  a \emph{garbage industry}. They are providing a much-needed service
  and when trash collectors go on strike, we all miss
  them.
}%\protect\hypertarget{fnref1}{\protect\hyperlink{fn1}{\textsuperscript{1}}}
Garbage industries are depressingly common in the modern world.
\emph{Facebook,} (now \emph{Meta}), is garbage. \emph{Twitter} is
garbage. \emph{TikTok, Instagram}, and all their wannabes are garbage.
Fast food restaurants are garbage. Cable TV is garbage. Cosmetics are
garbage. Vast swaths of the processed food and pharmaceutical industries
are garbage. Many insurance companies are garbage. The fashion industry
is garbage. The diet industry, (please people get some self-respect), is
a steaming pile of garbage. I could go on and on because we live in a
wasteland people and not the wholesome T. S. Eliot version.

Suppose the Hollywood writers and their employers go away, and we're
faced with a world without media company entertainment. How could we
possibly live in such a world? Easily. The crap Hollywood spews,
union-made, or not, is easily replaced by good books; we all have long
lists of \emph{actual classics} to read. And, if reading isn't your jam,
there's YouTube. None of my favorite Youtubers are affected by this
strike,
\href{https://www.youtube.com/c/SabineHossenfelder/videos}{Sabine
Hossenfelder},
\href{https://www.youtube.com/channel/UCYNbYGl89UUowy8oXkipC-Q}{Dr.
Becky},
\href{https://www.youtube.com/channel/UCZ4AMrDcNrfy3X6nsU8-rPg}{Economics
Explained},
\href{https://www.youtube.com/c/MicroVisualProofs}{Mathematical Visual
Proofs,} and many, many, more are still cranking out superb content that
outclasses the dumbed-down-drivel the \emph{Hollyweirdos} foist on us. I
observed many years ago that the best bloggers are better writers, and
cover more interesting topics, than mainstream journalists, and the same
holds for the best YouTubers. That small talented and dedicated
producers can do a better job than bloated self-satisfied billion-dollar
companies may be shocking but look at the work. To paraphrase Flaubert,
``The company is nothing, the product --- all.''

If you are left with any doubts, I'm enjoying this strike. It has driven
all the smug late-night clowns off the air; their minuscule minds cannot
function without scripts. On my own, I wouldn't waste a millisecond on
the likes of Colbert, Kimmel, Meyers, and others but my wife enjoys
their attempts at humor, so I'm occasionally exposed to their asinine
Youtubery\footnote{  Nobody of any consequence stays up to watch late-night anymore. That
  time is thankfully over.
} %\protect\hypertarget{fnref2}{\protect\hyperlink{fn2}{\textsuperscript{2}}}
while sitting with her in the evenings. Silence is a lovely substitute
for late-night. With luck, they will never come back.

%\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
%
%\begin{enumerate}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn1}{}}%
%  Ironically the people that pick up your curbside trash are not running
%  a \emph{garbage industry}. They are providing a much-needed service
%  and when trash collectors go on strike, we all miss
%  them.\protect\hyperlink{fnref1}{↩︎}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn2}{}}%
%  Nobody of any consequence stays up to watch late-night anymore. That
%  time is thankfully over.\protect\hyperlink{fnref2}{↩︎}
%\end{enumerate}



%\end{document}
 
