%\input{bmamble.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2013/01/02/argentina-or-australia/}{Argentina or Australia}}
\addcontentsline{toc}{subsection}{Argentina or Australia}


\noindent\emph{Posted: 03 Jan 2013 05:42:18}
\vspace{6pt}

We're planning a major trip for the fourth quarter of 2013. It's been
over a decade since my wife and I last sojourned beyond North America so
this year we're going to spend a few dollars, before the Obama economy
reduces them to useless paper, and see more of the world. Two countries
have long topped my must visit list: Argentina and Australia. I'm
attracted to each for different reasons. We would like to visit both but
resource constraints mandate one. So I thought I would ask you, dear
readers, to help us make up our minds.

In Australia's favor, it's a large English-speaking country inhabited
with unique flora and fauna. Who doesn't want to see many marauding
marsupials?\footnote{ Here in Missouri we often find dead opossums, members of the sole
  North American order of marsupials, on our
  highways.
} Visiting Australia would
let me tick off another continent leaving one, Antarctica, to visit. I
know getting around the country would be like a North American road trip
and culture shock would be limited or non-existent. From the outside
Australia seems like a warmer, drier and less
polite\footnote{Canadians are too polite. Assholes won't learn if you don't call them
  assholes.
} version of Canada sans Quebec.

Spanish-speaking Argentina presents a few more cultural barriers, but in
Argentina's favor, it has the
\href{http://www.aconcagua.com/about-aconcagua/location/}{highest
mountain} in both Americas, shares one of the
\href{http://www.worldwaterfalldatabase.com/waterfall/Iguazu-Cataratas-del-109/}{greatest
waterfalls} on Earth, sports a great new world city, Buenos Aires, and
is populated with people who have limited respect for their government.
Disdain for the ruling class: it's a sure sign of an \emph{enlightened
people.}

On the basis of current events this is~a no-brainer; Australia easily
wins. Australia, like Canada, is a relatively competent and safe
democratic state. But, on a darker note, and just like Canada, Australia
is overrun with prattling lefties on the government's payroll. I see no
serious ideological differences between the
\href{http://www.cbc.ca/}{CBC} and the
\href{http://www.abc.net.au/}{ABC}. Australia, like Canada, still
supports the anachronistic British crown, but in their favor, they're on
the republican edge and if
\href{http://www.spectator.co.uk/columnists/james-delingpole/6157403/is-prince-charles-illadvised-or-merely-idiotic/}{Chuck},
the idiot, becomes king they may finally cross over to the dark side.

Argentina's recent past is problematic. They provoked and lost a stupid
Falkland sheep pasture war. They alternate between clueless Peronista
cronies and
second-rate~\href{http://www.bbc.co.uk/news/world-latin-america-18731349}{fascists}.
You know~your government is pathetic when Madonna makes
\href{http://www.imdb.com/title/tt0116250/}{musicals} about it. The
current
\href{http://www.csmonitor.com/World/Americas/2012/1003/Argentina-Oil-nationalization-and-currency-controls-divide-a-nation}{Kirchner
government} is hopeless and is wrecking the country's finances at
Zimbabwean speed. This is all bad, but taking a contrarian tack,
Argentines have already
\href{http://www.efinancialnews.com/story/2011-07-25/history-of-debt-defaults-argentina-2001}{been
there done that}. When currency collapses and defaults are regular
events people plan for them. Argentines have much to teach the world
when it comes to ignoring, working around, and sabotaging the designs of
our delusional masters. They know their government is incompetent,
sometimes dangerous, and not be trusted --- especially with money. In
this regard they're light years ahead of
Americans.\footnote{
Don't worry, The One's inept regime is educating large numbers of
  Americans on the dangers of
  \href{http://www.usdebtclock.org/}{out-of-control} finances. Soon
  Americans will join more enlightened nationalities, like Mexicans, in
  their contempt for government.
} Such chaos would scare off
tourists in many parts of the world but nobody is raising red flags
about Argentina; it's not Gaza or even, post Arab spring, Egypt.

So where should we go? We promise to weigh any hints or suggestions you
leave. Click the following link for the first ever Analyze the Data not
the Drivel poll.

\href{http://polldaddy.com/poll/6805019/}{Should we visit Argentina or
Australia?}


%\end{document}