%\input{bmamble.tex}

\subsection*{\href{http://bakerjd99.wordpress.com/2014/04/14/blood-morons/}{Blood Morons}}
\addcontentsline{toc}{subsection}{Blood Morons}


\noindent\emph{Posted: 14 Apr 2014 16:39:03}
\vspace{6pt}

Here we go again; \emph{literal lunatics} are, for the zillionth time,
announcing the end of the world. What's going to do us in this time?
Would you believe the next four lunar eclipses? Starting tonight, an
unusual\emph{, but not rare,} sequence of four lunar eclipses begins.
Some
\href{http://www.nydailynews.com/news/national/televangelist-claims-blood-moons-sign-world-shaking-event-article-1.1754601}{religious
loons} are claiming this so-called \emph{eclipse tetrad} is a sign of
the end times. Oh, if it were only so. Imagine a world cleansed of
imbeciles! Unfortunately, as
\href{http://eclipse.gsfc.nasa.gov/OH/OH2014.html\#tetrads}{Fred
Espenak} notes on his highly regarded eclipse pages, there is nothing
unusual about this sequence of eclipses. In the last five thousand
years we've had 142 eclipse tetrads. That's about one world ending
every thirty-five years. Look around people; we're still here.

It astounds me that there is still a market for such nonsense.
Astrology, and that's all this blood moon rubbish is, has been
completely, totally, absolutely and utterly debunked. On this the
science really is settled! But, when have we ever let science get in the
way of a \href{http://fourbloodmoons.net/}{good marketing opportunity},
and world endings are well --- world ending --- sales opportunities.
Get your end times before they're gone! Running astronomical scams is
easy because large swaths of the public cannot reliably answer basic
questions like:
\href{http://www.npr.org/blogs/thetwo-way/2014/02/14/277058739/1-in-4-americans-think-the-sun-goes-around-the-earth-survey-says}{does
the Sun go around the Earth?} Maintaining such levels of ignorance must
be exhausting.

You might want to pull your head out of your blood moron ass long enough
to observe tonight's total lunar eclipse. It starts around midnight
\href{http://blog.realtimestl.com/2014/04/when-and-how-to-watch-the-lunar-eclipse-in-st-louis/}{here
in St. Louis} with totality commencing around 2:00 am. I'll be out
there, St. Louis weather permitting, shooting eclipse tracks. With
proper framing eclipse tracks make neat pictures. If what I have in mind
pans out it will constitute my next post.



%\end{document}