%\input{bmamble.tex}

\subsection*{\href{http://bakerjd99.wordpress.com/2012/12/27/books-to-ignore/}{Books to Ignore}}
\addcontentsline{toc}{subsection}{Books to Ignore}


\noindent\emph{Posted: 27 Dec 2012 23:31:03}
\vspace{6pt}

My superpower is indifference. Indifference is the soporific that lets
my inner beast nap in peace. Without it I would have long since turned
into a murdering psychopath, but I remain calm, rational, nearly
ethereal, as I proudly ignore the unhinged idiocy of my fellow human
beings. I prize my detachment, my don't-give-a-shit-ness, my lordly
disdain, and I work hard to maintain it. Today I'm sharing one of my,
how to resist pummeling the morons around you, secrets. Here it is:
\emph{don't read rubbish.}

Now, don't fire up your
\href{https://www.youtube.com/watch?v=ETJP1ElHTps}{book Barbie}; that's
not what I'm suggesting. I'm asking you to upgrade your standards and
scoot past toxic aisles in your favorite book store. Ignorable books are
legion and they're relatively easy to identify. The following rules have
served me well.

\begin{enumerate}
\item
  \textbf{Do not read biographies of living people.} There are few, if
  any, definitive biographies of the living for the simple reason that
  they're almost impossible to write without triggering crippling law
  suits. Historical figures, and their entire sycophantic bottom-feeding
  cohort, must~be long dead before anything approaching perspective is
  possible. So put down that
  \href{http://www.amazon.com/Prince-Wales-Biography-Jonathan-Dimbleby/dp/0688146155}{Prince
  of Wales} or, don't make me
  puke,~\href{http://www.barnesandnoble.com/w/ted-turner-michael-oconnor/1103045877?cm\_mmc=googlepla-\_-book-\_-q000000633-\_-9780313350429\&cm\_mmca2=pla\&ean=9780313350429\&isbn=9780313350429\&r=1}{Ted
  Turner}, biography. They're trash, worse than pornography, at least
  porn facilitates release.
\item
  \textbf{Do not read autobiographies.} Autobiographical fiction, and it
  always is, is akin to masturbating in public. Only one person is going
  to enjoy it. Everything I said about biographies goes double for
  autobiographies. We know you're misleading, omitting, embellishing,
  polishing, fabricating, composting and just plain lying. If you're one
  of the rare true worthies, say a
  \href{http://www.mathunion.org/general/prizes/fields/details/}{Fields
  Medalist}, a hard science Nobel winner, a Caesar, or a Mark Twain then
  go ahead and indulge yourself. Your scribbling's will show future
  generations that bullshit is the only human universal.
\item
  \textbf{Do not read hyphenated anything.} Only mediocre twaddle preens
  as black-history, feminist-politics, gay-literature,
  Indian-mathematics, lesbian-drama or aboriginal-stories; the good
  stuff is known as history, politics, literature, mathematics, drama
  and stories.
\item
  \textbf{Skip anything with ``New Age'' in its title, preamble,
  introduction, appendices or footnotes.} Virtually everything written
  about new age beliefs, medicine, philosophy and so on is complete and
  utter garbage. This dreck is for feeble, magical-thinking, childish
  minds. I genuinely pity the purveyors and swallowers of new-age bilge;
  they're sad silly people: come the zombie apocalypse the Deepak
  Copra's of the world are starters.
\item
  \textbf{Eschew political diatribes written solely to exploit current
  events.} The political diatribe, or insta-history, like
  autobiographical fiction, may let readers in the future relive our
  self-deceptions, but we don't live in the future. Most of these books
  emit a foul, \emph{cash in on my 15 minutes of fame}, stench. I weep
  for the trees that died to print this crap.
\item
  \textbf{Ignore books that rehash thoroughly debunked cover-ups and
  conspiracies.} 9/11 was not an inside job, there are no miracle cancer
  cures, Bigfoot does not exist, the pyramids were not built by aliens,
  dowsing is crap, Oswald shot Kennedy, and the world did not end on
  December 21, 2012. Being a
  \href{http://bakerjd99.wordpress.com/2009/10/29/hard-ass-skeptic-rules/}{hard-ass
  skeptic} clears entire drivel laden bookshelves.
\item
  \textbf{Do not read diet books.} You are not going to learn anything
  you don't already know. We know why we're fat. We eat too much and
  move to little. It's really that simple. Get off you're stupid obese
  ass and stop wasting your money on diet books.
\item
  \textbf{Do not read computer books with high screen-shot densities.}
  As a programmer I am constantly pawing through computer books and it
  pains me to report that vast swathes of this technical genre are
  awful. Stop printing one damn screen shot after another. It's not
  helping.
\item
  \textbf{Ignore how to get rich books.} Get rich whores are worse than
  insta-history whores and often far more damaging to the pocketbooks of
  gullible readers.
\item
  \textbf{Give any book sharing Steve Job's secrets a wide berth.} The
  necrophages writing this tripe are stunted little animals. Let's feed
  on the dead, rich, white guy. Maybe if we eat his soul we'll get rich
  too.
\end{enumerate}

See that wasn't so bad. With these ten rules you, shrink big-box
bookstores to manageable dimensions, speed up online searching, and
cut your exposure to rage fomenting mental pollution. I must warn you
that there are exceptions my rules and it delights me when I find them.
If you can point to books that break my rules please drop a note.
\emph{I enjoy being wrong; it's an opportunity to learn something and
it's a rare experience.}



%\end{document}