%\input{bmamble.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2020/12/26/cataract-conjunction-caps-coronavirus-year/}{Cataract Conjunction Caps Coronavirus Year}}
\addcontentsline{toc}{subsection}{Cataract Conjunction Caps Coronavirus Year}


\noindent\emph{Posted: 27 Dec 2020 00:00:50}
\vspace{6pt}

Our crappy Coronavirus year wound down with a bright spot: actually, two
of them. On the 21st of December 2020, Jupiter and Saturn appeared right
beside each other in the early evening southwestern sky. The last time
they could be seen
\href{https://astronomy.com/news/2020/12/jupiter-and-saturn-will-form-rare-christmas-star-on-winter-solstice}{this
close it was 1226:} Notre Dame was still being built and the world was
filled with ill-informed naked apes that thought Astrology was a thing!
Boy have we progressed --- not!

For the week leading up to the ``great conjunction,'' I wondered if I
would see it. The skies of Southern Idaho were filled with nasty opaque
clouds but the weather broke and I was able to observe the conjunction
from my backyard. In 16x70 binoculars I could easily make out Jupiter's
disk and see that Saturn was ``not round'' but my cataract
comprised eyes could not resolve any moons or Saturn's rings. Without
binoculars, the great conjunction looked like a \emph{tri-junction.} My
cataracts split point sources of light into multiple images. The
conjunction looked like a little star cluster while bright solitary
stars looked like visual binaries. Declining vision blows but on a
lighter note, I'm seeing a lot more stars these days! Cataract surgery
is on my 2021 agenda, but it will have to wait for the Coronavirus
pandemic to subside. Hospitals are way too busy coping with Winnie the
Kung Flu victims to deal with minor old fart elective procedures.

Unlike many, I don't consider 2020 to be the worst year ever. I've
personally endured far worse. The year I simultaneously tore the
quadricep tendons in both legs and spent months in painful rehab easily
\emph{out-agonizes} the minor irritants of 2020. Honestly, I've enjoyed
some of 2020's \emph{hardships}, starting with being forced to work from
home.

I've long held that there are very few ``legitimate'' reasons for
IT workers to haul their asses into the office to be ``managed.'' This
has been true for well over a decade but in today's world of gigabit
internet, collaboration tools like Teams and Zoom, and remote desktops
controlling virtual machine servers it's ludicrous and insulting.
Management still harps on about how nothing substitutes for the high
bandwidth in-person experience. That when you really want to hash out
ideas and wrestle with demanding concepts getting together is still the
best option. This, of course, blithely assumes management deals with
ideas and concepts. Maybe it's just me, but I've rarely observed
``concepts'' in the management wild. For me, the typical business
meeting is an exercise in eye-rolling suppression; the Microsoft Teams
experience is far superior for 90\% of day-to-day meetings.

My problem hasn't been working for home. My problem is what do I do when
I'm expected to return to the office. I'm hoping to make working from
home a permanent thing but if that proves impossible, I'll retire,
\emph{again}, for good. It's great having options.

My ambitions for 2021 go beyond continuing to work from home. I always
have a few projects on the go, but I rarely blog about them because I
hate having to explain why most of my projects never get completed or
morph into something else during execution. \emph{Don't turn your
hobbies into jobs!} Making a TODO list feels ``jobby'' but despite my
advanced age and well-earned cynicism, especially about my own plans, I
occasionally cough up TODO lists. Here's one for 2021.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Update
  \href{https://analyzethedatanotthedrivel.org/the-jod-page/}{JOD} to
  handle J's new
  \href{https://code.jsoftware.com/wiki/Vocabulary/DirectDefinition}{direction
  definitions}. I'd also like to update JOD's tests and make sure they
  pass in Windows, Mac, and Linux environments.
\item
  Print this blog as a proper ISBN'ed book. In 2020 I released a new
  printed version of the \href{https://www.amazon.com/dp/B08M2KBMND}{JOD
  manual}. It's time to do the same for \emph{Analyze the Data not the
  Drivel.}
\item
  Write at least 50 blog posts: about one a week.
\item
  Upload at least 250 well-captioned images to my
  \href{https://conceptcontrol.smugmug.com/}{SmugMug picture site}. I
  didn't shoot very many pictures in 2020. My photographic passions wax
  and wane. Time to get waxing.
\item
  Learn far more about the \href{https://www.rust-lang.org/}{RUST
  programming language} and write some RUST binaries that can be called
  from J or Python.
\item
  Read at least twenty books. Binge streaming and, to a much lesser
  degree, work interfered with my 2020 reading.
\item
  Work through at least three \emph{math-intense} books.
\item
  Make another pass at learning and using
  \href{https://leanprover.github.io/}{proof assistants like LEAN}.
\end{enumerate}

Well, that ought to be enough rope to hang myself with. We can all meet
here again next year and peruse my magnificent excuses for doing very
little of the above. Oh, and one more thing:
\href{https://www.youtube.com/watch?v=I_izvAbhExY}{just stay alive}. At
my age this can no longer be taken for granted.



%\end{document}
 

