%\input{bmamble.tex}

\subsection*{\href{http://bakerjd99.wordpress.com/2011/08/13/common-table-expression-cte-sqlserver-queries-with-j/}{Common Table Expression (CTE) SQLServer Queries with J}}
\addcontentsline{toc}{subsection}{Common Table Expression (CTE) SQLServer Queries with J}


\noindent\emph{Posted: 13 Aug 2011 22:01:10}
\vspace{6pt}

I've been blogging long enough to observe that your \emph{awesome posts
are often ignored} while your little ``one-offs'' sometimes strike
\href{http://www.webopedia.com/TERM/H/hit.html}{hit} gold. This is
particularly true for ``code example'' posts. When I'm trolling for code
--- the geek equivalent of trolling for babes --- I don't want to read
about the author's programming philosophy or what the hell he thinks
about the idiot in the White House. \textbf{Just show me the code and
shut up!}

So, taking my own advice, the following is an example of a SQLSever
\href{http://msdn.microsoft.com/en-us/library/ms190766.aspx}{Common
Table Expression} (CTE) query.

%[sourcecode language="sql" wraplines="false" gutter="false" autolinks="false"]
\begin{lstlisting}[language=SQL,frame=single,framerule=0pt,label=lst:scr1795X0]
WITH cte1
     AS (SELECT c.obj_id                            AS obj_id,
                a.created                           AS creation_date,
                Datediff(DAY, a.created, Getdate()) AS day_cnt
         FROM   [HIST].[dbo].[History] a
                JOIN [HIST].[dbo].[HistorySummary] b
                  ON a.rowid = b.rowid
                JOIN [HIST].[dbo].[ObjectNames] c
                  ON c.obj_name = b.obj_name),
     cte2
     AS (SELECT cte1.obj_id AS obj_id,
                CASE
                  WHEN cte1.day_cnt <= 30 THEN 1
                  ELSE 0
                END         AS d0,
                CASE
                  WHEN ( cte1.day_cnt > 30 )
                       AND ( cte1.day_cnt <= 60 ) THEN 1
                  ELSE 0
                END         AS d1,
                CASE
                  WHEN ( cte1.day_cnt > 60 )
                       AND ( cte1.day_cnt <= 90 ) THEN 1
                  ELSE 0
                END         AS d2,
                CASE
                  WHEN ( cte1.day_cnt > 90 ) THEN 1
                  ELSE 0
                END         AS d3
         FROM   cte1)
SELECT obj_id,
       SUM(d0) AS OneMonth,
       SUM(d1) AS TwoMonths,
       SUM(d2) AS ThreeMonths,
       SUM(d3) AS Overdue
FROM   cte2
GROUP  BY obj_id
\end{lstlisting}

CTE queries \emph{essentially} create temporary virtual tables during
query execution. They are similar to nested SQL queries but are easier
to code, more general, (see
\href{http://msdn.microsoft.com/en-us/library/ms186243.aspx}{recursive
CTE queries}), and often perform better than their convoluted
equivalents. This example creates two virtual tables \texttt{cte1} and \texttt{cte2} that
are then used to compute a quick histogram.

You can call CTE queries with the
\href{http://www.jsoftware.com/jwiki/ODBC}{J ODBC} interface. The
following assumes a SQLServer ODBC connection
\href{http://www.geeksengine.com/article/mysql-odbc.html}{dsn} history.

%[sourcecode wraplines="false" gutter="false" autolinks="false"]
\begin{lstlisting}[language=jdoc, frame=single,framerule=0pt,label=lst:scr1795X1]
NB. odbc interface
require 'dd'

NB. read CTE query
HistoryAgeSQL=. read 'c:/temp/HistoryAge.sql'

NB. connect sqlserver database
ch =. ddcon 'dsn=history'

NB. select with CTE query
sh =. HistoryAgeSQL ddsel ch

NB. fetch results
data=. ddfet sh,_1
\end{lstlisting}

As a final note it's worth comparing the SQL CTE histogram code with J
equivalents. The two following J verbs taken from the
\href{http://www.jsoftware.com/jwiki/FrontPage}{J wiki},
(\href{http://www.jsoftware.com/jwiki/Essays/Histogram}{here} and
\href{http://www.jsoftware.com/jwiki/BrianSchott/Histogram}{here}),
compute histograms.


%[sourcecode wraplines="false" gutter="false" autolinks="false"]
\begin{lstlisting}[language=jdoc, frame=single,framerule=0pt,label=lst:scr1795X2]
NB. computes histograms uses right open intervals
histogram=:<:@(#/.~)@(i.@#@[ , I.)

NB. variation on (histogram) uses left open intervals
histogram2=:<:@(#/.~)@(i.@>:@#@[ , |.@[ (#@[ - I.) ])
\end{lstlisting}

They scale to tens of millions of data points; returning results in a
few seconds on my laptop. The SQL CTE, shown above, takes about three
seconds running on 180,000 row tables on my employer's
\href{http://www.trekmania.net/science/warp\_scale.htm}{full warp}
servers. If I could convince the masses to adopt languages like J a
large part of my job would disappear. Fortunately, \emph{the world is
hostile to terse elegance!}



%\end{document}