%\input{bmamble.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2015/06/13/copulation-cooking-and-cleaning/}{Copulation, Cooking and Cleaning}}
\addcontentsline{toc}{subsection}{Copulation, Cooking and Cleaning}


\noindent\emph{Posted: 13 Jun 2015 18:21:29}
\vspace{6pt}

A refreshing
\href{http://www.merriam-webster.com/dictionary/blogosphere}{blogosphere}
development is something called the
\href{http://www.urbandictionary.com/define.php?term=Manosphere}{``manosphere.''}
The manosphere is a mangy collection of young male bloggers that have
had it with man hating feminism. I'm an old boomer fart, not exactly the
manosphere demographic, but I see their point. I remember when
rational feminists\footnote{\emph{Rational feminist} was not oxymoronic when the movement started.
} set %\hyperdef{}{fnref1}{}{\hyperref[fn1]{\textsuperscript{1}}}
their sights on ``equal pay for equal work.'' I fully
supported pay equity and, when you correct for
\href{http://www.forbes.com/sites/realspin/2012/04/16/its-time-that-we-end-the-equal-pay-myth/}{actual
hours worked}, that battle has been won in \emph{oppressive western
cultures.}\footnote{Not such much in
\href{http://thefederalist.com/2014/07/07/the-pathetic-provincialism-of-american-feminists/}{Clitoridectomy
happy nonwestern} societies.
} But, %\hyperdef{}{fnref2}{}{\hyperref[fn2]{\textsuperscript{2}}}
as every married man knows, what women ask for is seldom what they
really want.

Equity was never the goal of radical feminists! Radical feminists are
nasty menstruating socialists. Their perfect world looks a lot like an
old-fashioned
\href{http://en.wikipedia.org/wiki/New_Soviet_man}{new-man} communist
utopia: a utopia that was rudely rejected for all sorts of
\href{http://www.slate.com/articles/news_and_politics/foreigners/2008/08/death_of_a_writer.html}{Gulag'ey}
reasons. Sadly, radical feminists don't take rejection gracefully. Once
a month their bitter frustrations manifest as malignant misandry. Yeah,
``femnazis'' are real and they're everywhere! Femnazicism rears its ugly
bull dyke head in repressive
\href{http://www.nytimes.com/2015/03/22/opinion/sunday/judith-shulevitz-hiding-from-scary-ideas.html?_r=0}{campus
speech codes}, phony palimony suits,
\href{https://en.wikipedia.org/wiki/False_accusation_of_rape}{bogus rape
claims}, ``fat acceptance'' campaigns, and tiresome PMS laced whining
about how hard it is to find a \emph{real} man. Well ladies, I am going
to let you in on a little guy secret; \emph{it's much harder to find a
real woman!}

What I am about to say will strike manospherians, and real men
everywhere, as obvious but we can no longer count on men being men.
There are a lot of misguided
\href{http://www.urbandictionary.com/define.php?term=White+Knight}{white
knights} and whipped
\href{http://rationalwiki.org/wiki/Fun:Mangina}{manginas} out there so
grab your sanitary napkins and brace for reality.

\emph{In pre-pussy-boy days, men looked for, fought over, and highly
valued ``three C'' women.}

What the hell is a ``three C'' woman? A three C woman understands men.
She has intuitively, or intellectually, grasped that human males are
simple short-lived creatures that are biologically programmed to seek
three things from woman: \emph{copulation, cooking and cleaning} - the
three Cs.

You can determine a man's age by how he sorts his three Cs. When we're
young copulation is our absolute number one priority. Given a choice
between copulation, cooking and cleaning we'll always pick copulation.
When we're older, more settled, and our frantic need for copulation
subsides, given a choice of fine cuisine or fine ass, we may choose the
former. Finally, in our limp dotage, when Viagra no longer works, gently
wiping the dribble off our chins, (cleaning), after a fine meal,
(cooking), is greatly appreciated. Ladies if the three Cs are graciously
on tap we'll happily put up with any amount of lady-shit. It sounds
simple because it
is!\footnote{Male maintenance requires some real work. Men expect to put in long
hours looking after the women in their lives and they expect women to
reciprocate. Unfortunately modern feminism labels such reciprocation
``oppression.''}%\hyperdef{}{fnref3}{}{\hyperref[fn3]{\textsuperscript{3}}}

Bang us, feed us, and cleanup afterwards, \emph{without nagging
resentment,} and we will love, cherish, protect, work, and die for you!
And, here's the good news; you don't have to be a Victoria Secret
maximum babe to pull this off. In purely economic terms any comely young
woman who masters the three Cs is literally worth her weight in
gold!\footnote{I am assuming a normal female weight of less than sixty-five
kilograms. \emph{Obese land fe-whales} are not worth their weight in
gold.} At %\hyperdef{}{fnref4}{}{\hyperref[fn4]{\textsuperscript{4}}} 
current gold prices
\href{http://www.wolframalpha.com/input/?i=dollar+value+of+60kg+gold}{one
woman weight} is about \$2,300.000 US. Amortized over a fifty year
marriage that works out to around \$45,000 per year. Guys, just try
paying for hookers, gourmet takeout, and maid services for a measly
\$45,000 a year. When you throw \emph{love} into the deal the quality
three C woman is the biggest bargain out there. So ladies, if you really
want a \emph{real} man, master your three Cs and you'll have your pick
of them.

%\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
%
%\begin{enumerate}
%\item
%  \hyperdef{}{fn1}{}
%
%  \emph{Rational feminist} was not oxymoronic when the movement
%  started.\hyperref[fnref1]{↩}
%\item
%  \hyperdef{}{fn2}{}
%
%  Not such much in
%  \href{http://thefederalist.com/2014/07/07/the-pathetic-provincialism-of-american-feminists/}{Clitoridectomy
%  happy nonwestern} societies.\hyperref[fnref2]{↩}
%\item
%  \hyperdef{}{fn3}{}
%
%  Male maintenance requires some real work. Men expect to put in long
%  hours looking after the women in their lives and they expect women to
%  reciprocate. Unfortunately modern feminism labels such reciprocation
%  ``oppression.''\hyperref[fnref3]{↩}
%\item
%  \hyperdef{}{fn4}{}
%
%  I am assuming a normal female weight of less than sixty-five
%  kilograms. O\emph{bese land fe-whales} are not worth their weight in
%  gold.\hyperref[fnref4]{↩}
%\end{enumerate}



%\end{document}