%\input{bmamble.tex}

\subsection*{\href{http://bakerjd99.wordpress.com/2009/10/26/counting-gods/}{Counting Gods}}
\addcontentsline{toc}{subsection}{Counting Gods}


\noindent\emph{Posted: 26 Oct 2009 16:28:33}
\vspace{6pt}

How many fingers do you need to count gods? If you are like most people
you simply assume the set of gods is enumerable and then you start
fighting over which value in the set of positive integers $\mathbb{Z}_{\geq0}$
or ${0, 1, 2, 3, \ldots, }$ is correct. This process is
\href{http://conceptcontrol.smugmug.com/photos/1123810114\_ARzWN-L.jpg}{elegantly
explained by this flowchart}.

I have a simple question. Is the set of gods enumerable? For all you
\href{http://www.aolsvc.merriam-webster.aol.com/dictionary/innumerate}{\emph{innumerates}} out
there a set is enumerable \emph{if-and-only-if} its members can be
counted. It's a rather astonishing fact that many humdrum sets cannot be
counted. Do you remember line segments $\overline{AB}$ from school
geometry?

The number of points in \emph{any} nonzero length Euclidean line segment
$\overline{AB}$ cannot be counted. There are more points in $\overline{AB}$
than there are counting numbers. If you don't believe me check out
\href{http://en.wikipedia.org/wiki/Cantor's\_diagonal\_argument}{Cantor's
diagonal argument} and savor a classical mathematical treat.

Once you get your head around the idea that some things cannot be
counted the notion of counting gods looks ludicrous. Why do you expect
to tally your supreme beings with ordinary counting numbers when they
cannot deal with line segments? Perhaps god counting requires more than
positive integers!

Perhaps the bloody disputes between atheists $GodCount=0$ and deists
$GodCount > 0$ can be resolved with rational numbers $\mathbb{Q}$. How
about fractional $1/2$ gods? Let's just split the difference and
all get along. Unfortunately rational numbers will not satisfy
\emph{ultrapolytheists}, believers in more gods than you can count,
because you
\emph{\href{http://www.homeschoolmath.net/teaching/rational-numbers-countable.php}{can
count rational numbers}}. Ultrapolytheists need to get real
$\mathbb{R}$ -- the numbers - anyway.

Counting gods is a complex problem. Electrical engineers cannot deal
with the wiring in your fridge without complex numbers $\mathbb{C}$.
Maybe a god count of $3 + 7i$ is the ticket

If this sounds silly, condescending and sarcastic congratulations your
bullshit detector is working. However, ridiculous as this little
diatribe is, \emph{\href{http://www.ffrf.org/}{it is as sound as any
mainstream religious doctrine}.} So if you find this absurd and, you
have a fixed god count in your little head, who is really being silly?


%\end{document}