%\input{bmamble.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2015/04/16/dark-energy-entities/}{Dark Energy Entities}}
\addcontentsline{toc}{subsection}{Dark Energy Entities}


\noindent\emph{Posted: 17 Apr 2015 03:44:02}
\vspace{6pt}

I've been having fun on a new social media site called
\href{http://www.quora.com/John-Baker-98}{Quora}. Quora operates on the
\href{http://stackoverflow.com/}{StackOverFlow} principle. People pose
questions and others answer. The act of asking of sincere questions,
\href{http://www.quora.com/How-would-the-world-change-if-prairie-dogs-spontaneously-became-super-intelligent-but-only-the-French-knew-about-it}{even
silly ones}, seems to take the wind out of troll sails. Political sites
quickly degenerate into primate poo tossing contests. I enjoy pitching
poo with the best of them but I demand wit, verve and humor with my
insults. Sadly, these qualities are the first to go when vicious trolls
tear into partisan believers of any persuasion. Honest political
conversations have never been easy. I remember screeching, mostly
left-wing, university harridans shouting down heretics forty years ago.
I'm sure they would have burned them at the stake if the option had been
available. Still there is something about the question that makes people
put down their torches and give a heretic a break.

A good question and answer session is like a connect-the-dots cartoon.
For example \href{http://www.quora.com/Javed-Qadrud-Din}{Javed
Qadrud-Din} observed when responding to the question:

\begin{quote}
\href{http://www.quora.com/Hypothetically-if-there-is-intelligent-alien-life-with-the-knowledge-and-means-to-traverse-space-and-travel-to-Earth-what-would-be-their-reasons-for-not-making-contact-Please-read-details}{Hypothetically,
if there is intelligent alien life, with the knowledge and means to
traverse space and travel to Earth, what would be their reasons for not
making contact?}
\end{quote}

\noindent That aliens might be billions of years ahead of us and

\begin{quote}
we would be unable to recognize the evidence of their existence, and
such evidence would instead appear to us as aspects of the nature of
reality itself.
\end{quote}

\noindent I thought about this and responded:

\begin{quote}
Your observation that some alien intelligences could be billions of
years ahead of us and may, ``appear as part of nature,'' made we wonder
what might qualify as a manifestation of such beings. It goes without
saying that super advanced beings with real immortal ambitions will be
somewhat bummed with mere matter. If our, admittedly primitive physical
theories hold up, it looks like in the very long run, e.g.
10\textsuperscript{100} or more years, all matter will decay and space
will expand into an unimaginably vast void with a temperature
indistinguishable from absolute zero. All matter and energy based
sentience will be snuffed out: everything, absolutely everything dies.
What's left in such a universe? Only Dark Energy survives and prospers.
Cosmologists have noted that we appear to live in a Dark Energy dominated
universe and the domination started fairly recently, within the last two
billion years or so. If intelligent life evolved somewhere in the cosmos
six or seven billion years ago that would be plenty of time to advance
to the point that such beings could insert themselves into the only
durable part of our universe: space itself. So perhaps the accelerating
expansion of space is the ``part of nature'' that gives away the
presence of such highly evolved beings.
\end{quote}

We may be living in a Dark Energy Entity \emph{Cosmoscene.} It's
unlikely that beings able to alter the entire observable universe are
going to make contact with pitiful little poo throwing naked apes.



%\end{document}