%\input{bmamblenew.tex}

\subsection*{\href{https://analyzethedatanotthedrivel.org/2020/01/20/extracting-sql-code-from-ssis-dtsx-packages-with-python-lxml/}{Extracting SQL code from SSIS dtsx packages with Python lxml}}
\addcontentsline{toc}{subsection}{Extracting SQL code from SSIS dtsx packages with Python lxml}


\noindent\emph{Posted: 21 Jan 2020 02:30:48}
\vspace{6pt}

Lately, I've been refactoring a sprawling SSIS
\href{https://docs.microsoft.com/en-us/sql/integration-services/sql-server-integration-services?view=sql-server-ver15}{(SQL
Server Integration Services)} package that ineffectually wrestles with
large XML files. In this programmer's opinion using SSIS for heavy-duty
XML parsing is geeky self-abuse so I've opted to replace an eye-ball
straining\footnote{
I frequently run into SSIS packages that cannot be viewed on \texttt{4K}
monitors when fully zoomed out.
} SSIS package
with half a dozen,
\href{https://quoteinvestigator.com/2011/05/13/einstein-simple/}{``as
simple as possible but no simpler''}, Python scripts. If the Python is
fast enough for production great! If not the scripts will serve as a
clear model\footnote{
Python's readability is a major asset when disentangling \emph{mess-ware}.
} for something faster.

I'm only refactoring\footnote{
Yes, I've railed about the word ``refactoring'' in the past but I've
moved on and so should you.
\href{https://www.dictionary.com/browse/a-foolish-consistency-is-the-hobgoblin-of-little-minds}{``A
foolish consistency is the hobgoblin of little minds.''}
} part of a larger \href{https://www.webopedia.com/TERM/E/ETL.html}{ETL}
process so whatever I do \emph{it must mesh with the rest of the mess.}

\medskip

\textbf{\emph{So where is the rest of the SSIS mess?}}

\medskip

SSIS's visual editor does a wonderful job of hiding the damn code!

\medskip

\textbf{\emph{This is a problem!}}

\medskip

If only there was a simple way to troll through large sprawling SSIS
\emph{spider-webby} packages and extract
\href{https://www.youtube.com/watch?v=wPiHQ37gXnE}{the good bits}.
Fortunately, Python's XML parsing tools can be easily applied to SSIS
\texttt{dtsx} files. \emph{SSIS \texttt{dtsx} files are XML files.} The
following code snippets illustrate how to hack these files.

First import the required Python modules. \texttt{lxml} is not always
included in Python distributions. Use the
\href{https://remotedevdaily.com/how-to-install-lxml-in-python-using-pip/}{pip}
or \href{https://anaconda.org/anaconda/lxml}{conda} tools to install
this module.

\begin{lstlisting}[language=python, frame=single, framerule=0pt, label=lst:scr5673X0]
# imports
import os
from lxml import etree
\end{lstlisting}

Set an output directory. I'm running on a Windows machine. If you're on
a Mac or Linux machine adjust the path.

\begin{lstlisting}[language=python, frame=single, framerule=0pt, label=lst:scr5673X1]
# set sql output directory
sql_out = r"C:\temp\dtsxsql"
if not os.path.isdir(sql_out):
    os.makedirs(sql_out)
\end{lstlisting}


Point to the \texttt{dtsx} package you want to extract code from.


\begin{lstlisting}[language=python, frame=single, framerule=0pt, label=lst:scr5673X2]
# dtsx files
dtsx_path = r'C:\Users\john\AnacondaProjects\testfolder\bixml'
ssis_dtsx = dtsx_path + r'\ParseXML.dtsx'
\end{lstlisting}


Read and parse the SSIS package.

\begin{lstlisting}[language=python, frame=single, framerule=0pt, label=lst:scr5673X3]
tree = etree.parse(ssis_dtsx)
root = tree.getroot()
\end{lstlisting}


\texttt{lxml} renders XML namespace tags like
\verb|<DTS:Executable| as
\verb|www.microsoft.com/SqlServer/Dts\}Executable|. The following
gathers all the transformed element tags in the \texttt{dtsx} package.


\begin{lstlisting}[language=python, frame=single, framerule=0pt, label=lst:scr5673X4]
# collect unique element tags in dtsx
ele_set = set()
for ele in root.xpath(".//*"):
    ele_set.add(ele.tag)    
print(ele_set)
print(len(ele_set))
\end{lstlisting}

Using transformed element tags of interest blast over the \texttt{dtsx}
and suck out the bits of interest.

\begin{lstlisting}[language=python, frame=single, framerule=0pt, label=lst:scr5673X5, basicstyle=\ttfamily\scriptsize]
# extract sql code in source statements and write to *.sql files 
total_bytes = 0
package_name = root.attrib['{www.microsoft.com/SqlServer/Dts}ObjectName'].replace(" ","")
for cnt, ele in enumerate(root.xpath(".//*")):
  if ele.tag == "{www.microsoft.com/SqlServer/Dts}Executable":
    attr = ele.attrib
    for child0 in ele:
      if child0.tag == "{www.microsoft.com/SqlServer/Dts}ObjectData":
        for child1 in child0:
          sql_comment = attr["{www.microsoft.com/SqlServer/Dts}ObjectName"].strip()
          if child1.tag == "{www.microsoft.com/sqlserver/dts/tasks/sqltask}SqlTaskData":
            dtsx_sql = child1.attrib["{www.microsoft.com/sqlserver/dts/tasks/sqltask}SqlStatementSource"]
            dtsx_sql = "-- " + sql_comment + "\n" + dtsx_sql
            sql_file = sql_out + "\\" + package_name + str(cnt) + ".sql"
            total_bytes += len(dtsx_sql)
            print((len(dtsx_sql), sql_comment, sql_file))
            with open(sql_file, "w") as file:
              file.write(dtsx_sql)
print(('total sql code bytes',total_bytes))
\end{lstlisting}


The code snippets in this post are available in this Jupyter notebook:
\href{https://github.com/bakerjd99/jacks/blob/master/notebooks/Extracting\%20SQL\%20code\%20from\%20SSIS\%20dtsx\%20packages\%20with\%20Python\%20lxml.ipynb}{Extracting
SQL code from SSIS dtsx packages with Python lxml}. \emph{Download and tweak
for your \texttt{dtsx} nightmare!}

%\begin{verbatim}
%\end{verbatim}
%
%\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
%
%\begin{enumerate}
%\item
%  \hypertarget{fn1}{}
%
%  I frequently run into SSIS packages that cannot be viewed on 4K
%  monitors when fully zoomed out.\protect\hyperlink{fnref1}{↩}
%\item
%  \hypertarget{fn2}{}
%
%  Python's readability is a major asset when disentangling
%  \emph{mess-ware}.\protect\hyperlink{fnref3}{↩}
%\item
%  \hypertarget{fn3}{}
%
%  Yes, I've railed about the word ``refactoring'' in the past but I've
%  moved on and so should you.
%  \href{https://www.dictionary.com/browse/a-foolish-consistency-is-the-hobgoblin-of-little-minds}{``A
%  foolish consistency is the hobgoblin of little
%  minds.''}\protect\hyperlink{fnref3}{↩}
%\end{enumerate}



%\end{document}
