%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2023/01/08/for-me-in-twenty-twenty-three/}{For Me in Twenty Twenty-Three}}
\addcontentsline{toc}{subsection}{For Me in Twenty Twenty-Three}


\noindent\emph{Posted: 09 Jan 2023 06:17:47}
\vspace{6pt}

Let's get this over with!

Every year I task myself with a list of \emph{publicly declared
goals,}\footnote{Private goals can be conveniently
  memory-holed.} and %\protect\hypertarget{fnref1}{\protect\hyperlink{fn1}{\textsuperscript{1}}}
then in the next year, if I find myself among the
living,\footnote{At my age this cannot be taken granted.
} I %\protect\hypertarget{fnref2}{\protect\hyperlink{fn2}{\textsuperscript{2}}}
grade myself. How did 2022 go? Let's start with my \emph{small} goals.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Goal:} \emph{Observe as many Messier objects as weather
  permits and get my \href{https://rasc.ca/}{RASC} certificate.}
\end{enumerate}

Well, I did not get my RASC certificate but I made progress. Meridian's
skies are often overcast and even when clear, are horribly
light-polluted. I figure I can only \emph{naked-eye} magnitude 3 or 4
stars from my backyard. When using my binoculars or telescope I estimate
I lose two or more stellar magnitudes to light pollution. Bright,
magnitude 8 or 9 Messier objects, that are easily seen with binoculars
from dark sites are not visible in my backyard. It's frustrating.
\href{https://www.youtube.com/watch?v=VdO--3UL5D8}{\emph{Urge to kill rising!}} To make a dent in my list of \emph{missing
Messiers} I will need to seek out dark skies. For 2023, I am repeating
this goal; I will keep looking until I complete my \emph{Messiers} or
expire. As for my ``grade,'' I'm giving myself an \textbf{Incomplete}.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\item
  \textbf{Goal:} \emph{Learn more proper northern hemisphere star
  names.}
\end{enumerate}

I am pursuing the quixotic quest of stepping outside on my patio and
calling out the visible ``named'' stars. This is a rare astronomical
task that \emph{light pollution helps}; it greatly reduces the number of
stars you must name. I am making slow progress. I can already achieve
this goal on some nights, especially partly overcast nights, as only the
brightest planets and stars can be seen. For 2023 I will increase my
efforts and cultivate some productive habits like looking up the ten
brightest named stars visible from my backyard on given nights. I'm
giving myself another \textbf{Incomplete}.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\item
  \textbf{Goal:} \emph{Continue shooting and adding captioned images to
  \href{https://conceptcontrol.smugmug.com/}{my pictures site}.}
\end{enumerate}

In 2022 I set an all-time captioned image upload record. I wrote almost
as many \emph{caption
words}\footnote{I call them
  \href{https://analyzethedatanotthedrivel.org/2016/05/22/milliblog-photo-captions/}{milliblogs}
} (about {5}0 pages), %\protect\hypertarget{fnref3}{\protect\hyperlink{fn3}{\textsuperscript{3}}}
as \emph{blog words} (about 60 pages). Many 2022
pictures came from our
\href{https://conceptcontrol.smugmug.com/Trips/Overseas/Australia-New-Zealand-2022/i-FdKCt59}{Australia
and New Zealand trip}. But, importantly, I more than met my goal. I'm
giving myself an \textbf{A+}. For 2023 I am not setting an image quota.
I will upload pictures when the whim strikes.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\item
  \textbf{Goal:} \emph{Read at least ten books.}
\end{enumerate}

I read twenty books so I'm giving myself an \textbf{A}. For 2023 I am
not setting any reading goals. I will read what I read.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\item
  \textbf{Goal:} \emph{Blog more!}
\end{enumerate}

In 2022 I cranked out 19 blog posts: not great, but better than many
previous years. I'm giving myself a \textbf{C+}. For 2023 I am planning
to break my all-time blog post record. In 2012 I wrote 37 posts, so I
have to hit 38.

That completes my small goals for 2022. In 2023 I'm adding one
additional small goal.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\item
  \textbf{Goal:} \emph{Weigh 85 kilograms or less on December 25, 2024.}
\end{enumerate}

For the last two years, I have been slowly losing weight: currently, I'm
at 88 kilograms. I haven't been making an effort to lose weight, it's a
consequence of walking a lot, and staying on the Mali diet. The Mali
diet is super-heathy, anyone that stays on it will lose weight. I might
as well make it a little goal.

Now let's address the \emph{Humpback in the Sea}. How did I do with my
primary priority project which was:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{6}
\item
  \textbf{Whale Goal:} \emph{Write a first draft of a short book that
  uses \href{https://leanprover-community.github.io/}{LEAN} to formally
  prove some school geometry theorems.}
\end{enumerate}

I've written a fragmented partial draft and I've made headway on the
thousands of little things you must do to write a book about software,
mathematics, and history but overall, I have failed --- abjectly! I'm
giving myself an \textbf{F+}\emph{. I am not giving up!} I will continue
working on this project in 2023 but I'm changing how I swim after this
whale.

To start, I am going to write some \emph{typical programs} in
\href{https://github.com/leanprover/lean4}{LEAN4}. The LEAN type system
is powerful enough to \emph{formally} prove advanced mathematical
theorems. This distinguishes LEAN from most programming languages and
tells this old polyglot programmer that ``LEANish'' languages represent
something new and important. Most mathematicians using LEAN focus on
formal theorem proving but my tiny naked ape brain may have better luck
with prosaic ``hello world'' applications. As I work out some LEAN
programs I will post them here.

Finally, I'm going to take Roy Peter Clark's advice (see
\href{https://www.amazon.com/Writing-Tools-Essential-Strategies-Writer-ebook/dp/B000SEIW9E}{Writing
Tools}) and write about the problems I face while working on my draft.
I'll use this blog as a test site, sounding board, whipping post, and
confessional as I foolishly attempt to outswim a whale.

Overall, I'm rating 2022 as a \textbf{D+} year. I will make efforts to
improve, and if in 2024 I find myself among the living, I will tell you about it.

%\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
%
%\begin{enumerate}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn1}{}}%
%  Private goals can be conveniently
%  memory-holed.\protect\hyperlink{fnref1}{↩︎}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn2}{}}%
%  At my age this cannot be taken granted.\protect\hyperlink{fnref2}{↩︎}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn3}{}}%
%  I call them
%  \href{https://analyzethedatanotthedrivel.org/2016/05/22/milliblog-photo-captions/}{milliblogs}.\protect\hyperlink{fnref3}{↩︎}
%\end{enumerate}



%\end{document}
 
