%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2024/03/28/frankenstein-weather/}{Frankenstein Weather}}
\addcontentsline{toc}{subsection}{Frankenstein Weather}


\noindent\emph{Posted: 28 Mar 2024 19:19:49}
\vspace{6pt}

In my old age, I've picked up a nasty habit: a fondness for literary
biographies. Recently, I've enjoyed books about Keats, Shelley, Byron,
Blake, Twain, Orwell, Tagore, Joyce, and others. It's a strange
affliction --- utterly without rational basis, lacking the danger of
street drugs, but like drugs delivering peculiar damaging delights. Last
night, while enjoying Andrew Stauffer's new Byron biography,
\href{https://www.amazon.com/Byron-Life-Letters-Andrew-Stauffer/dp/100920016X}{\emph{Byron
a Life in Ten Letters}}, I revisited the famous \emph{Frankenstein}
origin story. In the summer of 1816, Lord Byron, Percy Bysshe Shelly,
Mary (Godwin) Shelly, John Polidori, and Claire Clairmont spent a long,
extremely dark, and rainy summer together near the shore of Lake Geneva
in Switzerland. On one of that summer's dark, gloomy days, they held a
``Who can write the best horror story contest.'' The winner of the
contest was, of course, Mary Shelley with her epic \emph{Frankenstein}.

If you've never read \emph{Frankenstein,} get off your damn phone or
computer, get a copy of the book and read! The novel is orders of
magnitude better than all the movies and TV shows it has inspired.
Ironically, the visual \emph{Frankenstein} derivatives deform Mary's
masterpiece like her novel's protagonist deformed body parts. Trust me,
the book is another country; if you've never visited, you don't know
\emph{Frankenstein}.

As Stauffer pointed out, Frankenstein wasn't the only iconic monster to
emerge from that bleak summer. Byron and Polidori created the urbane,
upper-class, blood-sucking, murderous bad boy that Bram Stoker later
elaborated into the \emph{Dracula} we love today. So, shitty weather
helped create both \emph{Frankenstein} and \emph{Dracula}. I already
knew this. The Shelley \emph{Frankenstein} story is so famous a
\href{https://www.youtube.com/watch?v=Q8Tq5bfYudU}{\emph{Doctor Who}
episode} is based on it. What I didn't know was why the weather of 1816
was so shitty. Stauffer's book connects the dots.

\begin{quote}
\ldots{} a massive eruption of the Tambora volcano in Indonesia the
previous year was the cause of the extraordinarily bad meteorological
conditions. According to Galen Wood, ``The sun-dimming stratospheric
aerosols produced by Tambora's eruption in 1815 spawned the most
devastating, sustained period of extreme weather seen on our planet in
perhaps thousands of years.''
\end{quote}

The summer of 1816 was later called the ``Year without a summer.'' Crops
failed everywhere, and tens of thousands starved. It was a grand little
mini-apocalypse, sure the body count was high, but we got
\emph{Frankenstein} and \emph{Dracula}.

So bad weather is good for literature. Good to know! If one big volcano
can play midwife to \emph{Frankenstein,} imagine the literary canon that
will derive from (say it in a deep, scary monster voice) \emph{Global
Climate Change}! As cities sink beneath rising seas, crops fail, deserts
expand, billions move, and resource wars erupt, authors everywhere,
perhaps even AI authors, will be inspired. Hey, the world might burn,
but boy, we will see some
\href{https://www.urbandictionary.com/define.php?term=Banger}{banger}
literature.

%\end{document}

