%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2025/11/28/franks/}{Franks}}
\addcontentsline{toc}{subsection}{Franks}


\noindent\emph{Posted: 28 Nov 2025 20:06:11}
\vspace{6pt}

Our calculations indicate that the phenomenon began on September
13\textsuperscript{th} at precisely 2:43:05.81458 mountain time. Frank,
that is what he called himself, jumped awake to find another fully grown
man in his bed. Perhaps some background might help. Frank was recently
divorced. His wife had stormed out of their common domicile some months
ago and was in the process of absconding with half of Frank's
possessions. Let's not get distracted with the peculiar and frankly
insane dissolution customs of Frank's people. It made no sense to them,
and we will never understand. Finding another man in your bed,
especially after falling asleep alone, would alarm anyone, but Frank
faced something far more disturbing.

The other man looked exactly like Frank. The resemblance was not
superficial; it was atomic. The other man, the other Frank, was
precisely like the first. Both Franks had the same skin, hair, and eye
color. Both had what Frank considered a unique little ``V'' scar on
their left index fingers. They weighed the same, smelled the same,
sounded the same, and moved the same. Both Franks were even wearing
their favorite ``It's Good to Crush Your Enemies'' T-shirt. Frank never
wore underwear to bed. When the Franks jumped out of bed, their modest
dangling penises were also the same. Both Franks yelled, ``Who are
you?'' and both immediately recoiled when their own voices, sounding
like an audio recording, shouted back.

If the other man had been anyone but another Frank, the situation might
have escalated, but the Franks were identical. Their endocrine systems
reacted alike. At first, their hearts pounded with alarm, but the
absolute impossibility of what they saw calmed both men. Frank, we're
now speaking of the entire class, was a curious borderline autistic
analytic individual. Before the phenomenon, Frank made his way in the
world as a programmer. An occupation that rewards obsessive attention to
detail and precise causal thinking. Frank was an excellent programmer,
but he was, to use the vernacular, an asshole. When he wasn't thinking
about programming, he was thinking about himself. In retrospect, Frank's
divorce was inevitable. The initial configuration was incorrect, and
serious refactoring was infeasible. There is logic in all things. Both
Franks, identical to the synapse, immediately had the same thought as
they gazed at each other. Both immediately asked, ``How?''

The Franks spent the remainder of that first long night running
impromptu experiments. They carefully examined each other and checked
everything they could think of. They weighed each other; they matched to
the scale's precision. They broke out their 10x jewelers' loupe and
confirmed that they both had the same corneal scar. They asked each
other invasive personal questions about things they had kept hidden from
everyone. Before the phenomenon, Frank concealed a vast private inner
life, but both Franks were privy to it all. There could be no secrets
between them. No suppressed shame or disgusting deceit escaped
revelation. They knew each other better than any two humans ever had. It
was alarming and fascinating. Would you like a copy of yourself? Both
Franks confessed they did. The Franks did not sleep for the rest of the
night. As dawn approached, they wanted to go outside and watch Venus in
the morning sky, but both Franks, thinking alike, immediately worried
about what the neighbors would think if they saw two Franks in the yard.
They agreed to take turns in the greater world. As the sun rose, their
analytic minds considered how to take advantage of their doubling.

Our records of that first day are incomplete. We know the Franks left
the house at different times. One went to work while the other went to
the bank to withdraw as much cash as possible. They needed money to test
a conjecture about their ``It's Good to Crush Your Enemies'' T-shirts.
When \emph{work} Frank returned home, \emph{home} Frank was busy making
a plain dinner. They ate together and then spent that first evening
streaming their favorite shows. They didn't talk to each other about how
bizarre it was to ignore their doubling and watch TV nonsense. They both
knew exactly what the other thought; words were redundant. Before going
to bed, they showered together. The Franks, marginally versed in the
classics, knew this was beyond Narcissus looking at a reflection in a
still pond. This was soaping and caressing a solid, perfect, compatible
copy of yourself. Identical erections presented, and the Franks, so
versed in each other that they were beyond shame, explored
possibilities. As they both crawled into the King-size bed formerly
shared with Frank's wife, they took care to tape stacks of dollar bills
to their chests and abdomens. During their day together, they wondered
if more doublings might occur and how their ``It's Good to Crush Your
Enemies'' T-shirts were copied. Could other things be copied?

There are no records of the Franks, or of anyone else or anything else
ever witnessing the phenomenon, but again, at 2:43:05.81458 mountain
time, the Franks were jolted awake. This time, to no Frank's surprise,
four Franks were in the bedroom. Each Frank wore a perfect copy of the
``It's Good to Crush Your Enemies'' T-shirt. Each Frank immediately
pulled off his T-shirt. The four nude Franks stared at each other; they
all saw taped dollar bills on their chests and abdomens. Pulling the
taped bills off their bodies, they checked the serial numbers. The bills
were exact copies. The Franks had doubled themselves and their dollars.
Their conjecture had been sustained. Again, words were redundant. All
Franks were alike. They all remembered staying home and going to work
the day before. Their memories were exact. Nothing was missing.

The Franks had no explanation for the phenomenon. But before the
phenomenon, there was much in Frank's ken for which he had no answer.
What exactly is driving distant galaxies away? Why is time irreversible?
Will the Collatz conjecture ever be proven? Can cosmic entropy be
reversed? Do we have a greater purpose? Unanswerable questions oppressed
Frank. Yet, unlike religious cowards and blinkered ideologues, he
managed to maintain enough intellectual honesty to admit he didn't know
squat and was probably never going to know squat. Frank didn't satiate
his ignorance with pleasant fantasies; he preferred the stark void.
Living with acknowledged ignorance requires courage and humility. Oddly,
this philosophic plasticity made the Franks surprisingly accepting of
their unique situation. You might not be able to explain what's going
on, but you can always exploit it. All four Franks thought the same
thing as they passed the copied bills around. At least money wouldn't be
a problem.

Seconds later, the Franks considered what might happen if the doublings
continued. They looked around their bedroom; they had to act. On the
second day, the four Franks split up. One Frank went to the bank again,
this time to withdraw six one-ounce gold coins from their safety deposit
box. Another Frank went to a car dealer and rented a car. They only had
one driver's license. None had thought about taping their license or
passport to their bodies the night before. A third Frank booked a flight
to a distant city that the Franks had long wanted to visit. As the
second day came to an end, all the Franks gathered at home. Once more,
they showered together, and now, freed from any inhibitions (how could
they justify inhibitions anymore?), they enjoyed. Before falling asleep,
they taped dollar bills, gold coins, and their only passport and
driver's license to their chests and abdomens.

Again, there were no witnesses, but reliably at 2:43:05.81458 mountain
time, eight Franks jerked awake in their bedroom. The eight
T-shirt-adorned men filled the tiny room. Immediately, the Franks
stripped off their T-shirts and inspected the bills, coins, and
documents taped to their bodies. Everything was perfectly duplicated.
Even microscopic dents and scratches on the gold coins were identical.
The Franks looked at each other and smiled. They had anticipated this
doubling. It precipitated their contingency plan. Sharing every memory
and feeling, the Franks were perfectly briefed on what had to be done;
they immediately dispersed. Four Franks piled into the rented car. One
Frank drove while the others ducked under the seats to hide. They
dropped one Frank at the airport and another at the bus terminal. Then
the two Franks in the car headed across country. After a few hours on
the road, the two car Franks split up. One was left in a motel while the
other continued driving. As for the four home Franks, two booked flights
out of the country. The home Franks had only two passports, so only two
of the four could leave. Using their personal car, one Frank drove the
other two to the airport. They took two trips to avoid duplicate Franks
being at the airport at the same time. They all worried their duplicate
passports would get flagged at security, but they weren't. The two
passport-carrying Franks safely managed to leave the country.

The two homebound Franks agreed (Franks never argued) that one Frank
should stay at home to field calls and maintain the façade of normality
for as long as possible. They tossed a coin to decide which Frank would
stay. Once again, they showered together. By now, they were completely
habituated to their unprecedented situation and did not hold back.
Social rules apply to singletons, not multitudes. Before sleeping, they
taped their gold coins, dollar bills, and a copy of their driver's
license to their chest.

Again, the phenomenon passed unobserved, but at precisely 2:43:05.81458
mountain time, sixteen Franks appeared in the world. Immediately, one of
their questions was answered. Did the phenomenon require a unique
location? It did not. A duplicate Frank appeared beside every dispersed
Frank. The Franks in hotels and motels awoke to find \emph{their}
duplicate Frank wearing their favorite ``It's Good to Crush Your
Enemies'' T-shirt beside them. Each Frank remembered, in the strange way
we all walk through our memories, everything the other Franks had
experienced the day before. All Franks recalled passing through
airports, clearing customs, hauling an overnight bag into motels,
changing currency, gassing up the rented car, enjoying sunsets, cinching
seatbelts, enjoying a beer with pretzels, and indulging in homoerotic
peccadillos. Nothing was hidden; it was available to all. The Franks
wondered how they might use this perfect information-sharing. Surely
such a powerful gift could be leveraged. As they mused, they worried
about what would happen when they could no longer conceal themselves.

Our records of the following week of doublings are limited, but the
Franks managed to hide themselves until 4096 Franks walked the Earth.
They dreaded detection day, and they weren't surprised that it came by
accident. Though they took care to limit their use of duplicate
passports, bills, and coins as they rapidly dispersed to every country
on Earth, eventually, a customs check in Accra, Ghana, exposed them.
Within hours of triggering alarms, seven Franks were in custody in
various countries. The authorities were completely confounded. At first,
nobody believed the Franks were in some sense the same person, but as
the interrogations became more detailed and harsher, culminating in
torture. The inexplicable truth forced itself upon the ruling echelons.
Global elites, facing a genuine, uncontrolled element, did what they
always did. They suppressed all knowledge of the Franks and initiated a
worldwide effort to capture and contain them.

The Franks, intimate with powers of two, had anticipated this reaction
on the second day. All programmers know and revere powers of two.
Exponentiation delights analytic minds. The Franks, to once again use
the vernacular, \emph{ran the numbers}. What would uncontrolled
duplication entail? The ruling echelons are venal, amoral, and cruel,
but they're not stupid. They, too, immediately understood the peril,
and, like any cornered beast, the ruling echelons experimented. Two
incarcerated Franks were executed. One was mercifully shot, while the
other was beaten to death. The bodies of the dead Franks were burned,
but again, at 2:43:05.81458 mountain time, two living Franks, both
wearing an ``It's Good to Crush Your Enemies'' T-shirt, appeared where
each solitary Frank had died. Every captured Frank was under constant
video and personal surveillance, but again, nobody and nothing witnessed
the phenomenon. The videos all glitched; the witnesses all looked away
or fell asleep. It seemed the universe was conspiring to conceal the
phenomenon. Now, 8192 Franks briefly walked the Earth. The ruling elites
were terrified and amplified their cruelty.

For the next week of doublings, the authorities managed to hide the
Franks from the public, but the Franks were too widely scattered and
growing too rapidly to be contained. Within hours of public exposure,
Frank's (all Franks') faces became the most famous visage on Earth.
People reacted in every imaginable way. Some, the more numerically
inclined, immediately understood the danger. Others, venting mystical
and religious fervor, proclaimed the Franks to be angels (or demons)
come to Earth. Franks were harbingers; the end times were nigh. Maybe
not the way everyone had expected, but prophetic revelations can be
twisted to any reality. While many Franks were feted, others were
tormented. Cruel experiments were conducted everywhere. Four Franks were
welded into a small steel tank. They died of painful suffocation, then
at 2:43:05.81458 mountain time, the \emph{entanked} Franks doubled,
blasting the tank apart and scattering metal fragments and compressed
and brutalized Frank body parts. But the following day, sixteen living
Franks appeared beside the shattered tank, all wearing that hideous
``It's Good to Crush Your Enemies'' T-shirt.

The monstrous treatment of the doubling Franks during the next month
exceeded all prior genocides and brutalities. History's abominations
seem quaint, amusing, even innocent by comparison. Franks were shot,
hanged, gassed, electrocuted, beheaded, vivisected, irradiated,
incinerated, impaled, crucified, and dissolved in acid. Every possible
attempt was made to curtail their growth, but nothing worked. At
precisely 2:43:05.81458 mountain time, twice as many living Franks, all
naked except for the ``It's Good to Crush Your Enemies'' T-shirt,
reappeared. And no matter how many cameras, witnesses, or experimental
devices were mustered to observe the doublings, the phenomenon was never
recorded or witnessed. How? How? How?

When the number of Franks briefly reached 2,147,483,648, humankind
surrendered. There were only 10 billion people on Earth: one-fifth were
Franks. The next day, 4,294,967,296 Franks walked the Earth, and on the
following day, 8,589,934,592 Franks made up most of the human
population. With each passing day, the Franks overwhelmed the residual,
by now insignificant, human population. During this period of Frank
dominance, the atrocities suffered by the Franks were avenged. The
Franks, more voracious and numerous than locusts, butchered and consumed
everything: people, animals, plants, yet the doublings continued. In two
months, Franks covered the entire Earth. They had run out of land to
stand on. With subsequent doublings, quadrillions of Franks were shoved
into the seas. They drowned in untold quadrillions only to be
reconstituted at 2:43:05.81458 mountain time to drown all over again.
Every Frank felt the pain and fear of his duplicates. An entire Earth of
Franks knew what was coming. They hoped their agonies would soon end.

We are not entirely sure if the agony of the Franks ended, but the
doublings kept going. The increasing mass of the Franks quickly
overwhelmed the Earth, and within a few years, the Earth collapsed into
a stellar-sized black hole. We thought, like many others, the doublings
would cease at the black hole stage, but we were wrong. Our observations
show that the mass of the \emph{Frank Hole} doubles roughly every 24
Earth hours at that abominable and arbitrary Earth time of 2:43:05.81458
mountain time. If the doublings continue, the event horizon of the
\emph{Frank Hole}, which, need I remind you, is a form of space and
therefore not limited by the speed of light, will soon expand so rapidly
that it will devour the observable universe. Gentle sentients, it seems
that Frank's T-shirt motto, ``It's Good to Crush Your Enemies,'' applies
to us all.



%\end{document}
