%\input{bmamble.tex}

\subsection*{\href{http://bakerjd99.wordpress.com/2009/10/21/f-sirens-are-seducing/}{F\# Sirens are Seducing}}
\addcontentsline{toc}{subsection}{F\# Sirens are Seducing}


\noindent\emph{Posted: 21 Oct 2009 20:18:03}
\vspace{6pt}

For the last few days I have been playing around with an
\href{http://research.microsoft.com/en-us/um/cambridge/projects/fsharp/}{early
release of F\#}. F\# looks like it might be a
\href{http://www.microsoft.com/NET/}{.Net} language that I can stand!
The alpha-geeks at Microsoft Research have convinced their corporate
masters that the world needs a \emph{functional programming language
that can be compiled and executed as efficiently as traditional
imperative and object oriented languages.}

As a long time user of interpreted functional programming languages I
can only say: \emph{it's about freaking time!}

F\# appeals to me for a number of reasons:

\begin{enumerate}
\item
  I am familiar with many of the concepts of functional programming.
  Coming from the
  \href{http://en.wikipedia.org/wiki/APL\_(programming\_language)}{APL}
  world I have been using many of these ideas for decades.
\item
  F\# can use .Net facilities. It can call, and be called, by any of the
  .Net languages. Lack of \emph{deep supported} integration with host
  facilities has always hurt languages like J. You pretty much have to
  roll your own for everything.
\item
  F\# can be compiled to virtual machine code just like C\#. APL, J, K
  and others do not compile well.
  \href{http://www.snakeisland.com/}{Heroic attempts have been made to
  compile APL} and similar languages but sometimes heroes fail.
\item
  F\# supports asynchronous and parallel programming. The typical
  computer these days has two, four, eight or more processors. In the
  very near future your grandmother's PC will have eight or more 64 bit
  processors and perhaps hundreds of gigabytes of \emph{real}, (not
  virtual), memory. Programming such machines with conventional
  languages and tools will be, as one blogger noted, insanely
  complicated. F\# may provide a means to focus the power of such
  machines without sweating blood.
\end{enumerate}
I have ordered
\href{http://oreilly.com/catalog/9780596153656}{Programming F\#} and now
I actually have something to look forward to in
\href{http://www.microsoft.com/visualstudio/en-us/products/2010/default.mspx}{Visual
Studio 2010}.


%\end{document}