%\input{bmamble.tex}

\subsection*{\href{http://bakerjd99.wordpress.com/2012/11/18/git-me-a-hubbery/}{Git me a Hub'bery}}
\addcontentsline{toc}{subsection}{Git me a Hub'bery}


\noindent\emph{Posted: 18 Nov 2012 23:51:38}
\vspace{6pt}

Sometime ago I crossed my machine synchronization threshold. I routinely
work on four operating systems, three laptops, a few servers, a bunch of
phones and so on. I synchronized the directories I cared about while
forming deep and rewarding relationships with file sharing services like
\href{https://www.dropbox.com/}{Dropbox}. Dropbox is great but its
success has attracted the attention of paranoid IT micromanagers and
it's now frequently blocked on internal corporate networks. The
be\href{http://www.techdirt.com/articles/20070115/163130.shtml}{SOX}ed
imbeciles that set IT policies will not rest until it's impossible to do
useful work on \emph{corporate assets} and people wonder why there is so
little return on IT investment.

Living without Dropbox and its many peers is annoying but tolerable
provided humble USB ports are still useful but restricting plug-in
drives is now \textbf{\emph{standard not-operating procedure}} in
most companies. So if you cannot share files or use USB what's left?
Would you believe \href{https://github.com/}{GitHub}?

GitHub is close to total global dominance in the geeky code sharing
world. I would not have expected a version control system
to attract a fiercely loyal and dedicated cult following but it has.
Linus Torvalds, the Linux demigod, started
\href{http://git-scm.com/}{Git} when he \emph{correctly observed} that
all pre-Git version control system were fundamentally flawed because
they \emph{enshrine the overlord peon hierarchy.} The overload, usually
some IT nitwit, \emph{manages} the entire code submission, review and
backup process and the peons, that would be us, bend over take it. Until
Git appeared the majority of programmers despised and detested version
control. It was just more IT management bullshit. We put up with it
because version control is a necessary evil and paychecks are even more
necessary evil. We only wished things could be
\href{http://www.youtube.com/watch?v=w27meg0YfEU}{less evil} and then
Git appeared.

Git dumped the overlord peon hierarchy and adopted the radical notion
that all repositories are created equal. When you synchronize Git
repositories \emph{everything is synchronized.} Your local copy contains
everything the source does. This makes Git a superb peer-to-peer file
distribution tool. Not only are you distributing files you're also
distributing their complete histories. This, almost biological
replication model, has resulted in an explosion of Git repositories and
the rise of hub sites like GitHub. Git's dominance would not be possible
if it was centrally managed. It's succeeded because it's harnessed
market chaos.

I've used Git for over a year and I have often thought about pushing
\href{http://bakerjd99.wordpress.com/the-jod-page/}{JOD} source to
public repositories. This weekend I bit the bullet and set up
\href{https://github.com/bakerjd99}{public repositories.} Now it's easy
to \href{http://www.youtube.com/watch?v=2UbtcmjfKa8}{Git me a Hub'bery!}



%\end{document}