%\input{bmamble.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2018/01/21/government-shutdown-and-rapture-2018/}{Government Shutdown and Rapture 2018}}
\addcontentsline{toc}{subsection}{Government Shutdown and Rapture 2018}


\noindent\emph{Posted: 21 Jan 2018 21:43:58}
\vspace{6pt}

It's 2018. 2018 has prime factors of 2 and 1009, e.g. $2018 = 2 \times 1009$.

\medskip

Did anything happen in the years 2 and 1009?

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  \href{https://www.onthisday.com/events/date/2}{In the year 2} Venus
  and Jupiter were in conjunction. Some speculate this may have been the
  ``Star of Bethlehem.''
\item
  \href{https://www.onthisday.com/events/october/18}{In 1009} the Church
  of Holy Sepulcher was destroyed.
\end{enumerate}

How odd, the prime factors of 2018 yield two Jesus related events,
separated by over a thousand years that are mysteriously tied to his
birthplace. Evidently, the Star of Bethlehem marked the beginning, 1009
marked the middle, and 2018 is the end! \emph{Repent, the rapture is
upon us!} Better buckle up non-gender specific bovine control officers
(cowboys) 2018 is going to be rough.

Just how rough you ask? Imagine hordes of underachieving and mostly
useless bureaucrats forced to take an impromptu paid
holiday\footnote{None of the furiously furloughed will miss a single damn paycheck.
 Where can I get a job that pays me to sit on my ass and whine about
 whatever the idiot talking point of the day
 is?
} because even more
useless legislators cannot agree on how to spend other people's money.
Let's hope the government stays shutdown down until the imminent rapture
renders it redundant.

My calculations cannot pinpoint the exact time and date of the rapture.
My guess would be the first\footnote{2018 has two total lunar eclipses. If we're not
 raptured on January 31\textsuperscript{st} wait until
 \href{https://eclipse.gsfc.nasa.gov/LEplot/LEplot2001/LE2018Jul27T.pdf}{July
 27\textsuperscript{th}}
}
\href{https://eclipse.gsfc.nasa.gov/LEplot/LEplot2001/LE2018Jan31T.pdf}{blood
moon of the year, January 31, 2018}. Get your affairs in order and
divest yourself of your worldly
bitcoins.\footnote{Sky Fairy consultants, also known as prophets, have high overhead and
 need substantial donations to maintain their close connections with
 the divine.
} Use the address
encoded in the QR graphic of this blog.

\medskip

\emph{Hey: If you think this micro-epiphany is batshit crazy}
\href{https://endtimesforecaster.blogspot.com/2018/01/the-rapture-theorem-proving-blood-moon.html}{\emph{take
a look at this!}} \emph{It's getting to the point where it's no longer
possible to be satirical because somewhere on the intertubes you'll find
true believers that go way beyond satire.}

%\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

%\begin{enumerate}
%\item
%  \hypertarget{fn1}{}
%
%  None of the furiously furloughed will miss a single damn paycheck.
%  Where can I get a job that pays me to sit on my ass and whine about
%  whatever the idiot talking point of the day
%  is?\protect\hyperlink{fnref1}{↩}
%\item
%  \hypertarget{fn2}{}
%
%  2018 has two total lunar - blood moon - eclipses. If we're not
%  raptured on January 31\textsuperscript{st} wait until
%  \href{https://eclipse.gsfc.nasa.gov/LEplot/LEplot2001/LE2018Jul27T.pdf}{July
%  27\textsuperscript{th}}\protect\hyperlink{fnref2}{↩}
%\item
%  \hypertarget{fn3}{}
%
%  Sky Fairy consultants, also known as prophets, have high overhead and
%  need substantial donations to maintain their close connections with
%  the divine.\protect\hyperlink{fnref3}{↩}
%\end{enumerate}



%\end{document}

