%\input{bmamble.tex}

\subsection*{\href{http://bakerjd99.wordpress.com/2009/10/29/hard-ass-skeptic-rules/}{Hard Ass Skeptic Rules}}
\addcontentsline{toc}{subsection}{Hard Ass Skeptic Rules}


\noindent\emph{Posted: 29 Oct 2009 14:05:06}
\vspace{6pt}

I am a hard ass skeptic. A hard ass skeptic is somebody that holds:

\begin{enumerate}
\item
  Ghosts do not exist
\item
  Gods do not exist
\item
  UFOs are not alien spaceships
\item
  There are no Yetis
\item
  There are no psychics
\item
  9/11 was not an inside job
\item
  Life after death is nonsense
\item
  Reincarnation is more nonsense
\item
  Somebody called Christ did not rise from the grave
\item
  Mohammed did not ascend to heaven
\item
  The world will not end in 2012
\item
  Heaven and Hell do not exist
\item
  You cannot build a Good and Evil meter
\end{enumerate}
Hard ass skeptics are often accused of being sour, bitter, judgmental
\emph{know-it-alls} by the usual crew of credulous buffoons. Cry me a
river people! No matter how many idiotic ghost hunting shows you put on
the history channel you are never going to convince a hard ass skeptic
that ghosts exist. Just so we can all get along I am going to disclose
how you can win an argument with a hard ass skeptic.

The key to marketing ideas to hard ass skeptics is to understand what
hard ass skeptics consider valid arguments. Hard ass skeptics will
consider only two types of arguments:

\begin{enumerate}
\item
  Mathematical proof
\item
  Hard science
\end{enumerate}
If you cannot couch your argument in these terms just shut the fuck up.
You are wasting your breath and the hard ass skeptic's time.

I know this is harsh but it gets worse. Mathematicians and scientists
make mistakes: lots and lots of mistakes. How does the hard ass skeptic
deal with this \emph{inconvenient} truth? The typical hard ass skeptic
simply doesn't have enough time, skill or expertise to filter the
rubbish from the rubies. \textbf{\emph{So the hard ass skeptic assumes
it's all crap until there is verified overwhelming evidence to the
contrary.}}

Finally, hard ass skeptics \emph{put the burden of proof on a
supposition's supporters.} It's not the hard ass skeptic's job to prove
you are wrong. It's your job to prove, beyond any reasonable
mathematical or scientific doubt, you are correct. So please stop
whining about how we haven't proved that psychics, Yetis or Heaven do
not exist. It's not our job and it never will be.


%\end{document}