%\input{bmamble.tex}

\subsection*{\href{https://analyzethedatanotthedrivel.org/2020/06/29/how-do-you-check-your-vote/}{How Do You Check Your Vote?}}
\addcontentsline{toc}{subsection}{How Do You Check Your Vote?}


\noindent\emph{Posted: 29 Jun 2020 17:35:45}
\vspace{6pt}

\emph{How do you check your vote?}

It's a simple question with a simple disturbing answer.

\emph{You cannot check your vote!}

And when I say ``you'' I mean you. I don't mean the system, the
authorities, electoral officials, foreign auditors, or any third
party\emph{. I mean you - just you.}

There isn't an electoral system on Earth that allows voters to check
their votes. Americans cannot check their votes. Canadians cannot check
their votes. Germans cannot check their votes. ~Indians cannot check
their votes. The same holds for the British, the Japanese, the Koreans,
the Australians, the French, and the Danes. Everywhere people cast
ballots they are denied the means to \emph{personally} check them.
Amazingly, billions of people all over the world go through the motions
of voting without demanding a rigorous system to check their votes and
assess the integrity of their elections.

Well this is planet moron!

``Oh, come on,'' cried
\href{https://www.dictionary.com/e/slang/karen/}{Karen}. ``Surely you
can trust law-abiding and well-ordered electoral systems to properly
count ballots? ~And, aren't you undermining the public's confidence in
the \emph{democratic process} by demanding ways to verify votes? Are you
a crypto-fascist?~ An Asian supremacist?~ A wife beater? Do you want the
terrorists to win? Do you eat black puppies?''

Let's all calm down and look at the ``checking your vote problem'' with
\href{https://analyzethedatanotthedrivel.org/2018/05/08/informed-naked-ape-protocol/}{Informed
Naked Ape Protocol} (iNap) in mind.~ When you cast your vote \emph{you
are forced to trust the electoral system}. Informed Naked Ape Protocol
has much to say about trust.

\begin{quote}
\emph{iNap \#9: If you don't control it you cannot trust it.}
\end{quote}

I don't control the electoral system in the United States. I didn't
control it in Canada either. \emph{If you don't personally and
absolutely control a thing you can never trust it.} I've voted in
American and Canadian electoral systems and trusted neither because:

\begin{quote}
\emph{iNap \#2: Trust is for imbeciles.}
\end{quote}

``Oh, John you're so negative, so cynical, so filled with bitterness.''

It gets worse.

\begin{quote}
\emph{iNap \#4: Assume corruption.}
\end{quote}

It's wise to assume that \emph{any system you deal with is corrupt.}
Corruption is the default state. Things are either innocently or
intentionally fucked up until there are deep, open, and relentlessly
verified scientific arguments to the contrary.

\begin{quote}
\emph{iNap \#7: Practice relentless verification.}

\emph{iNap \#10: Only scientific and mathematical arguments are admissible.}
\end{quote}

How can I analyze the integrity of Idaho's electoral system? I would
need unfettered access to state voter registrations, paper ballots,
voting machine memories, and electoral officials. I would have to
personally inspect every component of the entire system to pass
judgment. I lack such access and so do you. Don't pretend otherwise.
\emph{You cannot verify the integrity of your electoral system.} Once
again you are forced to trust and as I've said before and will repeat
until my dying day:

\begin{quote}
\emph{iNap \#2: Trust is for imbeciles.}
\end{quote}

It's time to stop \emph{believing} in electoral systems because that is
precisely what we are doing. We believe our systems are sound yet
tolerate their inability to meet basic needs like personal vote
checking. Would you \emph{believe} your money was safe in bank that
didn't let you check account balances? Well imbeciles, that's what
you're doing when you vote! Belief in anything is a giant red flag
because:

\begin{quote}
\emph{iNap \#3: ``Belief'' is a bullshit word.}
\end{quote}

All modern voting systems are broken. Without a sound open source
mathematically rigorous means of checking personal votes and verifying
vote aggregates elections are nothing more than cynical and insulting
public relations spectacles
\href{https://www.poetryfoundation.org/poems/56964/speech-tomorrow-and-tomorrow-and-tomorrow}{``full
of sound and fury and signifying nothing.''}

Yes, Karen, all our electoral systems are broken but they don't have to
be. It's entirely possible, indeed \emph{technically trivial}, to create
voting systems that:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Count only registered votes.
\item
  Permit voters to check their votes.
\item
  Allow full secure public vote aggregation verification.
\item
  Satisfy the highest standards of public disclosure and scrutiny.
\end{enumerate}

\begin{quote}
\emph{iNap \#6: Demand full analytic disclosure.}
\end{quote}

In the next few posts, I will outline such a system. We know how to do
this; the creators of block-chains and public-key cryptography have
already done all the hard work. We could have much better electoral
systems up and running in months. Major obstacles are not technical;
they are entirely political.



%\end{document}
