%\input{bmamble.tex}

\subsection*{\href{https://analyzethedatanotthedrivel.org/2018/05/17/inap-1-enough-people-are-scum/}{iNap \#1: Enough People are Scum}}
\addcontentsline{toc}{subsection}{iNap \#1: Enough People are Scum}


\noindent\emph{Posted: 17 May 2018 20:45:27}
\vspace{6pt}

Intelligible systems are built on a few basic
principles.\footnote{The human preference for systems with a few axioms is an artifact of
  our primitive intellects. There are few if any human beings that would
  be comfortable with axiomatic theories that depend on trillions of
  independent axioms yet we know that such systems exist and remain
  incomplete. Our drive to reduce things to a manageable set of rules,
  even when we know it is naïve and futile, amounts to little more than
  thumb-sucking. It makes our baby brains happy even if it will not
  solve our problems.
} While reducing
my dour skepticism to the memorable maxims that codify
\href{https://analyzethedatanotthedrivel.org/2018/05/08/informed-naked-ape-protocol/}{\emph{Informed
Naked Ape Protocol}}. I repeatedly asked myself what animates unflagging
skepticism? What turns naturally cheerful and optimistic people like
myself into raging cynics? What motivates
\href{https://www.lifewire.com/types-of-internet-trolls-3485894}{noble
trolls} to put down the pizza and grab the keyboard? \emph{Only one
answer sprang to mind: other people.}

Regardless of your politics, gender, education, race, age, nationality,
or ethnicity, you have probably noticed there are a lot of scummy people
out there.

Why is this?

The answer derives from our evolution. Evolutionary advantages often
accrue to individuals that cheat. Cheating is a fundamental behavioral
adaptation that has been observed in many animal, bird and plant
species\emph{. \textbf{Cheating is so common that cheating the system is
the system!}} How cheaters might benefit was best illustrated in the
hilarious
\href{https://www.imdb.com/name/nm0315041/?ref_=tt_ov_dr}{Ricky Gervais}
movie \href{https://www.imdb.com/title/tt1058017/}{The Invention of
Lying}. In Ricky's world, everybody told the truth until one day he
discovered that you could lie. The best scene in the film has Ricky
running into a beautiful woman on the street. He tells her that the
world is doomed unless she immediately agrees to have sex with him.
Given the dire circumstances, she instantly agrees to save the world.
Clearly, liars are going to enjoy immense reproductive success in a
world of truth tellers. Similarly, scumbags will profit in a world of
purely honorable people.

We don't live in a world of purely honorable people or purely scummy
people. Human scum density is complicated; it depends on more variables
than the weather. Nevertheless, we can infer that human scum density is
\emph{seldom zero} and is \emph{often appreciable}.

How big is appreciable?

My bitter sampling of humanity yields an estimate of approximately 0.05
for contemporary American
society.\footnote{Yes, human scum density varies with culture. Some societies are
  briefly more virtuous than others.
} It's definitely bad
news that 5\% of the people around you cannot be trusted or depended on.
It's even worse news that human scum, like pond scum, often floats to
the upper echelons of society. This is a nasty reality and I wish it
wasn't so but reality is often unpleasant and leaves few options: either
adapt or be crushed.

The first step in adapting to scummy naked apes is acknowledging the
most fundamental fact about them --- \emph{enough people are scum!}


%\end{document}

