%\input{bmamble.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2018/05/08/informed-naked-ape-protocol/}{Informed Naked Ape Protocol}}
\addcontentsline{toc}{subsection}{Informed Naked Ape Protocol}


\noindent\emph{Posted: 08 May 2018 19:09:28}
\vspace{6pt}

Many think we are living in a golden age of bullshit. That public
discourse has never been gaudier or more demeaning. That respect for
truth and decency has reached all-time lows. The mental pygmies that
hold these opinions don't read or think for themselves. Deceiving
ourselves and others is the one thing our species excels at. Lies are
the bedrock of art, economics, politics, and religion. Only two tiny
slivers of human thought have ever breached the bullshit barrier and
approached something that might be credibly labeled truth: hard science,
and harder mathematics.

If you think I am going to praise brave men, (and bitches), of science
for lighting a candle in the perpetual darkness, (Carl Sagan already
wrote
\href{https://www.goodreads.com/book/show/17349.The_Demon_Haunted_World}{an
entire fawning book} on this self-aggrandizing theme), think again.
Scientists are just as flawed and full of crap as the rest of us.
Science occasionally succeeds because it has evolved protocols that
correct for human bullshit. A good protocol protects us against our
worst enemy --- ourselves.

My \emph{Informed Naked Ape Protocol}, or \emph{iNap} for short,
consists of eleven\footnote{Why eleven? The last time somebody tried to get the inhabitants of
  planet moron to follow ten simple rules it didn't work
  out.
} pithy
maxims that force a
\href{https://analyzethedatanotthedrivel.org/2009/10/29/hard-ass-skeptic-rules/}{hard
ass skeptical} view of things. I will manifest my maxims here and
elaborate on each one in following posts.

\bigskip

\emph{Informed Naked Ape Protocol}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  Enough people are scum.
\item
  Trust is for imbeciles.
\item
  ``Belief'' is a bullshit word.
\item
  Assume corruption.
\item
  Analyze the data, not the drivel.
\item
  Demand full analytic disclosure.
\item
  Practice relentless verification.
\item
  Centralized systems are always corrupted.
\item
  If you don't control it you cannot trust it.
\item
  Only scientific and mathematical arguments are admissible.
\item
  Correct errors.
\end{enumerate}

%\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

%\begin{enumerate}
%\item
%  \hypertarget{fn1}{}
%
%  Why eleven? The last time somebody tried to get the inhabitants of
%  planet moron to follow ten simple rules it didn't work
%  out.\protect\hyperlink{fnref1}{↩}
%\end{enumerate}



%\end{document}
 