%\input{bmamble.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2013/09/02/i-write-my-congresswoman-about-syria/}{I write my Congresswoman about Syria}}
\addcontentsline{toc}{subsection}{I write my Congresswoman about Syria}


\noindent\emph{Posted: 02 Sep 2013 05:09:58}
\vspace{6pt}

\begin{quote}
\emph{I just emailed this to my Congresswoman, Ann Wagner,
2\textsuperscript{nd} district Missouri. I'm going to make sure I'm
on~the NSA's naughty malcontent list.}
\end{quote}

\noindent Dear Ann,

\medskip

Your summer vacation from Congress is coming to an end. Soon you will be
back in Washington dealing with all our little problems like:
\href{http://www.usdebtclock.org/}{runaway deficit financing},
relentless FED driven currency debasement, rampant illegal immigration
and, finally, what to do about Syria.

You're probably surprised that the Obama administration punted on Syria
and threw you this hand grenade. By now you've noticed that the
\emph{Light-Bringer's} administration only goes to Congress to steal or
print more money, debt limit, ram through hideous partisan, ``have to
pass it to find out what's in it,'' bills, Obamacare, or get begrudging
constitutionally mandated approval for political appointee hacks.
\emph{Of course Obama despises Congress. It's the most American thing
about him.}

Ann, you're from Missouri, so you probably know that Missouri's most
famous native son, Mark Twain, maintained a complete and robust contempt
for the institution you belong too.

\begin{quote}
\emph{Suppose you were an idiot, and suppose you were a member of Congress;
but I repeat myself.}

\emph{Mark Twain}
\end{quote}

No one has characterized the simpering idiocy of Congress better. Mark
did not suffer fools well and he certainly wasn't naive or stupid enough
to believe his congressman, or congresswoman, \emph{actually represented
him.}

Ann, I'm afraid I share Mark's bleak view, but just for the sake of
argument, let's assume you do represent me. I did vote for you. And, as
I recall, I didn't have to hold my nose or look down ballot for my
default, ``anyone but that shithead,'' option. I actually felt you were
the best person for the job. That you've kept out of the news, no sex
scandals, no outrageous pork projects, no hysterical CSPAN fits, no
public bitch slapping and no DUIs\footnote{
We set a very low bar for Congress.
} makes me think you're actually a decent human being even though you
associate with known felons.

\medskip

\emph{Well as one decent human being to another I am asking you to vote
no on any motion that authorizes the use of force in Syria.}

\medskip

I'd bet that I know far more about the Middle East than you or the vast
majority of your peers in Congress. I lived in Iran and Lebanon. I was
evacuated from Beirut during the 1967 Arab Israeli War. I'm married to
an Iranian refugee. She had to flee her native country after protesting
Khomeini's thugs in the early 1980's. The Middle East is not a TV
reality show for me. When I hear of bombs falling in the Beqaa valley I
think about how I camped down the road.

When I say there are no good options in Syria I not running off
teleprompter. On one side you have Assad's Ba'athist criminals:
essentially modern Nazis. That delusional dolts like your colleague,
Nancy Pelosi, thought Assad
\href{http://www.nationalreview.com/articles/312450/assads-useful-idiots-noah-glyn}{was
a reformer} is partly why we think you're all morons. Opposing Assad is
a rag-tag coalition of rebels, Islamists and
\href{http://www.bbc.co.uk/news/magazine-23190533}{crazy cannibal}
Jihadists. This is a war that both sides deserve to lose. Firing a few
cruise missiles into this mess is not going to alter the outcome or
elevate the world's low opinion of Americans. All it will do is add more
legions of US hating Middle Easterners to what's already a vast throng.

Ann, how would you feel if some inept clueless foreign power lobbed a
few drone missiles into Saint Louis neighborhoods because they objected
to local law enforcement? I'm pretty sure you'd be livid: boiling with
incandescent rage. Imagine how your mood will improve when you learn the
attack was
\href{http://www.thedailybeast.com/articles/2013/08/31/is-obama-going-to-war-just-to-check-the-box.html}{calibrated
to avoid mockery}. Would you feel a new-found respect for the bombers?
I'm guessing your new life's work would be striking back. This is what
our remote control war is doing. It's creating far more enemies than it
kills.

Ann, do you really want to be a part of this? What we are doing is
catastrophically stupid and has to stop. Vote no on Syria.

\medskip

\noindent Respectfully, I'm not kidding, yours

\noindent John Baker Saint Louis County

%\end{document}