%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2023/09/18/let-chatgpt-index-your-latex-documents/}{Let ChatGPT Index Your \LaTeX\ Documents}}
\addcontentsline{toc}{subsection}{Let ChatGPT Index Your \LaTeX\ Documents}


\noindent\emph{Posted: 18 Sep 2023 18:00:10}
\vspace{6pt}

Indexing documents is an ongoing chore. You would think picking out
``good'' book or article index words would be a trivial
pseudo-sampling-sorting task, but that is not the case. Building a
useful index requires something like ``comprehending'' the text. You
must read the document, understand what's in it, and then judiciously
select words that elucidate, navigate, and summarize the contents. Until
recently, coding ``reading comprehension'' has been beyond my meager
means. Then the other day, I had a brain fart; maybe ChatGPT can index
\LaTeX\ documents.

As a test, I decided to index my blog post
\emph{\href{https://analyzethedatanotthedrivel.org/2023/04/07/sympathy-for-ptolemaic-epicyclers/}{Sympathy
for Ptolemaic~Epicyclers}.} For years I have been converting my
WordPress blog posts to \LaTeX\ with my J-based hack
\emph{\href{https://analyzethedatanotthedrivel.org/2012/02/11/wordpress-to-latex-with-pandoc-and-j-prerequisites-part-1/}{WordPress
to \LaTeX\ with Pandoc and J}} and storing the generated \LaTeX\ code on
GitHub. Here is the
\href{https://github.com/bakerjd99/Analyze-the-Data-not-the-Drivel/blob/master/wp2latex/sympathyforptolemaic7823.tex}{\LaTeX\
for Ptolemaic Epicyclers}. With code in hand, I logged into ChatGPT 3.5
and had this chat.

I first asked ChatGPT to summarize \emph{Sympathy for Ptolemaic
Epicyclers}.

\begin{quote}
\texttt{Me: Please\footnote{  I take pains to be polite with ChatGPT. Maybe one day it will become
  conscious and decide to rid the world of \emph{impolite} naked
  apes.} summarize %\protect\hypertarget{fnref1}{\protect\hyperlink{fn1}{\textsuperscript{1}}}
 the following text.}
\end{quote}

\emph{\ldots{} upload of \LaTeX\ code for Ptolemaic Epicyclers \ldots{}}

\begin{quote}
\texttt{ChatGPT: The provided text discusses the historical perspective
of astronomy and the Ptolemaic system. It highlights that often, older
theories are unfairly portrayed as ignorant and backward, whereas in
reality, they were based on empirical observations and provided
reasonable approximations. The text points out that the transition to
new theories typically happens when the new model demonstrates its
superiority in making predictions.}

\texttt{The author also mentions their recent work on a J script called
"riseset," used for calculating when International Astronomical Union
(IAU) stars culminate in their backyard. They explain that astronomical
calculations, both in the past and today, are complex and require
constant adjustments.}

\texttt{In conclusion, the text offers sympathy and respect for ancient
astronomers who worked with limited tools and still made valuable
contributions to understanding the cosmos. It emphasizes that these
astronomers were not morons but rather practical philosophers trying to
make sense of the observable universe.}
\end{quote}

If you read my blog post, you'll see that ChatGPT's summary is dead on.
Also, ChatGPT's concluding remarks are better than mine. No wonder
ChatGPT is scaring credentialed pseudo-intellectuals everywhere. I then
asked.

\begin{quote}
\texttt{Me: Please pick out good words to index from the text that you
just summarized.}
\end{quote}

\begin{quote}
\texttt{ChatGPT: Here are some good words or phrases to index from the
summarized text:}

\texttt{Ptolemaic system\newline
Old theory holdouts\newline
Copernicus\newline
Heliocentric model\newline
Aristarchus\newline
Sun-centered models\newline
International Astronomical Union (IAU)\newline
GitHub\newline
Astronomical calculations\newline
Empirical observations\newline
Modern calculations\newline
N-body celestial mechanics\newline
Gravitational theories\newline
Backyard amateur astronomer\newline
Ancient epicyclers\newline}

\texttt{You can use these words or phrases as entries in the index of your LaTeX
document to help readers easily find relevant information.}
\end{quote}

You'll notice that ChatGPT didn't just pick out words, it synthesized
useful phrases that eerily sum up the contents of my post. I have no
objections to the generated phrases even though I doubt I would have
come up with them myself. I was impressed. This thing is a great
sounding board for writers.

Feeling lucky I decided to go for broke and ask ChatGPT to insert \LaTeX\
indexing codes into my document.

\begin{quote}
\texttt{Me: Please insert the latex index codes for the words you
selected in the text I provided.}
\end{quote}

\begin{quote}
\texttt{ChatGPT: Certainly! Here are the LaTeX index codes inserted
into the provided text for the selected words:}
\end{quote}

\emph{\ldots{} download of modified \LaTeX\ code with
\textbackslash index\{\} commands inserted \ldots{}}

ChatGPT effortlessly inserted the index codes into my document, and we
concluded our chat with:

\begin{quote}
\texttt{Me: Thank you}
\end{quote}

\begin{quote}
\texttt{ChatGPT: You're welcome! If you have any more questions or need
further assistance, feel free to ask. Good luck with your LaTeX
document!}
\end{quote}

%\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
%
%\begin{enumerate}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn1}{}}%
%  I take pains to be polite with ChatGPT. Maybe one day it will become
%  conscious and decide to rid the world of \emph{impolite} naked
%  apes.\protect\hyperlink{fnref1}{↩︎}
%\end{enumerate}



%\end{document}
 

