%\input{bmamble.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2012/12/24/lets-trade-constitutional-amendments/}{Let's Trade Constitutional Amendments}}
\addcontentsline{toc}{subsection}{Let's Trade Constitutional Amendments}


\noindent\emph{Posted: 24 Dec 2012 22:28:45}
\vspace{6pt}

I'm a big fan of stark choices. Stark choices push trivialities aside,
expose underlying problems and bring hidden motivations to light. There
is nothing more satisfying than watching well nursed notions
self-destruct when reduced to stark choices. Here's a stark choice our
corrupt ruling class will never put on ballots, or discuss, or dare
mention.

\begin{quote}
We can continue riding our gun-toting financial train wreck or we can
repeal the Second Amendment, the right to bear arms, and substitute a
Balanced Budget Amendment in its place.
\end{quote}

Citizens lose the right to bear arms and government loses the right to
borrow and print money. To my tiny programmer brain this seems like a
completely \href{http://www.globalexchange.org/programs/fairtrade}{fair
trade.} The Second Amendment was never about creating a safe cozy
society. It was all about safe-guarding liberty; it still is. Today, the
biggest threat to the liberty of Americans is our own government. If it
was cut down to a fiscally sustainable size the need for firearms, to
shoot the bastards in DC, would dramatically subside and then all of us,
left,
right, \href{http://public.web.cern.ch/public/en/science/standardmodel-en.html}{up,
down, top and strange} could join hands for one big happy
\href{http://www.urbandictionary.com/define.php?term=kumbaya}{Kumbaya-a-thon.}

Yeah I didn't think so.

Still it's fun to play these mind games. If by some miracle, and I'm
talking Red Sea parting here, my amendment swap ever got serious
consideration, it would be amusing to watch the partisan
cockroaches\footnote{
  My apologies to cockroaches. You are fine upstanding arthropods while
  political partisans barely reach the level of toxic
  waste.
} run for cover.

For the left the primacy of the state is everything. Gun control is far
more about control than it is about guns and public safety. Faced with
the dramatic curtailment of largely wasteful government social programs,
a logical consequence of balanced budgets, your typical lefty would
happily accept one, two, three, maybe more kindergarten massacres per
year to keep their beloved entitlements flowing.

As for the gun rights crowd: many of them clamor for balanced budgets
but I suspect many would go all, ``deficits don't matter,'' if they had
to cough up their beloved 9mm pistols, sawed off shotguns and AR-15's.

There is very little intellectual honesty or creativity on either side
of this debate and I'm tired of it. If we don't fall off the damn fiscal
cliff I'm going push your dumb asses over it. Have a merry freaking
Christmas and a less miserable New Year!


%\end{document}