%\input{bmamblenew.tex}

\subsection*{\href{https://analyzethedatanotthedrivel.org/2022/08/08/managing-a-sqlite-database-with-j-part-2/}{"Managing" a SQLite Database with J (Part 2)}}
\addcontentsline{toc}{subsection}{"Managing" a SQLite Database with J (Part 2)}


\noindent\emph{Posted: 09 Aug 2022 04:58:06}
\vspace{6pt}

When faced with unfamiliar program code
\href{https://rogerhui.rip/}{Roger Hui}, the cocreator of the
\href{https://code2.jsoftware.com/wiki/Main_Page}{J Programming
Language} would sometimes wipe out all the code comments. He told me
this forced him to concentrate on the actual code and not the
\emph{opinions} of previous developers. Roger was an exceptional
programmer; he knew that program comments are often dated, misleading
and wrong. And, the only way to ``correct the comments'' is to read the
code; so why not just read the code and skip the philosophy? Roger's
comment purges underscore an important point. However you document your
code, \emph{it must be better than the null or empty document.}

With this in mind, I wrote a few versions of this post, but I hated them
all. Then I realized that
\href{https://github.com/bakerjd99/jacks/blob/master/jodliterate/UsingJodliterate.pdf}{\texttt{jodliterate}}
PDF documents \emph{mostly} do what I want. So, instead of rewriting
\href{https://github.com/bakerjd99/jacks/blob/master/mirrorxref/MirrorXref.pdf}{\texttt{MirrorXref.pdf}},
I will make a few comments about jodliterate group documents in general.
If you're interested in using
\href{https://sqlite.org/index.html}{SQLite} with J, download the
self-contained
\href{https://github.com/bakerjd99/jacks/tree/master/mirrorxref}{GitHub
files \texttt{MirrorXref.ijs} and \texttt{MirrorXref.pdf}} and have a look.

%\hypertarget{jodliterate-group-documents}{%
\subsubsection*{jodliterate Group Documents}%\label{jodliterate-group-documents}}

jodliterate group documents are directly generated from
\href{https://analyzethedatanotthedrivel.org/the-jod-page/}{JOD
dictionaries} using J, \href{https://pandoc.org/}{pandoc}, and \LaTeX.
Group documents have three major parts.

\begin{enumerate}
\tightlist
\item
  An overview.
\item
  Complete typeset source code.
\item
  A global word index.
\end{enumerate}

The source code and index sections are self-explanatory, but a few
remarks about overviews are warranted.

The overview might have several subsections. There's usually a
hyperlinked \textbf{Interface} subsection. J doesn't have formal
interfaces like many programming languages. The words listed in the
\textbf{Interface} section are words you will use when running the
script. The \textbf{Interface} section highlights where to get started.

For complex scripts, there is usually a \textbf{Using} subsection.
\href{https://github.com/bakerjd99/jacks/blob/master/mirrorxref/MirrorXref.pdf}{\texttt{MirrorXref.pdf}}'s
\textbf{Using} subsection is typical.

Finally, there might be a \textbf{Code Hints} subsection. Code Hints are
lists of hyperlinked words that you should heed.

For more, take Roger's advice and read the code.


%\end{document}
 

