%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2024/03/17/math-eras/}{Math Eras}}
\addcontentsline{toc}{subsection}{Math Eras}


\noindent\emph{Posted: 17 Mar 2024 18:36:37}
\vspace{6pt}

As part of a larger project, I needed a simple timeline for the history
of mathematics. I kicked around a bunch of candidates but settled on the
following:

\begin{enumerate}
\tightlist
\item
  Old Tally --- before 4000 BCE
\item
  Bronze River --- 4000 BCE to 1001 BCE
\item
  Early Philosophic --- 1000 BCE to 301 BCE
\item
  Euclidean --- 300 BCE to 599 CE
\item
  Medieval Zero --- 600 CE to 1499 CE
\item
  Gutenberg --- 1500 CE to 1799 CE
\item
  Protoformal --- 1800 to 1949
\item
  Turing --- 1950 to present
\item
  AIM --- future, when AIs eclipse human mathematicians.
\end{enumerate}

Like all timelines, this one is entirely arbitrary. Its primary function
is to impose document structure and provide handy bins for sorting
material. While this timeline is arbitrary, it is not without
justification. Here are my admittedly questionable reasons for each
period.

%\hypertarget{old-tally-before-4000-bce}{%
\subsubsection*{Old Tally --- before 4000 BCE}%\label{old-tally-before-4000-bce}}

Only a handful of surviving authentic mathematical artifacts can be
dated to periods before 4000 BCE. The most famous are notched bones like
the
\href{https://maa.org/press/periodicals/convergence/mathematical-treasure-ishango-bone}{Ishango}
and \href{https://mathworld.wolfram.com/LebomboBone.html}{Lebombo}
bones. In addition to bones, we also have artworks and tools showing
people in the Old Tally period share our affinities for symmetry and
balance. We also find many earthworks and
\href{https://muze.gov.tr/muze-detay?sectionId=SGT01\&distId=SGT}{impressive
monuments} that reflect a basic grasp of geometric principles. You
cannot infer much about Old Tally mathematics from such artifacts.
Still, Old Tally people matched, counted, estimated distances, compared
quantities, and appreciated symmetries long before anything resembling
``civilization'' appeared. Tally is another word for counting. There has
never been a human culture without some form of counting, so it's safe
to assume our long-dead ancestors counted.

%\hypertarget{bronze-river-4000-bce-to-1001-bce}{%
\subsubsection*{Bronze River --- 4000 BCE to 1001 BCE}%\label{bronze-river-4000-bce-to-1001-bce}}

The Bronze River Era gets its name from the many prominent Bronze Age
civilizations that sprung up near major historic rivers, with the most
famous being the Nile, Tigris, Euphrates, Indus, Yellow, and Yangtze
Rivers. During the Bronze Age, Egyptian, Mesopotamian, Indic, and
Chinese cultures developed sophisticated, practical problem-solving
mathematics. Bronze River mathematicians dealt with many accounting,
surveying, and astronomical calculations. They tackled area and volume
calculations, solved some linear and quadratic equations, extracted
roots, handled fractions, and computed loan interest. The largest number
of surviving Bronze River mathematical artifacts are Mesopotamian.
Mesopotamians wrote on durable cuneiform tablets, and many thousands of
them have survived. Hence, we know more about their mathematics than
other Bronze Age civilizations, but what survives from the others
indicates comparable levels of sophistication. I suspect there was more
contact between Bronze Age people than previously supposed. Humans are
highly mobile animals that cannot resist the urge to see what's over the
horizon.

%\hypertarget{early-philosophic-1000-bce-to-301-bce}{%
\subsubsection*{Early Philosophic --- 1000 BCE to 301 BCE}%\label{early-philosophic-1000-bce-to-301-bce}}

The seven centuries from the end of the Bronze River to the Euclidean
era saw something new develop in mathematics: an emphasis on
\emph{philosophical} proof. Proof, in an almost modern programming
language debugging sense, had long existed in mathematics.
Mathematicians of earlier eras constantly looked for ways to verify
their work. They checked and double-checked their calculations. They
came up with general schema to justify their complex methods and, in
some cases, produced convincing proofs of various assertions. The notion
that proof was a unique invention of the ancient Greeks is misleading.
Their unique innovation was more subtle. Debugging proof focuses on
exposing local errors and not constructing coherent, logical wholes. The
yearning for logical wholes is a philosophical tendency, not a practical
one. You do not need logical wholes to solve problems.

The poster boys for insisting on logical wholes were the Pythagoreans
and their titular sage, Pythagoras. Recently, Pythagoras has been
\href{https://analyzethedatanotthedrivel.org/2022/09/28/on-eponymous-erasure/}{denounced
by ignorant harpies} and diverse idiots as an uber-dead white male who
stole the work of the BIPOC'ky brown and passed it off as his own. This,
in Pauli's immortal words, ``Is not even wrong!'' We know very little
about the alleged person Pythagoras. We don't know his skin color, his
sexual orientation, his penis length, or perhaps \emph{her} vagina
depth. If you're going to slander someone, do your homework. But all of
this woke whining doesn't matter. Pythagoras may or may not have
existed, but the philosophical school taking his name did! The Romans
were bitching about the Pythagoreans centuries after Pythagoras's
alleged lifetime, so the school's attitudes and outlook certainly had an
impact. We know this because the very word ``mathematics'' derives from
one of the Pythagorean schools. The Pythagoreans and others persuasively
argued that it wasn't enough to check your homework; a deeper and more
comprehensive understanding was required. You needed coherent, logical
wholes. This change in outlook elevated the status of mathematical
proof. It was no longer a check or test of useful methods; it became the
rarest of things: a \emph{philosophical
necessity}\footnote{Philosophy is rarely associated with necessity.}.

%\hypertarget{euclidean-300-bce-to-599-ce}{%
\subsubsection*{Euclidean --- 300 BCE to 599 CE}%\label{euclidean-300-bce-to-599-ce}}

Once the philosophical necessity of proof was established, it was
probably only a matter of time before someone constructed a coherent,
logical whole. Euclid turned out to be that person, and his
\emph{Elements} was the logical whole. While there are arguments about
how much material in the \emph{Elements} dates to 300 BCE and how much
can be accurately attributed to its author, there are no arguments about
the importance of this singular work. The \emph{Elements} is easily the
most influential scholarly work in history. Its impact is only exceeded
by sky fairy manuals like the Bible, Koran, and Mahabharata. Euclid was
the first, as far as we know, to organize a large body of results into a
systematic, logical, deductive structure. You can quibble about the
\emph{Element's} defects and omissions (and many have), but the
\emph{Elements} created the theorem-proof world that mathematicians
still live in. The book's impact was so overwhelming that its style and
conventions set the tone for centuries.

%\hypertarget{medieval-zero-600-ce-to-1499-ce}{%
\subsubsection*{Medieval Zero --- 600 CE to 1499 CE}%\label{medieval-zero-600-ce-to-1499-ce}}

The Medieval Zero period was characterized by the rise of Algebra by
figures like al-Khwarizmi, the global spread of Indian place value
numbers, and the emergence of Zero. In the modern world, two numbers,
One and Zero, reign supreme. We could not do without them. It's ironic
that perhaps the most important of the two, Zero, took so long to be
appreciated. But, better late than never.

%\hypertarget{gutenberg-1500-ce-to-1799-ce}{%
\subsubsection*{Gutenberg --- 1500 CE to 1799 CE}%\label{gutenberg-1500-ce-to-1799-ce}}

It may seem strange to name a mathematical era filled with giants like
Descartes, Fermat, Newton, Leibniz, Laplace, Euler, Bernoulli, and many
more after a printer, but the giants would not have been so gigantic
without lowly movable print. You can see the impact of printing in the
enormous increase in mathematical documents after 1500. This is evident
in \href{https://maa.org/press/periodicals/convergence/index-to-mathematical-treasures}{The
Mathematical Treasures} list maintained by \emph{The Mathematical
Association of America}. The bulk of the entries appeared after 1500.

%\hypertarget{protoformal-1800-to-1949}{%
\subsubsection*{Protoformal --- 1800 to 1949}%\label{protoformal-1800-to-1949}}

It took me some time to come up with a polite name for this period. I
wanted to call it the age of bogus rigor, but that's a tad mean. From
1800 until well into the 20\textsuperscript{th} century, mathematicians
were anal about rigor. The advent of epsilontics and the driving out of
the infinitesimals had to happen. You cannot live in a theorem-proof
world without solid proofs, but in their zeal to banish all sloppy
thinking, they discovered that perfect formal proofs are horrendously
long and yet hopelessly incomplete. The idea that all mathematics could
be consistently constructed from a small set of axioms and a
sufficiently powerful set of deduction rules was shown to be impossible.
Some philosophical necessities cannot be realized.

%\hypertarget{turing-1950-to-present}{%
\subsubsection*{Turing --- 1950 to present}%\label{turing-1950-to-present}}

Naming our current era after Alan Turing was a no-brainer. Computers
have utterly transformed our world. Many mathematicians, being elite
establishmentarians, were slow to adjust. Some were on board almost as
soon as computers became available, but most held back. This is
changing. While it's not feasible to formalize vast swathes of
mathematics by hand, it's entirely possible with computers. We're
currently witnessing another shift in attitude about what's an
acceptable proof. In a few more years, mathematicians will be expected
to formalize new theorems. It will be seen as a tightening up of the
peer review process. It might even become a requirement for publishing
in major journals. It will be a brave new world.

%\hypertarget{aim-future-when-ais-eclipse-human-mathematicians}{%
\subsubsection*{AIM --- future, when AIs eclipse human mathematicians}%\label{aim-future-when-ais-eclipse-human-mathematicians}}

If you've been paying attention, you've probably noticed machines
slowly chipping away at human intellectual benchmarks. I'm old enough
to remember people saying machines would never beat the best Chess
players. Wrong. Then it was Go. Wrong. Then \emph{Jeopardy}. Wrong. Similarly,
they would never be able to converse fluently. Wrong. With each
advance, the goalposts are moved. Now, machines must demonstrate consciousness
(we can't do this for ourselves), speak a few dozen languages, play many
musical instruments, write novels, and prove deep theorems before we
call them intelligent. We are all in a state of AI denial, and
mathematicians, despite
\href{https://www.youtube.com/watch?v=CCCx1j8WsHU}{``being smarter than average bears,''}
are not exempt. I don't know when AIs will eclipse human beings at
finding and proving theorems, but I suspect it's only a matter of time.
It may be centuries (unlikely), but it will happen\footnote{I am assuming we don't nuke ourselves.}
and when it does, we enter the \textbf{AI} \textbf{M}athematician or AIM age.

%\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
%
%\begin{enumerate}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn1}{}}%
%  Philosophy is rarely associated with
%  necessity.\protect\hyperlink{fnref1}{↩︎}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn2}{}}%
%  I am assuming we don't nuke ourselves.\protect\hyperlink{fnref2}{↩︎}
%\end{enumerate}


%\end{document}
 
