%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2022/12/20/mission-statements-for-this-blog/}{Mission Statements for this Blog}}
\addcontentsline{toc}{subsection}{Mission Statements for this Blog}


\noindent\emph{Posted: 20 Dec 2022 22:41:44}
\vspace{6pt}

I have a weakness for \emph{how to improve your writing}
books.\footnote{This blog clearly shows I need all the help I can get.
} Lately, I've been reading
\href{https://www.amazon.com/Writing-Tools-Essential-Strategies-Writer/dp/0316014990}{\emph{Writing
Tools}} by Roy Peter Clark. \emph{Writing Tool}s is full of useful
advice that I will make efforts to heed. Clark's Tool 40 motivated this
post.

Tool 40 advises writers to craft short \emph{mission
statements}\footnote{  Corporate \emph{mission statements} were all the rage not long ago.
  Every two-bit company chimed in with vacuous twaddle about creating
  \emph{excellent products} and \emph{exemplary customer experiences}.
  Predictably, this drivel degraded the value of mission statements, so
  nowadays we don't \emph{endure} them
  anymore.} for their compositions. He provides an example from his writing about
AIDS.

\begin{itemize}
\tightlist
\item
  \emph{I want to portray my protagonist as a fully human character ---
  and not some kind of cardboard saint.}
\item
  \emph{I want to do this so people can identify with and care for her
  and her family...}
\item
  \emph{I want to help illuminate AIDS, and help educate the public
  about key aspects of the disease.}
\end{itemize}

%\hspace{16pt}\emph{\ldots{} and so on \ldots{}}

He then relates how this helped him write a series of newspaper
articles.

\begin{quote}
\emph{I cannot overstate the value of this exercise. It gave me a view
over the horizon as I drafted the story. This 250-word mission
statement, which took about ten minutes to write, helped create a
25,000-word series.}
\end{quote}

This got me thinking, ``What would a mission statement for this blog
look like?''

My first take:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \emph{I want to write a blog that lets me vent and rage about whatever
  bug is up my arse.}
\end{enumerate}

Yes, I've written lots of bug-up-my-arse posts but \emph{Analyze the
Data not the Drivel} (ADND) aspires to more than castrated whining. I
like to think that it lets me try out ideas and refine fuzzy notions. So
perhaps this should be added:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  \emph{In this blog I will speculate, explore and develop ideas that
  range over my peculiar interests.}
\end{enumerate}

You'll find many explore-ideas posts, most of them dealing with aspects
of programming, but this doesn't fully represent this blog. I also write
a lot of diary entries. Hence,

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  \emph{In this blog I will write sporadic diary entries.}
\end{enumerate}

There's more; ADND contains book, movie, TV, and software reviews.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  \emph{In this blog I will sometimes review cultural artifacts that get
  my attention.}
\end{enumerate}

We're not done. ADND has obituaries, snarky listicles, outright
trolling, and dismissive sarcasm.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  \emph{This blog will showcase the unrepentant dickishness of its
  author.}
\end{enumerate}

Clark's mission statement makes sense when you want your writing to
\emph{achieve} goals. I have no goals for this blog. I am not writing
for you; I am writing for myself, not because I want to hear myself
think, or feel that anything I might say, do, suggest or note, is of any
interest or importance. I blog for the same reason smokers smoke, and
gamblers gamble and drug addicts keep taking drugs; I cannot help
myself. Compulsions often precipitate therapy and ADND reeks of it.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\tightlist
\item
  \emph{This blog will provide cheap self-administered therapy and
  remind the author that he lives.}
\end{enumerate}

My \emph{living} is a temporary state of being. Soon the silence will
take me, as it will take you, and you, and you. Maybe this sad little
blog will form the residue of my existence. We all labor consciously or
subconsciously erecting our own memorials. Certainly, the taint of
memorialization stains this blog.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{6}
\tightlist
\item
  \emph{This blog will memorialize its author.}
\end{enumerate}

Of course, monument erection is futile. Camus once moaned that all
\emph{creation is self-consciously ephemeral}. All our monuments will,
in his words, ``weather to mud.''

This blog has no mission. It wanders at will. Some posts have goals but
overall, the best mission statement for this blog is a riff on
\href{https://en.wikipedia.org/wiki/Douglas_Adams}{Douglas Adams}:

\emph{This blog is about life, the universe, and everything.}

%\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
%
%\begin{enumerate}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn1}{}}%
%  This blog clearly shows I need all the help I can
%  get.\protect\hyperlink{fnref1}{↩︎}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn2}{}}%
%  Corporate \emph{mission statements} were all the rage not long ago.
%  Every two-bit company chimed in with vacuous twaddle about creating
%  \emph{excellent products} and \emph{exemplary customer experiences}.
%  Predictably, this drivel degraded the value of mission statements, so
%  nowadays we don't \emph{endure} them
%  anymore.\protect\hyperlink{fnref2}{↩︎}
%\end{enumerate}


%\end{document}
 

