%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2023/09/02/morals-are-demons-that-people-actually-believe-in/}{Morals are Demons that People Actually Believe In}}
\addcontentsline{toc}{subsection}{Morals are Demons that People Actually Believe In}


\noindent\emph{Posted: 02 Sep 2023 18:21:10}
\vspace{6pt}

Too much has been written about ``morality.'' It almost pains me to add
to the deluge of drivel this topic has inundated the world with, but
pains aside, here goes. If you are human and reading
this\footnote{Most of my readers are Bots and AIs.
} you've %\protect\hypertarget{fnref1}{\protect\hyperlink{fn1}{\textsuperscript{1}}},
probably been advised and instructed for your entire short life
to be a ``good moral person.'' It hardly matters whether you're a
fundamentalist religious freak or a fundamentalist atheist freak; you've
been told, trained, advised, and chastised to be a ``good moral
person.''

Of course, what's good to one is evil to another. To a warthog fleeing a
lion, the lion is evil. To the lion chasing the warthog, the warthog is
lunch. Where exactly is the ``morality?'' We're not supposed to ask such
questions because when we do, ``morality,'' whatever the hell it is,
vanishes like Beelzebub after taking a dump in Pandemonium's
gold-encrusted shitter. Many philosophers and other alleged wise men
(I'm not going down the gender-fluid rabbit hole here) have wasted way
too much of their short lives pondering ``morality.'' They've concluded
that ``morality'' is at best a social construct. It's something that
humans seem to think exists. It's akin to a limited liability
corporation without the legal paperwork. All social constructs have one
thing in common: no society, no construct.

If humans disappear, electrons will be just fine. They existed long
before us and will exist long after us. Sadly, or gladly, this is not
true of morals. They vanish with us. They vanish so completely, so
utterly, so absolutely, that even the most astute of precision
instruments won't pick up any lingering traces. \emph{Morals are
imaginary.} They're like vampires, ghosts, gods, and demons. They can
only be found in our deluded minds and nowhere else, but unlike
vampires, ghosts, gods, and demons---entities that even fundamentalist
religious freaks no longer take seriously---morals are still reified,
and people get very upset when their lack of physical existence is
pointed out.

How people get upset has always amused me. Many screech that, ``Without
morals, the world would be a horrible place.''

``Are you sure?''

We've always believed in morals, and the world has always been a
horrible place. Perhaps there's a connection. Maybe if we didn't infuse
our limited intellects with demonic delusions, like morals, and attended
to what's verifiably real, like electrons, then maybe we could fix some
of the horribleness that stalks us from womb to tomb.

%\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

%\begin{enumerate}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn1}{}}%
%  Most of my readers are Bots and AIs.\protect\hyperlink{fnref1}{↩︎}
%\end{enumerate}



%\end{document}
 

