%\input{bmamble.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2020/02/19/more-j-pandoc-syntax-highlighting/}{More J Pandoc Syntax HighLighting}}
\addcontentsline{toc}{subsection}{More J Pandoc Syntax HighLighting}


\noindent\emph{Posted: 20 Feb 2020 02:48:09}
\vspace{6pt}

Syntax highlighting is essential for blogging program code. Many blog
hosts recognize this and provide tools for highlighting programming
languages. \href{https://wordpress.com/}{WordPress.com} (this host) has
a
\href{https://en.support.wordpress.com/wordpress-editor/blocks/syntax-highlighter-code-block/}{nifty
highlighting tool} that handles dozens of mainstream programming
languages. Unfortunately, one of my favorite programming languages,
\href{//www.jsoftware.com}{J}, (yes it's a single letter name), is way
out of the mainstream and is not supported.

There are a few ways to deal with this \emph{problem.}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  Eschew J highlighting.
\item
  Upgrade\footnote{
  The pay more option is always available.
  } your
  \emph{WordPress.com} subscription and install custom syntax
  highlighters that can handle arbitrary language definitions.
\item
  Find another blog host that freely supports custom highlighters.
\item
  Roll your own or customize an existing highlighter.
\end{enumerate}

A few years ago I went with the fourth option and hacked the superb
open-source tool \href{https://pandoc.org/}{pandoc}. The grim details
are described in
\href{https://analyzethedatanotthedrivel.org/2012/09/20/pandoc-based-j-syntax-highlighting/}{this
blog post}. My hack produced a customized version of pandoc with J
highlighting. I still use my hacked version and I'd probably stick with
it if current pandoc versions had not introduced \emph{must-have
features like converting \href{https://jupyter.org/}{Jupyter} notebooks
to Markdown, PDF, LaTeX and HTML.} Jupyter is my default
\emph{thinking-things-through} programming environment. I've even taken
to
\href{https://github.com/bakerjd99/smugpyter/blob/master/notebooks/Unified\%20XKCD\%20Colors.ipynb}{blogging
with Jupyter notebooks}. If you write and explain code you owe it to
yourself to give Jupyter a try.

Unwilling to eschew J highlighting or forgo Jupyter I was on the verge
of re-hacking pandoc when I read the current pandoc (version 2.9.1.1)
documentation and saw that \textbf{\emph{J is now officially supported
by pandoc.}} You can verify this with the shell commands.

The pandoc developers made my day! I felt like
\href{https://www.youtube.com/watch?v=lBEn3a4TIUw}{Wayne meeting a rock
star}.

Highlighting J is now a simple matter of placing J code in markdown
blocks like:

\begin{verbatim}
    ~~~~ { .j }
        ... code code code ...
    ~~~~
\end{verbatim}

and issuing shell commands like:


%\footnotesize
\begin{verbatim}
    pandoc --highlight-style tango --metadata title="J test" -s jpdh.md -o jpdh.html
\end{verbatim}
%\normalsize


The previous command generated the HTML of this post which I pasted into
the WordPress.com \emph{Classic Editor.} Not only do I get J code
highlighting on the cheap I also get footnotes which, \emph{for god
freaking sakes},\footnote{WordPress.com is beginning to remind me of Adobe. Stop taking away
 longstanding features when upgrading!
} are not
supported by the new WordPress block editor for low budget blogs.

\medskip

\textbf{\emph{The source \href{https://github.com/bakerjd99/jacks/tree/master/pandocexamples}{markdown used for this post is available here enjoy!}}}

\small
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{tdkeytest}\KeywordTok{=:}\DecValTok{4} \RegionMarkerTok{: 0}

\CommentTok{NB.*tdkeytest v{-}{-} test natural primary key columns of TAB delimited text files.}
\CommentTok{NB.}
\CommentTok{NB. dyad:  il =. blclColnames tdkeytest clFile}
\CommentTok{NB.}
\CommentTok{NB.   f0=. \textquotesingle{}C:\textbackslash{}temp\textbackslash{}dailytsv\textbackslash{}raw\_ST\_BU.txt\textquotesingle{}}
\CommentTok{NB.   k0=. ;:\textquotesingle{}BuId XMLFileDate\textquotesingle{}}
\CommentTok{NB.   k0 tdkeytest f0}

\CommentTok{NB. first row is header}
\NormalTok{h}\KeywordTok{=.} \DecValTok{0}\KeywordTok{\{}\NormalTok{d}\KeywordTok{=.}\NormalTok{ readtd2s }\KeywordTok{y}

\CommentTok{NB. key column positions}
\StringTok{\textquotesingle{}header key column(s) missing\textquotesingle{}}\NormalTok{ assert }\KeywordTok{{-}.}\RegionMarkerTok{(}\KeywordTok{\#}\NormalTok{h}\RegionMarkerTok{)} \KeywordTok{e.}\NormalTok{ p}\KeywordTok{=.}\NormalTok{ h }\KeywordTok{i.} \KeywordTok{s:} \KeywordTok{x}

\NormalTok{c}\KeywordTok{=.} \KeywordTok{\#}\NormalTok{d}\KeywordTok{=.} \KeywordTok{\}.}\NormalTok{ d}
\NormalTok{b}\KeywordTok{=.} \KeywordTok{\textasciitilde{}:}\NormalTok{p }\KeywordTok{\{"}\DecValTok{1}\NormalTok{ d}

\CommentTok{NB. columns unique, rowcnt, nonunique rowcnt}
\KeywordTok{if.}\NormalTok{ r}\KeywordTok{=.}\NormalTok{ c }\KeywordTok{=} \KeywordTok{+/}\NormalTok{b }\KeywordTok{do.}
\NormalTok{  r }\KeywordTok{,}\NormalTok{ c }\KeywordTok{,} \DecValTok{0}
\KeywordTok{else.}
  \CommentTok{NB. there are duplicates show some sorted duplicate keys}
\NormalTok{  k}\KeywordTok{=.}\NormalTok{ p }\KeywordTok{\{"}\DecValTok{1}\NormalTok{ d}
\NormalTok{  d}\KeywordTok{=.}\NormalTok{ d }\KeywordTok{\{\textasciitilde{}} \KeywordTok{I.}\NormalTok{ k }\KeywordTok{e.}\NormalTok{ k }\KeywordTok{\#\textasciitilde{}} \KeywordTok{{-}.}\NormalTok{b}
\NormalTok{  d}\KeywordTok{=.} \RegionMarkerTok{(}\KeywordTok{/:}\NormalTok{ p }\KeywordTok{\{"}\DecValTok{1}\NormalTok{ d}\RegionMarkerTok{)} \KeywordTok{\{}\NormalTok{ d}
\NormalTok{  b}\KeywordTok{=.} \KeywordTok{\textasciitilde{}:}\NormalTok{p }\KeywordTok{\{"}\DecValTok{1}\NormalTok{ d}
  \KeywordTok{m=.} \KeywordTok{+/}\NormalTok{b}
\NormalTok{  smoutput }\RegionMarkerTok{(}\KeywordTok{":m}\RegionMarkerTok{)}\KeywordTok{,}\StringTok{\textquotesingle{} duplicate key blocks\textquotesingle{}}
  \KeywordTok{n=.}\NormalTok{ DUPSHOW }\KeywordTok{<.} \KeywordTok{m}
\NormalTok{  smoutput }\StringTok{\textquotesingle{}first \textquotesingle{}}\KeywordTok{,}\RegionMarkerTok{(}\KeywordTok{":n}\RegionMarkerTok{)}\KeywordTok{,}\StringTok{\textquotesingle{} duplicate row key blocks\textquotesingle{}}
\NormalTok{  smoutput }\RegionMarkerTok{(}\KeywordTok{<}\NormalTok{p }\KeywordTok{\{}\NormalTok{ h}\RegionMarkerTok{)} \KeywordTok{,\&.>} \KeywordTok{n} \KeywordTok{\{.} \KeywordTok{,.}\NormalTok{ b }\KeywordTok{<;.}\DecValTok{1}\NormalTok{ p }\KeywordTok{\{"}\DecValTok{1}\NormalTok{ d}
\NormalTok{  r }\KeywordTok{,}\NormalTok{ c }\KeywordTok{,} \KeywordTok{\#}\NormalTok{d}
\KeywordTok{end.}
\RegionMarkerTok{)}
\end{Highlighting}
\end{Shaded}
\normalsize


%\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
%
%\begin{enumerate}
%\item
%  \hypertarget{fn1}{}
%
%  The pay more option is always available.\protect\hyperlink{fnref1}{↩︎}
%\item
%  \hypertarget{fn2}{}
%
%  WordPress.com is beginning to remind me of Adobe. Stop taking away
%  longstanding features when upgrading!\protect\hyperlink{fnref2}{↩︎}
%\end{enumerate}



%\end{document}
