%\input{bmamblenew.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2012/12/04/more-about-jhs-with-dhtmlx-the-grid/}{More about JHS with the DHTMLX Grid}}
\addcontentsline{toc}{subsection}{More about JHS with the DHTMLX Grid}


\noindent\emph{Posted: 05 Dec 2012 04:22:50}
\vspace{6pt}

I have resolved my \href{http://dhtmlx.com/docs/download.shtml}{DHTMLX
standard edition} row data extraction problem. The standard edition does
not serialize grids or track user cell changes. You have to pay for such
luxuries. Because I'm a
\href{http://www.youtube.com/watch?v=ZgP0aUKlmNw}{foul software Grinch}
and this is just an exploratory hack I had to roll my own. I am posting
the relevant JavaScript because I could not find similar examples. Here
is how you can fetch rows from standard edition DHTMLX grids and save
them as JSON in a hidden \texttt{textarea} element. Eric Iverson
suggested hidden \texttt{textarea}s and they work like a charm.

\begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
%[sourcecode language="javascript" wraplines="false" gutter="false" autolinks="false"]
\begin{lstlisting}[language=JavaScript,frame=single,framerule=0pt,label=lst:scr3516X0]

function ev_saveme_click(){

  if ('undefined' != typeof grid0){
  
    if (0 == grid0.getRowsNum()){
      jbyid("rerowcnt").innerHTML = "No rows to save"; 
      return;
    }

    var st = new Date().getTime(),  // start time  
        ids = grid0.getAllRowIds(","),
        ccnt = 1 + grid0.getColumnsNum();  // includes id
      
    ids = ids.split(",");  
    var rcnt = ids.length,
        tab = new Array(rcnt);
    
    // header row - tab[0][0] cell ignored
    tab[0] = new Array(ccnt);  
    for (var i = 1; i < ccnt; i++) {
      tab[0][i] = grid0.getColumnLabel(i-1,0); 
    }
     
    // cells with leading row id
    for (var i = 0 , si = 1 ; i < rcnt; i++ , si++) {
      tab[si] = new Array(ccnt);
      for (var j = 1; j < ccnt; j++) {
        tab[si][j] = grid0.cells((+ids[i]),j-1).getValue();
      }
      tab[si][0] = ids[i];
    }
  
    // prefix row column counts 
    var pfx = (rcnt+1) + " " + ccnt + "*";
    jbyid("gridchgs").innerHTML = pfx + JSON.stringify(tab);
    jdoajax(["gridchgs","tout"],"");
  
    var et = new Date().getTime() - st;  // end time    
    jbyid("rerowcnt").innerHTML= " row count= " + grid0.getRowsNum() +  
        ",  JavaScript ms= " + et; 
        
  } else {
  
    jbyid("rerowcnt").innerHTML= "Nothing to save";     
  }
}
\end{lstlisting}
\end{tcolorbox}

Passing data back to J is fast but the J JSON addon
\texttt{convert\textbackslash{}json} burps on large datasets. For this
demo I substituted a simple table oriented parser that is much faster.



%\end{document}