%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2020/09/10/oscars-now-as-meaningless-as-nobel-peace-prizes/}{Oscars Now as Meaningless as Nobel Peace Prizes}}
\addcontentsline{toc}{subsection}{Oscars Now as Meaningless as Nobel Peace Prizes}


\noindent\emph{Posted: 10 Sep 2020 18:08:55}
\vspace{6pt}

Eons ago, upon learning that Barak Obama, aka the
\href{https://www.nationalreview.com/the-campaign-spot/magic-lightbringer-messiah-not-new-terms-obama-jim-geraghty/}{Magic
Lightbringer}, had been awarded the Nobel Peace Prize for
\href{https://analyzethedatanotthedrivel.org/2009/10/09/nobel-peace-prize-idol/}{doing
sweet diddly-squat}, I rightfully concluded that the Nobel Peace Prize
had completed its long embarrassing journey to absolute irrelevance. I
opined that frivolous
\href{https://en.wikipedia.org/wiki/Canadian_Idol}{Canadian Idol} awards
meant more because at least Idol recipients had to ``do stuff.''

Well, I'm happy to report that the Oscars have also completed their long
sanctimonious, holier-than-thou, pilgrimage to pure pointlessness. With
today's woke-minded announcement that films must be ``sufficiently
diverse'' to qualify for a Best Picture Oscar, the Oscars are no longer
even pretending to be about quality. Frankly, it would be more honest to
simply ``cancel'' the Best Picture Oscar and replace it with a ``Wokist
Picture Oscar.''

I know I should just ignore this shit, but it's hard to resist looking
down the outhouse toilet hole. To qualify for the Wokist Picture Oscar
\href{https://www.nytimes.com/2020/09/09/movies/oscars-best-picture-diversity.html}{a
film must meet some basic} (Standard
A)\footnote{Yes, there are more ``standards.'' It's not enough to wreak the Oscars
  with art killing mandates; the entire process must have the exquisite
  eyeball rolling tedium of a corporate HR
  policy.
} criteria: %\protect\hyperlink{fn1}{\textsuperscript{1}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  At least one actor from an underrepresented racial or ethnic group
  must be cast in a significant role.
\item
  The story must center on women, L.G.T.B.Q. people, a racial or ethnic
  group or the disabled.
\item
  At least 30 percent of the cast must be actors from at least two of
  those four underrepresented categories.
\end{enumerate}

Strictly applied, \emph{Hollyweirdo's} new diversity rules would
eliminate \emph{Hamlet.} Hamlet has no \emph{overtly-out} gay
characters\footnote{We've all had our suspicions about Rosencrantz and
  Guildenstern.
}, no preening
lesbians, no bitchy bull dykes, no flouncing pussy boys. And, even
worse, Hamlet, in all its iambic pentameter'ized glory, is all about
\emph{pale white Danes.} Where's the diversity?

The \emph{Hollyidiots} have really
\href{https://www.urbandictionary.com/define.php?term=jump-the-shark}{jumped
the shark} here. The creation of art is hard enough without moronic
\emph{HR-Grant-Application-Legalistic-AA}\footnote{\emph{Asinine Action}}
bullshit piled on!

%\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

%\begin{enumerate}
%\item
%  \leavevmode\hypertarget{fn1}{}%
%  Yes, there are more ``standards.'' It's not enough to wreak the Oscars
%  with art killing mandates; the entire process must have the exquisite
%  eyeball rolling tedium of a corporate HR
%  policy.\protect\hyperlink{fnref1}{↩︎}
%\item
%  \leavevmode\hypertarget{fn2}{}%
%  We've all had our suspicions about Rosencrantz and
%  Guildenstern.\protect\hyperlink{fnref2}{↩︎}
%\item
%  \leavevmode\hypertarget{fn3}{}%
%  \emph{Asinine} \emph{Action}.\protect\hyperlink{fnref3}{↩︎}
%\end{enumerate}



%\end{document}
