%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2023/12/11/pam-and-the-alien-memory-biz/}{Pam and the Alien Memory Biz}}
\addcontentsline{toc}{subsection}{Pam and the Alien Memory Biz}


\noindent\emph{Posted: 11 Dec 2023 21:03:01}
\vspace{6pt}

A mockery by \emph{Kline Leopold Hedrös} ©2023

Nobody expected libertarian aliens to set up a memory trading post off
the west coast of Antarctica, but they did, and now Pam and her mates on
the good ship \emph{Forget Me Not} were entering the UN-patrolled waters
around the Human Exclusion Zone or ``the HEZ'' as everyone called it.
The HEZ was a human-specific force field that projected more than a
hundred kilometers around the HEZ's central spire. If you tried to cross
the HEZ, you would feel a greater and greater force pushing back until
you couldn't advance. The HEZ blocked only humans and their machines.
Birds, fish, marine mammals, and insects penetrated the HEZ unimpeded.
Nobody had a freaking clue how it worked.

From her position on the ship's bow, Pam saw the thirteen-kilometer-high
transparent alien spire in the center of the HEZ. The \emph{Spire}
shoots out of the west Antarctic Sea and climbs like a charmed, coiled
diamond cobra to heights far beyond the engineering prowess of naked
apes. The Spire made it crystal clear (why not use a crystal tower when
making things crystal clear) that the libertarian aliens had technology
thousands of years beyond human levels and were not to be fucked with.

Everyone remembers where they were when the libertarian aliens announced
their presence. It was during the last US Presidential debate. The old,
demented moron was squaring off against the old orange moron. The
``debate'' (please, no laughter) was going as expected when suddenly a
\emph{Star Wars'zy} apparition appeared between the old morons.

``Greeting citizens of Earth. Forgive this intrusion. My name is Sam. I
am here to say that our new west Antarctic memory trading outpost is
open for business. Look for the Spire. The first thousand customers will
get two life memories for one. Tell them Sam sent you.''

Sam made a big impression. Post-debate polls showed he was the clear
winner. Everyone wanted to vote for him. Sam radiated \emph{rizz}
(charisma) and seemed vastly more knowledgeable and trustworthy than the
old morons who, with their blank diaper-filled faces, couldn't have
looked more pathetic.~

We later learned that the Secret Service shat giant gooey bricks when
Sam appeared. They made frantic attempts to cut power to the debate
stage, but the libertarian aliens easily circumvented their primitive
naked ape technologies. Within minutes global social media forgot about
the orange morons' threat to democracy, the never-ending wars in
Ukraine, the middle east, the Congo, and now Guyana (come on, people),
our out-of-control global inflation, deficit financing, the plight of
the BIPOC'ky transgendered, global warming, climate justice, land back
hysterics, microplastics, reparations, the great Pacific garbage patch,
antisemitism in the academy, the lack of diversity in whatever was up
people asses today, and most miraculously Taylor Swift's divorce.
Suddenly, all our baby problems didn't matter. Most people wanted to
know \emph{one thing}: were they on alien menus? How to prepare man,
``it's a cookbook,'' was top of mind.

Lucky for us, the libertarian aliens were vegans. It was the first time
in recorded history that people were happy to learn somebody was vegan.
Even better, the libertarian aliens didn't brag about their diet.
Imagine that: vegans with a sense of perspective. The universe really is
queerer than we can imagine.

After our fears of appearing on dinner plates subsided, we wanted to
know why the libertarian aliens were here. What exactly are they
trading?

As if reading humanity's collective thoughts, Sam's \emph{Star Wars'zy}
apparition appeared on the UN General Assembly podium and explained.

``Since my last appearance, there's been a lot of buzz about `\emph{the
aliens}.' Just what's their deal? What are they up to? Why here? Why
now? Well, Earthlings, the answer is both complex and simple. Because
you are limited naked apes, I will give you the simple answer.''

Sam said, "There are three paths for intelligent life in the universe.''

``The first path is easy to understand. Extinction! Extinction is the
typical outcome. Some species disappear by natural means, and others do
themselves in. When species breach certain destructive technology
barriers, many cannot resist the urge to self-purge. Humans like to
think of themselves as apex assholes, but I can assure you that humans,
while not particularly bright on galactic scales, are more civilized
than most. You thought the \emph{Star Wars} galaxy was mean; news flash,
reality is super harsher.''

Sam paused and looked around at the dumbfounded faces (just another day
in the UN General Assembly) before continuing, ``The second path is what
we call Narcissistic Collapse.''

``Narcissistic collapse occurs when a species' ability to simulate
reality eclipses their desire to deal with it. Here on Earth, many of
you go on, and on, and on, and on, and on, and on, about how young
people (males) waste their lives playing video games. Imagine if you
could plug into a hyper realistic video game and erase your memory that
a real universe exists. Many species \emph{voluntarily} confine
themselves in \emph{Matrix} fantasies of their own devising and lose all
interest in the actual universe. Narcissistic collapse occurs far more
often than the last alternative.''

``The last path will be hard for many of you to understand, but here's
the dumbed-down version. Species with immortal ambitions have a problem
with ordinary baryonic matter. I don't think I will alarm you with a
little physics spoiler. The proton is not stable. I know you've
conducted your own experiments and concluded that if the proton isn't
stable, its half-life is greater than 10\textsuperscript{32} years. You
are right. The half-life is 10\textsuperscript{331} years. So long that
probably not a single proton in the entire observable universe has
decayed, but while 10\textsuperscript{331} is essentially forever on
human, or even Big Bang timescales, it's not. In a mere
10\textsuperscript{1000} years, everything in this universe ends with
one exception: space itself. ``

Sam looked up at the UN delegates. It was like an auditorium of drugged
deer in an 18-wheeler spotlight. The normally fatuous and stupid UN
delegate creatures looked even dumber than usual. Before any of them
could speak, Sam went on.

``The only way to live forever in this universe is to insert yourself
into space. Advanced species and their AI descendants have been doing
this all over the observable universe for billions of years. Years ago,
your astronomers detected a mysterious increase in the rate of the
universe's expansion. You call it Dark Energy. It seems that the
expansion rate accelerated about five billion years ago, and nobody
knows why. Well, here's another physics spoiler. As more and more
advanced species insert themselves into the fabric of space, the
universe's expansion rate increases. Don't ask me to explain; your
minuscule minds wouldn't understand. The rate was constant before the
insertions because it took roughly eight billion years for advanced
species to evolve. Beings of such power (gods) that they alter the
expansion rate of the observable universe are not concerned with the
antics of naked apes confined to one little shit-ball planet. About one
in a million intelligent species that dodge extinction and narcissistic
bullets ascend to the dark energy realm. Still, there are trillions of
galaxies hosting sometimes millions of intelligent species. Over vast
time and space scales, it adds up.''

Sam ended his little lecture by explaining the libertarian alien
business model.

``This brings me to what we are trading. While basically true, the three
paths have what your NPR Karens call `nuance.' Clearly, there's no
business case for the extinct or the ascending dark energy gods, but the
narcissists have unique needs that the galactic market can address.
\emph{Narcissists always stimulate the economy.} While most species
rapidly develop the capacity to simulate whatever they can imagine, they
also quickly discover they \emph{cannot imagine as much as they would
like}. Good old-fashioned reality with blind natural selection, humdrum
physics, and chemistry plodding over billions of years exhibits far
greater \emph{imaginative works} than any narcissistic species. The
universe is not only queerer than you can imagine, it's queerer than all
your alien peers can imagine as well.''

Sam dramatically paused to let this sink in but remembered he was
projecting in the UN, where nothing ever sinks in, and continued,
``There is a real hunger out there for brave new worlds. Not tedious
hacky fantasies, but nitty-gritty unimaginable alien realities. Your
memories, your sense of self, and the daily crap you carry in your tiny
naked ape skulls has great value simply because reality is beyond
simulation. There are trillions of creatures, very different from
yourselves, that hunger for lives they cannot imagine. Their hunger is
so great they are willing to cross interstellar space and trade their
memories.''

The porcine, docile, and vacuum-headed UN delegates started murmuring,
but Sam silenced them with, ``I know what you're thinking. What's in it
for us?''

``IP rights. We retain the right to duplicate client memories and reuse
them. Some lives are just more popular than others. You think Taylor
Swift is a big star. You have no idea what a real galactic star is! But,
for this month only, you can find out if you present yourself at the HEZ
boundary and trade your memories for Milky Way's biggest celebrity.
Remember, this is a time-limited offer.'' With that, Sam's \emph{Star
Wars'zy} apparition vanished.

Pam was Zeus-struck by Sam's UN speech. As an
\emph{uber-swiftie} she was appalled.

``There are bigger stars than Taylor Swift. Impossible. Blasphemy!''

Pam immediately blasted out a dozen social media posts, informing a
breath-baited world that she was offended and outraged
(\#CancelAlienSam). For a few days, Pam bathed in the affirmations of
her \emph{swiftie} herd, but then a nasty mind worm started eating her
confidence. The aliens knew a lot more than us. Everyone says that.
Maybe there is a bigger star than Taylor. Maybe her entire life is a
lie. Maybe everything she believes is parochial bullshit. She looked up
the meaning of ``parochial.'' She thought it had something to do with
the ``patriarchy.'' Pam couldn't be ``parochial.'' That sounded almost
racist, or \emph{all lives matter'ey}. What would the NPR Karens think?
To circumvent imagined parochial horrors, Pam decided to take Sam up on
his offer.

As a mega-online influencer-boss, Pam cut a deal to \emph{Tok} (TikTok),
\emph{Gram} (Instagram), and \emph{X,} her voyage to the HEZ, where she
would broadcast her memory trade with Sam. Nobody, including the
libertarian aliens, puts anything important on the mainstream media
anymore. As the good ship \emph{Forget Me Not} reached the designated
trade spot, a crystal-clear slab (libertarian aliens love their
crystals) with Sam's \emph{Star Wars'zy} apparition approached the good
ship \emph{Forget Me Not} from The Spire.

The slab hovered alongside, and Pam boldly stepped where no one had
stepped before. Then Pam's social media entourage, her video and podcast
crew, stepped where \emph{one} had stepped before. Soon, a little
nucleus of self-important naked apes gesticulated around Sam's
\emph{Star Wars'zy} apparition on the floating crystal slab.

The first order of business was signing the ATOS (Alien Terms of
Service).

The ATOS was an unenforceable bit of bureaucratic tentacle-kissing
bullshit. It was getting to the point where you couldn't run a business
in the galaxy without some GAG (Galactic Advisory Group) slime mold
smothering you. Want to get libertarian aliens going? Ask them how they
feel about unnecessary galactic regulations. What, you thought your MAGA
neighbors ranted?

With the ATOS signed, Sam explained how the memory trades worked.

``Memory swaps between alien minds are unstable and not advised by the
GAG. When the swap is complete, you will awake as an alien in an alien
world. Your life, your human sense of self, will seem like a vivid
fading dream. As you become fully conscious, the dream will fade away.
You will forget everything you have ever known about yourself and your
life. You will be something else, somewhere else.''

As Sam blah, blah, blahed on, Pam interrupted with, ``How will I post
this? My followers need to see something.''

Sam, used to dealing with recalcitrant customers, said, ``No
\emph{problemo!''} Sam was binging Schwarzenegger's early movies. He
found much to like in, crush your enemas, flush them before you, and
hear the lamentations of the vaginas.

Then Sam continued, ``Brain activity can be rendered as images. At no
extra cost, we will broadcast what your brain perceives to your
entourage.''

Satisfied, Pam said, ``Let's get started.''

Sam dropped a final caveat, ``The stress on your brain will be so great
that the swap will only last for a few days. We will have to shut your
brain down when this time is up. I know that sounds bad, but from your
point of view, it will be as if you have lived a full alien life. The
galactic star, the super Swift, whose memories you will assume, comes
from a long-lived species. \emph{Theez} (human sex doesn't apply here)
is around twenty thousand years old. You're trading your shortish human
life for a longish alien one. It's a great deal.''

Pam considered Sam's words. So, the libertarian aliens would flood her
mind with memories that would wipe hers and kill her in a few days. But
she would live the long life of a star greater than Taylor Swift, and
(what mattered to Pam) her every thought would be tsunami-splashed over
global social media. Imagine the likes, the reposts, the basic-bitch
envy, the cringe-incel whining, the masturbating emojis! As an
\emph{uber-swiftie,} Pam couldn't imagine a more heroic sacrifice.

``Like I said, let's get started.''



%\end{document}

