%\input{bmamble.tex}

\subsection*{\href{http://bakerjd99.wordpress.com/2012/07/09/playing-the-blog-hit-game/}{Playing the Blog hit game}}
\addcontentsline{toc}{subsection}{Playing the Blog hit game}


\noindent\emph{Posted: 10 Jul 2012 03:39:06}
\vspace{6pt}

On June 5\textsuperscript{th} 2012 my little blog set an all time hit
record: 198 robots, spammers and readers incremented my counters. 198
hits would be embarrassing for a major blog like
\href{http://pjmedia.com/instapundit/}{Instapundit} but for
\href{http://bakerjd99.wordpress.com/}{Analyze the Data not the Drivel}
it was a
``\href{http://www.samizdata.net/blog/glossary\_archives/2002/09/hitnosis.html}{hitnotic}''
day. I always attribute my triumphs to my utter manly awesomeness but I
had to ask; \emph{was anything else going on June 5\textsuperscript{th},
2012? Nothing much except the last transit of Venus in this century!} The
masses were searching for ``transit'' and hundreds landed on this
\href{http://bakerjd99.wordpress.com/2012/04/22/2012-venus-transit-and-annular-eclipse/}{little
entry} I wrote a few months ago.

It takes time for a blog post to burrow into cyberspace. Google and Bing
are always prowling blog sites and will pick up new posts within minutes
but it takes about two weeks before worldwide indexes are updated. Once
a post is on search engines readers will find it and when they do it
will meet one of these three fates.

\begin{enumerate}
\item
  \emph{Nobody ever reads it again.} This is the fate of most of my
  posts. I have posts that my dog, if I had a dog, wouldn't read. It's
  too bad because some of my
  \href{http://bakerjd99.wordpress.com/2010/06/16/i-did-not-have-sex-with-that-oil-spill/}{finest
  lyrical unhinged rants} are my least read posts.
\item
  \emph{It gets lots of hits followed by a quick return to few or none.}
  My popular posts follow this pattern. Now that the 2012 transit of
  Venus is history people will stop searching for it. Popular posts fade
  faster than
  \href{http://www.drparkave.com/news/10-famous-women-aging-gracefully-10-who-arent/}{old
  Botox saturated actresses} so enjoy your hits \emph{while they last!}
\item
  \emph{It gets legs and keeps sucking in hits for weeks, months and
  years.} My normal traffic comes from half a dozen \emph{leggy}
  postings. My \emph{leggy-est} posting is an
  \href{http://bakerjd99.wordpress.com/2010/07/28/the-20-seconds-that-ruined-inception/}{\emph{Inception}
  movie review} that I wrote almost two years ago; it's still generating
  ten to twenty hits per week. \emph{Its ok people nobody really got that
  movie.}
\end{enumerate}
Finally, \emph{the blog hit game is a long game;} you have to keep
playing. The best sports analogy is golf. Golf is the world's hardest
game. The gap between a perfect round of eighteen and what the best
players are capable of is insurmountable. Nobody will ever shoot an
honest eighteen. A
\href{http://golf.about.com/cs/golfterms/g/bldef\_bestball.htm}{best
ball} foursome of Buddha, Christ, Mohammad and the archangel Gabriel
couldn't shoot an honest eighteen. The Sun exploding tomorrow is more
likely than on honest eighteen. Golf sets a bar so high it will never be
breached. Artists have similar bars. The perfect novel is impossible.
The perfect song is impossible. The perfect sculpture is impossible and
I dare say the perfect blog post is impossible but then \emph{it's the
impossibility of perfection that keeps things interesting.} Keep at it
and the hits will come.



%\end{document}