%\input{bmamble.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2014/04/15/pussydent-hildabeast/}{Pussydent Hildabeast}}
\addcontentsline{toc}{subsection}{Pussydent Hildabeast}


\noindent\emph{Posted: 15 Apr 2014 21:41:44}
\vspace{6pt}

My blood moon photography didn't turn out because I didn't. Come
midnight fatigue, familiarity and spotty weather conspired to send this
exhausted W2\footnote{
W2 is a basic IRS tax form in the United State. I calculate my
taxes by hand. I sometimes do the arithmetic on paper just to increase
the pain and rage. Taxation should hurt and in my case it does. Taxes
are by far the largest ``line item'' in my budget, but what the heck,
lesbians on welfare need free birth control.
}
drone to bed. It's just as well; if you're not
doing consider sleeping. In six months I'll get another shot at
photographing a blood moon. For the nonce, I'll muse on menstrual moon
madness. Exactly what Earth shaking event does this terrible tetrad
foretell?

\begin{verse}
\textit{Some cry Ukraine}\\
\textit{I say are you insane}\\
\vspace{1em}
\textit{Others holler}\\
\textit{The demise of the dollar}\\
\vspace{1em}
\href{http://modernwomandigest.com/disturbing-new-feminist-trend-free-bleeding/}{\textit{Moon free bleeding}}\\
\href{http://modernwomandigest.com/disturbing-new-feminist-trend-free-bleeding/}{\textit{We're not needing}}\\
\vspace{1em}
\href{https://xkcd.com/386/}{\textit{Someone on the Internet}}\\
\href{https://xkcd.com/386/}{\textit{Is wrong}}\\
\end{verse}

But now, in the blood moon discharge, it's clear a fate worse than
community organizers awaits a pummeled public. Behold, \emph{Pussydent
Hildabeast},\footnote{
 A Pussydent is a \emph{metaphorically ball-less}~president and a
Hildabeast is Hillary Clinton.
}
 a rough nagging crone, her
``\href{http://en.wikipedia.org/wiki/The_Second_Coming_(poem)}{hour come
round at last, slouches towards Bethlehem to be born?''}

\begin{verse}
\textit{Soon we’ll beg}\\
\href{https://www.youtube.com/watch?v=kTcRRaXV-fg}{\textit{Who}}\\ 
\vspace{1em}
\href{https://www.youtube.com/watch?v=Qkuu0Lwb5EM&feature=kp}{\textit{To let}}\\
\href{https://www.youtube.com/watch?v=Qkuu0Lwb5EM&feature=kp}{\textit{The dogs of war out}}\\
\end{verse}


%{[}1{]}
% W2 is a basic IRS tax form in the United State. I calculate my
%taxes by hand. I sometimes do the arithmetic on paper just to increase
%the pain and rage. Taxation should hurt and in my case it does. Taxes
%are by far the largest ``line item'' in my budget, but what the heck,
%lesbians on welfare need free birth control.


%{[}2{]}
% A Pussydent is a \emph{metaphorically ball-less}~president and a
%Hildabeast is Hillary Clinton.



%\end{document}