%\input{bmamble.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2018/01/28/setting-smugmug-print-size-keywords-with-jupyter-and-python/}{Setting SmugMug Print Size Keywords with Jupyter and Python}}
\addcontentsline{toc}{subsection}{Setting SmugMug Print Size Keywords with Jupyter and Python}


\noindent\emph{Posted: 28 Jan 2018 07:27:10}
\vspace{6pt}

For the last few weeks, my normal hobbies have been preempted by my
obsessive \emph{refactoring} of an old SmugMug keyword setting program.
Many years ago I wrote a small application that helped me maintain
meaningful SmugMug keywords. I used this application for years until
inevitable software changes broke it. Replacing it with something better
has been on my to-do list for ages.

I kept putting it off because I knew the tools I used in the past,
mostly J and VB, were not well suited to REST API programming. Yes, I
know just about any programming tool can be forced to serve, Turning
completeness guarantees it, but I have grown weary of programming to
prove tiresome points. If a tool makes something more difficult or
tedious than it should be then change tools!

The downside of changing tools is that it usually results in learning
yet another programming language. I always try to avoid this! I briefly
considered languages with decent REST support that I already
\emph{sort-of-know}\footnote{Be highly suspicious of people who claim to fully understand any
  programming language. Only delusional nitwits would make such a claim
  for any natural language. Does anybody, even luminaries like
  Shakespeare, truly understand English? We all \emph{sort-of-know} our
  mother tongues and if we're honest, we're continually surprised by how
  others make use of it. \emph{Literature, it's a thing.} The same holds
  for programming languages. Every day I'm surprised, by unusual,
  stupid, silly, clever and freaking brilliant code fragments in
  programming languages that I have used for
  decades.
}, C\#,
JavaScript, VB.Net and decided that proper 64 bit versions were either
too expensive (C\#, VB.Net) or that I didn't want to stare at ugly
bracket infested syntax for weeks. I'm talking about you JavaScript.
Even your fanboys admit that you're an ugly duckling.

I eventually decided to go with Python. I've always found Python code
more readable than many other programming languages. This is a
widespread opinion. Python is free, open source, and comes with a large
diverse set of tools. One of the best tools to come out of the Python
world is Jupyter. \href{https://jupyter.org/}{Jupyter} is the first
public domain open source
\href{https://en.wikipedia.org/wiki/Literate_programming}{literate
programming} tool that has gained a large following.

I've been a fan of literate programming ever since I read
\href{https://en.wikipedia.org/wiki/Literate_programming}{Knuth's
seminal book}. He used the technique to create some of the
\href{https://www.amazon.com/TeXbook-Donald-Knuth/dp/0201134489}{best
program documentation ever created}. I always wondered why literate
programming never caught on. I suspected the basic problem was simply
that many programmers are not particularly literate. Well, Jupyter is
proving me wrong.

\emph{Jupyter is certainly helping me write and program with such
clarity that all my ideas seem trivial.}

Compare this notebook, (use the first link for the best layout), to my
\href{https://analyzethedatanotthedrivel.org/2010/02/21/assigning-smugmug-print-size-keys/}{earlier
blog post} about setting SmugMug print size keywords.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  \textbf{Nbviewer}:
  \href{https://nbviewer.jupyter.org/github/bakerjd99/smugpyter/blob/master/notebooks/Setting\%20SmugMug\%20Print\%20Size\%20Keywords\%20with\%20Jupyter\%20and\%20Python.ipynb}{Setting
  SmugMug Print Size Keywords with Jupyter and Python}
\item
  \textbf{GitHub}:
  \href{https://github.com/bakerjd99/smugpyter/blob/master/notebooks/Setting\%20SmugMug\%20Print\%20Size\%20Keywords\%20with\%20Jupyter\%20and\%20Python.ipynb}{Setting
  SmugMug Print Size Keywords with Jupyter and Python}
\end{enumerate}

%\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

%\begin{enumerate}
%\item
%  \hypertarget{fn1}{}
%
%  Be highly suspicious of people who claim to fully understand any
%  programming language. Only delusional nitwits would make such a claim
%  for any natural language. Does anybody, even luminaries like
%  Shakespeare, truly understand English? We all \emph{sort-of-know} our
%  mother tongues and if we're honest, we're continually surprised by how
%  others make use of it. \emph{Literature, it's a thing.} The same holds
%  for programming languages. Every day I'm surprised, by unusual,
%  stupid, silly, clever and freaking brilliant code fragments in
%  programming languages that I have used for
%  decades.\protect\hyperlink{fnref1}{↩}
%\end{enumerate}



%\end{document}

