%\input{bmamblenew.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2010/02/05/smugmug-duplicate-image-hunting/}{SmugMug Duplicate Image Hunting}}
\addcontentsline{toc}{subsection}{SmugMug Duplicate Image Hunting}


\noindent\emph{Posted: 05 Feb 2010 18:07:45}
\vspace{6pt}

One of the many things the developers of
\href{http://www.cerious.com/}{Thumbsplus} got right was a proper
\href{http://en.wikipedia.org/wiki/Database\_normalization}{normalized
database schema}. When I first inspected the layout of a Thumbsplus
database I knew I was in good hands. In Thumbsplus image files get
unique keys and image galleries are simply lists of image keys. Images
can appear in any number of galleries, without duplication, just the way
the gods of database design intended.

Assigning unique keys and grouping by key lists is \emph{so correct}
that it was a shock to discover that
\href{http://www.smugmug.com/}{SmugMug}, until recently, eschewed this
principle. Prior to a recent upgrade if you wanted to display an image
in more than one gallery you had to \emph{\ldots{} shudder with horror
\ldots{}}. make copies! Whenever I made an image copy I felt like I was
masturbating in an art museum.

This outrage is now fixed and you can place an image in as many
galleries as you want without copying. Unfortunately there is a
\emph{residual} problem. How do you hunt down and exterminate all your
bogus copies? In an acronym:
\href{http://www.fastsum.com/support/md5-checksum-utility-faq/md5-hash.php}{MD5}.
SmugMug assigns MD5' s to all images. If two MD5's are the same there is
an extremely high likelihood you are dealing with copies. So all you
have to do is find images with identical MD5's and delete the extra
copies. The following \href{http://www.jsoftware.com/}{J verb} uses image
tables created from the XML captured by my
\href{http://bakerjd99.wordpress.com/2010/02/03/command-line-c-smugmug-api-metadata-download/}{SmugMug
metadata dumper} to do just this.

\begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
%[sourcecode gutter="false" wraplines="false"]
\begin{lstlisting}[language=jdoc, frame=single,framerule=0pt,label=lst:scr369X0]
SmugDupsFrMD5=:3 : 0

NB.*SmugDupsFrMD5 v-- duplicate SmugMug images from MD5.
NB.
NB. monad:  btct =. SmugDupsFrMD5 clDirectory
NB.
NB.   SmugDupsFrMD5 'c:\pd\docs\smugmug\data\'

NB. read table files
path=.tslash y
albums=. readtd2 path,SMUGALBUMTABLE
images=. readtd2 path,SMUGIMAGETABLE
images=. }. images [ imhead=. 0 { images

NB. all duplicate MD5's
pos=. imhead i. <'MD5'
md5=. pos {"1 images
dup=. md5 #~ -. ~:md5
images=. (md5 e. dup)#images
images=. (/: pos {"1 images) { images

NB. remove images with matching smugmug pids
NB. these are proper virtual images and not copies
pos=. imhead i. <'PID'
pid=. pos {"1 images
dup=. pid #~ -. ~:pid
if. #images=. (-.pid e. dup)#images do.

  NB. retain selected columns and insert album names
  images=. (imhead i. ;:'FILENAME GID PID MD5 ALBUMURL') {"1 images
  albums=. ((0 {"1 albums) i. 1 {"1 images){ 1 {"1 albums
  images=. albums (<a:;1)} images

  NB. group by MD5
  images=. (~:3 {"1 images) <;.1 images
  images=. >&.>@:(<"1@|:) &> images

  NB. order MD5 groups by galleries in groups
  NB. this results in a good order for editing
  NB. out the duplicates on SmugMug
  images=. (\:&.> 1 {"1 images) {&.> images
  (\: 0 {&> 1 {"1 images){images
else.
  NB. no duplicates
  0 5$''
end.
)
\end{lstlisting}
\end{tcolorbox}

%J source is not supported by the WordPress source code plugin so no
%syntax coloring for now.


%\end{document}