%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2023/12/04/society-prefers-dead-liabilities/}{Society Prefers Dead Liabilities}}
\addcontentsline{toc}{subsection}{Society Prefers Dead Liabilities}


\noindent\emph{Posted: 04 Dec 2023 19:11:58}
\vspace{6pt}

The other day, while trolling the fetid depths of
\href{https://www.reddit.com/}{Reddit,} I was amused by the response to
this story about more and more
\href{https://moneywise.com/news/economy/rate-of-homeless-baby-boomers-increasing}{boomers
becoming homeless}. The nugatory netizens of Reddit were not
sympathetic. They blame the execrable boomer generation for many of the
ills, both real and imaginary, that have befallen them. \emph{Yes,
boomer hatred is booming!} As a bombastic boomer, all I can say is get
in line, kids; nobody hates them more than I do. The raging Redditers
were particularly incensed that they, the \emph{gen-what-evers}, will
now have to clean up boomer messes --- and diapers --- while forking
over vast sums to do so. It turns out that paying for old, unproductive
people is not popular. Who could have predicted that?

I labor under many illusions, but I have never swallowed the bilge that
``society'' cares about the welfare of the ``unproductive.'' Of course,
what counts as ``productive'' depends on \emph{what} is doing the
counting. Maybe a tortured homeless artist, dissolving in an opioid haze
while awaiting a muse's touch, might be considered worthy in some
dissolute domains. But I can assure you that is not how governments
measure worth. They have a more straightforward method. Are you paying
taxes? If you are paying taxes, you are worth something. If you are not
paying taxes, you are worthless. It gets worse. If you are receiving net
benefits, you are worse than useless; you are a liability, a parasite,
and society would be better off if you were dead. So, the Redditers have
a point. Boomers are now mostly expensive liabilities, and while the
\emph{gen-what-evers} are \emph{not currently on board} with murdering
them, they wouldn't mind if something else did. \emph{All entities seek
to eliminate liabilities.}

We all know this, but we pretend it's horrible to resent supporting the
useless. See all those unhoused addicts shitting in public parks; it's
going to take some fine bullshit to rationalize their utility, their
human dignity, their inherent worth, and the pressing need to put them
up in subsidized homes and throw good money after bad. The argument
becomes even more challenging when the money comes out of \emph{your
pockets}. Oh, in case you're wondering, you don't get to spend other
people's money!

How much are \emph{you} (just you) willing to pay to help the homeless?
When asking myself such questions, I play an order of magnitude game.
Here's how it goes. John, would you pay one dollar to help the homeless?
I'm a good sport, so sure. Have a dollar.

Would you pay ten dollars to help the homeless? Sure, I can pony up ten
bucks. Would you pay one hundred dollars to help the homeless? Now I'm
beginning to think about the money. Is that wreck of a human being
degrading public spaces worth a hundred bucks? Ok, I will cough up a
hundred bucks, but this had better be a one-off. Would you pay one
thousand dollars to help the homeless? Now I am absolutely thinking
about the money. With a thousand bucks, I could get a decent camera lens
or pay for five years of Amazon Prime. Let's face it: there are a
million better ways to spend your money. OK, would you pay ten thousand
dollars to help the homeless? Uh --- hard no! The order of magnitude
game quickly sets bounds on your compassion. I care roughly one thousand
\emph{per annum} for the
homeless\footnote{Not matter how loudly woke grammar checkers bitch about my harmful and
hurtful tone, I will not choose another term for ``the homeless.''
Some things hurt and covering them with euphemisms doesn't help.} %\protect\hypertarget{fnref1}{\protect\hyperlink{fn1}{\textsuperscript{1}}}.
If government financial rapists (tax authorities) come for more, I will
bitterly resent it and use every electoral opportunity to punish the
rapists. I identify as a \emph{compassion-free device!}

Because our ``compassion'' is biologically limited to a few people,
crafting ``compassionate government policy'' is a fool's errand. I don't
want to pay for your compassion; I doubt you want to pay for mine. We
can't even agree on what constitutes compassion or devise objective
measures for it. We have built many devices to measure electron mass,
but I challenge you to build a \emph{compassion meter}. You will quickly
discover that ``compassion'' has no physical basis. At best,
``compassion'' is a word associated with the behavior of some social
animals that derive evolutionary benefits from cooperation. Beyond that,
compassion is airy fairy sky fairy nonsense, and basing public policy on
it is pure idiocy.

Hence, insurance companies, corporations, governments, and even
homeowner associations base policies on things that can be measured,
like cool, clear cash. And when such stark measures are applied, it
turns out that society prefers dead liabilities.

%\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
%
%\begin{enumerate}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn1}{}}%
%  Not matter how loudly woke grammar checkers bitch about my harmful and
%  hurtful tone, I will not choose another term for ``the homeless.''
%  Some things hurt and covering them with euphemisms doesn't
%  help.\protect\hyperlink{fnref1}{↩︎}
%\end{enumerate}



%\end{document}

