%\input{bmamblenew.tex}

\subsection*{\href{https://analyzethedatanotthedrivel.org/2023/03/16/some-modest-proposals-for-svbish-bank-bailouts/}{Some Modest Proposals for SVBish Bank Bailouts}}
\addcontentsline{toc}{subsection}{Some Modest Proposals for SVBish Bank Bailouts}


\noindent\emph{Posted: 16 Mar 2023 22:58:04}
\vspace{6pt}

Here we go again another criminal bank bailout. Don't even try and argue
that the
\href{https://www.msn.com/en-us/money/companies/the-hideous-double-standards-of-the-silicon-valley-bank-bailout-bailouts-for-me-not-for-thee-opinion/ar-AA18IzEZ}{SVB
bailout} isn't a bailout. You can tell it's a bailout from all the
frantic explanations the Biden gang is pushing telling us how giving
funds, way over FDIC deposit insurance limits, to deposit holders in
2023 fundamentally differs from giving funds, way over insurance limits,
to others in 2008 for like --- \emph{totally other reasons.} Yes, public
money is being flushed down the toilet without consent, but this time
it's piss rather than shit in the pot. Trust us; it's so, so different.

Unfortunately, the hard arithmetic fact remains that FDIC deposit
insurance rules were revamped \emph{post facto}, without discussion, for
SVB, and some depositors are getting far more than they should at the
expense of the rest of us. Now braindead Biden assures us that we won't
lose a dollar and that this is a regrettably necessary step to shore up
the banking system. This sounds \emph{very familiar} and I am \emph{very tired}
of it. But once again the morons in Washington have injected a massive
dose of moral hazard into the system. Why would politically connected
\emph{depositors} bear even tiny private deposit insurance expenses when
their Washington fuck toys line up to tongue cash up their bungholes?

After 2008 any competent financial officer should have factored bank
instability into their calculations and plans. If you are stupid enough
to put all your eggs in one basket and said basket tips over, well
that's on you. \emph{Never assume things are fine because they never
fucking are!} Why the hell is it necessary to explain this to adults?

Moral hazard is a nasty trans-bitch genie. Once \emph{they} are out of
the lamp, \emph{they} delight in wreaking innocent bystanders at their
own expense. If only there was something we could do to mitigate the
damage. How about this?

\begin{quote}
I want a full, publicly disclosed list, of every single SVB depositor
that takes more than standard FDIC amounts. The list should include the
amount, name, and address of any individual or company that exceeds FDIC
limits. Furthermore, the list should be published on a system like
GitHub so the public can make as many secure copies as they deem
fit.
\end{quote}

Now, many will squeal that this is a horrible breach of banking privacy
and that making such information public might endanger people and
further rattle brittle markets

\emph{I don't fucking care!}

If you are so concerned that your privacy is being breached then don't
exceed FDIC limits. I would be willing to bet that a fair number of SVB
startup bros would prefer to keep their names off the bailout list ---
even if it costs them big time. Also, anyone choosing privacy over
public slush probably doesn't need it.

\emph{I'm not done here.}

The idiots in Washington have demonstrated over and over again that most
of them are, in Heinlein's immortal words, ``candidates for protective
restraint.'' They need adult supervision, meaning the rest of us must
monitor these MIBs (manifestly ignorant beings) twenty-four-seven. Let's
start with their tax returns.

Remember all the fuss about Trump's tax returns? Trump is a mendacious
fat \emph{n'th} rate intellect but he knows how to game the system. I would
argue it's about the only thing he knows. I submit that one-time tax
returns are not enough for nitwits like Trump or nonentities like Biden.

\begin{quote}
I want full yearly forensic IRS audits of the President, Vice
President, every sitting member of congress, the senate, the supreme
court, top officials in the executive branch like the Attorney General
and Head of the Federal Reserve, their immediate family members, and
their top ten political donors. Furthermore, said audits must be
published in excruciating detail on systems like GitHub so the public
can make as many secure copies as they deem fit.
\end{quote}

Of course, the political class will scream that this is a horrible,
horrible imposition. That it makes it too easy for friends and foes to
data-mine public officials, that it will deter donors, that it will
discourage \emph{good people} (don't make me laugh) from seeking public
office, that it endangers family members and poor innocent associates,
that it distracts from the \emph{real issues} (still not laughing) like
climate change.

\emph{Again, I don't fucking care!}

Here's the thing congress-creeps. If you feel you have things to hide,
maybe, just maybe, you're not fucking fit for office! Maybe your head is
better mounted on a pike.



%\end{document}
 
