%\input{bmamble.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2017/09/13/stop-writing-dead-tree-letters-to-the-editor/}{Stop Writing Dead Tree Letters to the Editor}}
\addcontentsline{toc}{subsection}{Stop Writing Dead Tree Letters to the Editor}


\noindent\emph{Posted: 13 Sep 2017 18:21:01}
\vspace{6pt}

I don't pay for newspapers anymore and neither should you. The dead tree
media is truly and absolutely dead. It serves no function in the modern
world and like the
\href{https://www.youtube.com/watch?v=yzDHHMWDC_k}{What Happened
Hildabeast}, it needs to
\href{https://www.acronymfinder.com/FOAD.html}{FOAD}. The collapse of
print media and the incontinent wailing of unemployed
\href{http://smallestminority.blogspot.com/2015/07/quote-of-day-democratic-operatives-with.html}{political
operatives with bylines} has been duly noted by many and, as much as I
love flogging dead horses, that is not why I \emph{blogforth} today.
There is one anachronistic section of dead tree newspapers that still
amuses me: letters to the editor.

\emph{Who the hell writes letters to the editor these days?}

Did these letter writers just wake from a long Rip Van Winkle nap and
take up where they left off in the 1960s? Oh, and it definitely is the
1960s. The overwhelming majority of dead tree letters clearly come from
the fat furrowed brows of retired old boomer farts that mistake
constipation for thought.

As I have said before, even though I am a boomer, nobody hates them more
than me.

There's no point in rehashing the infinitely rehashed. Modern letters to
the editor lack the intelligence of blog posts, the pithiness of tweets,
the sublimity of poetry or the seriousness of books. They're vain
displays. Look at me; I've bamboozled an idiot newspaper editor.
Congratulations, you've surmounted a bar low enough for Conga champions.

I think I speak for all of us when I say that we've had enough of your
letter antics. Please find your way to the nearest online comments
section and unleash your inner troll. And, if you must debase yourself
to a larger audience \emph{start a blog!}



%\end{document}

