%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2022/07/24/stupid-j-jupyter-tricks/}{Stupid J Jupyter Tricks}}
\addcontentsline{toc}{subsection}{Stupid J Jupyter Tricks}


\noindent\emph{Posted: 24 Jul 2022 23:29:27}
\vspace{6pt}

Continuing with my software irritant dispatching theme: today's irritant
- including \emph{syntax colored code} in blogs, \LaTeX, Word, and other
documents. This one is a persistent pain in the ass; especially for
users of idiosyncratic programming languages. We all have our favorite
hacks and workarounds; today I am sharing one of mine: using
\href{https://jupyter.org/}{jupyter} to syntax color J code.

A few years ago \href{https://github.com/martin-saurer}{Martin Saurer}
made an outstanding contribution to the
\href{https://code2.jsoftware.com/wiki/Main_Page}{J programming
language} community. He created a
\href{https://github.com/martin-saurer/jkernel}{jupyter kernel for J.}
If you don't know what jupyter is please crawl out from under your rock
and join the rest of us in the 21\textsuperscript{st} century.

As I have said before jupyter notebooks are simply the \emph{correct}
way to present complex ``executable'' technical documents that contain
heavy doses of mathematics, program code, and graphics. I'm not the only
one that holds this opinion: many concur. It would be an understatement
to say that jupyter has been a success. It's now a dominant tool in many
disciplines. If you're not using it you are missing out on one of the
most useful open-source programming tools available.

I came to jupyter from the \emph{pythonverse}. The JSON based \texttt{ipynb} notebook format
originated there and initially stood for \textbf{I}nteractive
\textbf{PY}thon \textbf{N}ote\textbf{B}ook, but in one of the best
software design decisions ever made, the creators of jupyter decided to
make it \emph{programming language agnostic.} This means any
programming language can plug into jupyter if it implements a
well-defined kernel interface. This is what Martin implemented. Now,
many programming languages support jupyter. It's become an expected
facility, and if it's missing, well that's a good reason to use another
programming language.

Martin's J kernel works very well and I use it all the time, but there
are a few ways the J kernel, and jupyter kernels in general, could be
improved.

%\hypertarget{debugging-notebook-code}{%
\subsubsection*{Debugging notebook code}%\label{debugging-notebook-code}}

Debugging notebook code is not as polished as it could be. Kernels are
typically ``invisible'' executables that respond to requests sent from
the notebook server. Most kernels stay in the background and do not
provide standard language-specific programming environments. Usually,
this isn't much of a problem, but when debugging complex programs it
would be handy to push a button and pop up a standard debugger. In J's
case, a JQt or JHS session would appear containing all the code loaded
or created by the notebook. You could then debug and modify your code,
then pop over to the notebook session to try it out.

Right now the J kernel does not ``pop up'' visible J sessions but you
can achieve something similar by extracting J notebook code as a J
script and executing it in another JQt or JHS session. jupyter makes
this easy!

%\hypertarget{stupid-j-jupyter-trick-1---export-notebook-code-as-a-j-script}{%
\subsubsection*{Stupid J Jupyter Trick \#1 - export notebook code as a J
script}%\label{stupid-j-jupyter-trick-1---export-notebook-code-as-a-j-script}}

jupyter can download notebooks in a variety of formats. One of the
formats provided by the J kernel is \texttt{ijs} or J script. Go to the
\textbf{File} menu, select \textbf{Download as}, then pick \textbf{J
(.ijs)}. jupyter will extract all the \emph{J code cells} in the
notebook \emph{in cell order} and write a script file to wherever you
want it. I usually save such scripts in the J temp directory \texttt{jpath
\textasciitilde temp} where they can be conveniently loaded and run.

When you run a downloaded J notebook script in another J session it
\emph{essentially}\footnote{Some care must be taken when developing J jupyter notebooks to
guarantee exported scripts accurately recreate kernel states.} recreates the notebook kernel state.

%\hypertarget{inserting-j-code-into-notebooks}{%
\subsubsection*{Inserting J code into
notebooks}%\label{inserting-j-code-into-notebooks}}

Extracting J code from notebooks for debugging is useful but oddly the
inverse, inserting J code into notebooks, is even more useful. As
previously noted, jupyter can export notebooks in many formats. In
particular, it can generate HTML, \LaTeX, Markdown, and PDF versions of
notebooks. I've found the generated \LaTeX, HTML, and Markdown formats
extremely handy.

%\hypertarget{stupid-j-jupyter-trick-2---j-code-notebook-insertion}{%
\subsubsection*{Stupid J Jupyter Trick \#2 - J code notebook
insertion}%\label{stupid-j-jupyter-trick-2---j-code-notebook-insertion}}

If you're looking for \emph{a quick and dirty way to syntax color J
code} do the following:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Create a blank jupyter notebook.
\item
  Open a J script in your favorite editor.
\item
  Cut and Paste the script into a jupyter code cell.
\item
  Download the notebook as HTML or PDF.
\end{enumerate}

jupyter will nicely syntax color your code. It even does a decent job of
breaking lines. \href{https://github.com/bakerjd99/jacks/tree/master/brandxmp/jupyter}{The GitHub files}
\texttt{brandxmp.ijs.pdf} and \texttt{brandxmp.ijs.html} are examples of what you get right out of the box.

%\hypertarget{stupid-j-jupyter-trick-3---smarter-j-code-notebook-insertion}{%
\subsubsection*{Stupid J Jupyter Trick \#3 - smarter J code notebook
insertion}%\label{stupid-j-jupyter-trick-3---smarter-j-code-notebook-insertion}}

The quick and dirty method is simple and handy but it's of limited use
when preparing complex \LaTeX\ documents. With \LaTeX, you want more than
just code. You want cross-references, web links, footnotes, mathematical
expressions, graphics, indexes, appendices, and other
\href{https://www-cs-faculty.stanford.edu/~knuth/lp.html}{\emph{literate
programming}} goodies. It's much easier to achieve such ends if your J
code is split over many cells. The following verb does this.


 \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
%\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n+nv}{ipynbfrjod}\PY{o}{=:}\PY{n+nf}{3 : 0}

\PY{c+c1}{NB.*ipynbfrjod v\PYZhy{}\PYZhy{} extract J  words from JOD  and insert in blank}
\PY{c+c1}{NB. jupyter notebook.}
\PY{c+c1}{NB.}
\PY{c+c1}{NB. monad:  clIpynb =. ipynbfrjod blclNames}
\PY{c+c1}{NB.}
\PY{c+c1}{NB.   NB. examples use docs and utils}
\PY{c+c1}{NB.   require \PYZsq{}general/jod\PYZsq{}}
\PY{c+c1}{NB.   od ;:\PYZsq{}docs utils\PYZsq{}}
\PY{c+c1}{NB.}
\PY{c+c1}{NB.   nbj=: ipynbfrjod ;:\PYZsq{}sha1 sha1dir\PYZsq{}}
\PY{c+c1}{NB.   nbj write \PYZsq{}C:\PYZbs{}Users\PYZbs{}baker\PYZbs{}jupyter\PYZus{}notebooks\PYZbs{}test0.ipynb\PYZsq{}}
\PY{c+c1}{NB.}
\PY{c+c1}{NB.   nbj=: ipynbfrjod \PYZcb{}. grp \PYZsq{}ipynb\PYZsq{}}
\PY{c+c1}{NB.   nbj write \PYZsq{}C:\PYZbs{}Users\PYZbs{}baker\PYZbs{}jupyter\PYZus{}notebooks\PYZbs{}ipynb\PYZus{}onself.ipynb\PYZsq{}}

\PY{c+c1}{NB. require \PYZsq{}general/jod\PYZsq{} !(*)=. disp}
\PY{n+nv}{jc}\PY{o}{=.} \PY{n+nv}{disp}\PY{o}{\PYZam{}}\PY{o}{.}\PY{o}{\PYZgt{}} \PY{n+nd}{y}

\PY{c+c1}{NB. markdown sections with word name}
\PY{n+nv}{sec}\PY{o}{=.} \PY{n+nv}{dblquote} \PY{p}{(}\PY{o}{\PYZlt{}}\PY{n+nv}{MDSECTION}\PY{o}{,}\PY{n+nv}{JWORDMARK}\PY{p}{)} \PY{o}{,}\PY{o}{\PYZam{}}\PY{o}{.}\PY{o}{\PYZgt{}} \PY{n+nd}{y}
\PY{n+nv}{sec}\PY{o}{=.} \PY{p}{(}\PY{o}{\PYZlt{}}\PY{n+nv}{NBJCELLBEGst}\PY{p}{)} \PY{o}{,}\PY{o}{\PYZam{}}\PY{o}{.}\PY{o}{\PYZgt{}} \PY{n+nv}{sec} \PY{o}{,}\PY{o}{\PYZam{}}\PY{o}{.}\PY{o}{\PYZgt{}} \PY{o}{\PYZlt{}}\PY{n+nv}{NBJCELLBEGen}

\PY{c+c1}{NB. j code to quoted list of python strings notebook format}
\PY{n+nv}{nbj}\PY{o}{=.} \PY{o}{\PYZlt{}}\PY{o}{;}\PY{o}{.}\PY{l+m+mi}{\PYZus{}2}\PY{o}{@}\PY{p}{(}\PY{n+nv}{REVPYESCAPECHRS}\PY{o}{\PYZam{}}\PY{n+nv}{changestr}\PY{p}{)}\PY{o}{@}\PY{n+nv}{tlf}\PY{o}{\PYZam{}}\PY{o}{.}\PY{o}{\PYZgt{}} \PY{n+nv}{jc}
\PY{n+nv}{nbj}\PY{o}{=.} \PY{o}{;}\PY{o}{\PYZam{}}\PY{o}{.}\PY{o}{\PYZgt{}} \PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZsq{}} \PY{o}{,} \PY{n+nv}{L}\PY{o}{:} \PY{l+m+mi}{0} \PY{p}{(}\PY{o}{\PYZlt{}}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZbs{}}\PY{l+s}{n}\PY{l+s}{\PYZdq{}}\PY{l+s}{,}\PY{l+s}{\PYZsq{}}\PY{o}{,}\PY{n+nv}{LF}\PY{p}{)} \PY{o}{,}\PY{o}{\PYZti{}} \PY{n+nv}{L}\PY{o}{:} \PY{l+m+mi}{0} \PY{n+nv}{nbj}
\PY{n+nv}{nbj}\PY{o}{=.} \PY{o}{,}\PY{o}{\PYZam{}}\PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZdq{}}\PY{l+s}{\PYZsq{}}\PY{o}{\PYZam{}}\PY{o}{.}\PY{o}{\PYZgt{}} \PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZbs{}}\PY{l+s}{n}\PY{l+s}{\PYZdq{}}\PY{l+s}{,}\PY{l+s}{\PYZsq{}}\PY{o}{\PYZam{}}\PY{n+nv}{beforelaststr}\PY{o}{\PYZam{}}\PY{o}{.}\PY{o}{\PYZgt{}} \PY{n+nv}{nbj}
\PY{n+nv}{nbj}\PY{o}{=.} \PY{n+nv}{sec} \PY{o}{,}\PY{o}{\PYZam{}}\PY{o}{.}\PY{o}{\PYZgt{}} \PY{n+nv}{nbj} \PY{o}{,}\PY{o}{\PYZam{}}\PY{o}{.}\PY{o}{\PYZgt{}} \PY{o}{\PYZlt{}}\PY{n+nv}{NBJCELLEND}
\PY{n+nv}{toJ} \PY{n+nv}{NBHEADER} \PY{o}{,} \PY{p}{(}\PY{n+nv}{LF} \PY{o}{,}\PY{o}{\PYZti{}} \PY{l+s}{\PYZsq{}}\PY{l+s}{,}\PY{l+s}{\PYZsq{}}\PY{o}{\PYZam{}}\PY{n+nv}{beforelaststr} \PY{o}{;}\PY{n+nv}{nbj}\PY{p}{)} \PY{o}{,} \PY{n+nv}{NBTRAILER}
\PY{n+nl}{)}
\end{Verbatim}
\end{tcolorbox}

After loading J words into cells all the jupyter export facilities are
immediately available. Examples of jupyter outputs exploiting this hack
are \href{https://github.com/bakerjd99/jacks/tree/master/ipynbfrjod}{available on GitHub:} see \texttt{ipynb\_onself.ipynb} and \texttt{ipynb\_onself.pdf}.

To use \texttt{ipynbfrjod} download \texttt{ipynb.ijs}
and the corresponding document \texttt{ipynb.pdf}.
All these files \href{https://github.com/bakerjd99/jacks/tree/master/ipynbfrjod}{are on
GitHub}. Help yourself!


 \textbf{Postscript:} If you already have a recent version of J installed
you can directly install this script as a J \texttt{addon} by typing the
following commands in a JQt or JHS session.

\begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
%\prompt{In}{incolor}{ }{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{NB. install addon files in ~addons/jacks}
\PY{n+nv}{install} \PY{l+s}{\PYZsq{}}\PY{l+s}{g}\PY{l+s}{i}\PY{l+s}{t}\PY{l+s}{h}\PY{l+s}{u}\PY{l+s}{b}\PY{l+s}{:}\PY{l+s}{b}\PY{l+s}{a}\PY{l+s}{k}\PY{l+s}{e}\PY{l+s}{r}\PY{l+s}{j}\PY{l+s}{d}\PY{l+s}{9}\PY{l+s}{9}\PY{l+s}{/}\PY{l+s}{j}\PY{l+s}{a}\PY{l+s}{c}\PY{l+s}{k}\PY{l+s}{s}\PY{l+s}{h}\PY{l+s}{a}\PY{l+s}{c}\PY{l+s}{k}\PY{l+s}{s}\PY{l+s}{\PYZsq{}}

\PY{c+c1}{NB. list installed files}
\PY{n+nv}{dir} \PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZti{}}\PY{l+s}{a}\PY{l+s}{d}\PY{l+s}{d}\PY{l+s}{o}\PY{l+s}{n}\PY{l+s}{s}\PY{l+s}{/}\PY{l+s}{j}\PY{l+s}{a}\PY{l+s}{c}\PY{l+s}{k}\PY{l+s}{s}\PY{l+s}{\PYZsq{}}

\PY{c+c1}{NB. load script}
\PY{n+nv}{load} \PY{l+s}{\PYZsq{}}\PY{l+s}{\PYZti{}}\PY{l+s}{a}\PY{l+s}{d}\PY{l+s}{d}\PY{l+s}{o}\PY{l+s}{n}\PY{l+s}{s}\PY{l+s}{/}\PY{l+s}{j}\PY{l+s}{a}\PY{l+s}{c}\PY{l+s}{k}\PY{l+s}{s}\PY{l+s}{/}\PY{l+s}{i}\PY{l+s}{p}\PY{l+s}{y}\PY{l+s}{n}\PY{l+s}{b}\PY{l+s}{.}\PY{l+s}{i}\PY{l+s}{j}\PY{l+s}{s}\PY{l+s}{\PYZsq{}}
\end{Verbatim}
\end{tcolorbox}


%\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
%
%\begin{enumerate}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn1}{}}%
%  Some care must be taken when developing J jupyter notebooks to
%  guarantee exported scripts accurately recreate kernel
%  states.\protect\hyperlink{fnref1}{↩︎}
%\end{enumerate}


%\end{document}

