%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2023/04/07/sympathy-for-ptolemaic-epicyclers/}{Sympathy for Ptolemaic Epicyclers}}
\addcontentsline{toc}{subsection}{Sympathy for Ptolemaic Epicyclers}


\noindent\emph{Posted: 07 Apr 2023 20:56:11}
\vspace{6pt}

Histories of science tend to cast ``old theory holdouts'' as uncouth,
backward, prejudiced, and stinky nitwits. If you don't immediately jump
on the shiny new science bandwagon you're on the \emph{wrong side of
history} and doomed to a legacy of ridicule and disdain. Mind you, these
\emph{just so} histories fail to mention that most new theories are
dead-ass wrong and that you need solid reasons for abandoning ideas that
more or less work. The classic ``old theory people are morons'' tale
appropriately revolves around astronomy's famous Earth-centered versus
Sun-centered debate. The standard tale casts Copernicus as a brave man
of science (even though he didn't fully publish while alive to avoid
censure) waging righteous war with hidebound doctrinaire
church-sanctioned
\href{https://microcosmos.uchicago.edu/ptolemy/astronomy.html}{Ptolemaic
astronomers} and their idiotic notion that the sky spins around the
Earth. How stupid is that?

Actually, it wasn't stupid. The Ptolemaic system was complicated, lacked
a physical basis, and required constant tweaking and adjustment, (sounds
like modern software), but at its core, the system was \emph{deeply
empirical}. It was based on watching the damn sky and here's the kicker;
it kind of worked. The epicylers predicted the planets' locations, the
moon's phases, when stars rose and set, and even some lunar and solar
eclipses. Ptolemaic calculations lacked modern precision but they were
good enough for naked-eye astronomers. When astronomers switched to
telescopes it quickly became apparent to anyone that cared to look that
Ptolemy's system was off and needed fixing. Kepler, Newton, and others
provided the fix and the new celestial regime was \emph{demonstrably
better} than Ptolemy's, and, as a bonus, Newtonian gravity finally
offered deep reasons for why orbits took observed shapes.

This all happened centuries after Copernicus, and because his
heliocentric model was essentially correct, people have forgotten that
Copernicus Version 1.0 made crappy predictions. The first iterations of
the heliocentric model did not match the accuracy of the hidebound
doctrinaire old fart Ptolemaic system; this is what fueled resistance
to the new model. Far from being morons, the Ptolemians were just being
good skeptical philosophers. Sun-centered models were not new even in
the 15\textsuperscript{th} century. Aristarchus speculated about them
around 200 BCE, and I'd bet big bucks the idea was old even then.
Sun-centered models did not immediately catch on because \emph{theories must
pay their way.} A nice idea that doesn't feed you, (I'm looking at you
Multiverse, and you too String Theory), will be tossed aside for
ones that do! Ptolemaic astronomy endured because it paid the bills and
fed the hungry. Copernicus Version 1.0 did not.

All of this was driven home by my recent development of a
\href{https://github.com/bakerjd99/jackshacks/blob/main/riseset.ijs}{J
script \texttt{riseset}} for calculating when officially named
\href{https://www.iau.org/}{International Astronomical Union} stars
(IAU) culminate in my backyard. The script is available on GitHub and
can be installed and run on current J systems with:

%\hypertarget{cb1}{}
\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{load }\StringTok{\textquotesingle{}pacman\textquotesingle{}}
\CommentTok{NB. files from https://github.com/bakerjd99/jackshacks}
\NormalTok{install }\StringTok{\textquotesingle{}github:bakerjd99/jackshacks\textquotesingle{}}

\NormalTok{load }\StringTok{\textquotesingle{}\textasciitilde{}addons/jacks/riseset.ijs\textquotesingle{}}
\NormalTok{location\_yellowstone }\DecValTok{0}
\CommentTok{NB. IAU stars rising/setting over Old Faithful}
\NormalTok{fmt\_today iau\_today }\DecValTok{0}
\end{Highlighting}
\end{Shaded}

Most of the algorithms in \texttt{riseset} derive from Jean Meeus's book
\href{https://archive.org/details/astronomicalalgorithmsjeanmeeus1991}{\emph{Astronomical
Algorithms}} with supplementary material from
\href{https://neoprogrammics.com/nutations/}{Jay Tanner} and
\href{https://eclipse.gsfc.nasa.gov/SEhelp/deltatpoly2004.html}{NASA's
eclipse site}. If you peruse the code or browse the source books you
will quickly see that modern astronomical calculations are complicated
and require constant tweaking --- just like the old Ptolemaic system.
The algorithms in Meeus will need updating every century or so and it is
the update process that distinguishes modern calculations from the
Ptolemaic system. Modern calculations are based on solving \emph{n-body}
celestial mechanics problems. The resulting, mostly series solutions,
form the basis of working algorithms like Tanner's
\href{https://neoprogrammics.com/nutations/}{nutation programs}.
\emph{N-body} problems are grounded in gravitational theories and there
was nothing like them in Ptolemy, but from the perspective of a backyard
amateur astronomer rolling his own code, the differences between modern
and Ptolemaic calculations seem moot. While working out \texttt{riseset} I
acquired a new respect and sympathy for the ancient epicyclers. They
carried out decent approximations, without computers, or even place
value arithmetic, and came up with answers that almost matched what they
saw. Not exactly the work of morons.



%\end{document}
 

