%\input{bmamble.tex}

\subsection*{\href{http://bakerjd99.wordpress.com/2014/01/15/the-great-verizon-data-famine/}{The Great Verizon Data Famine}}
\addcontentsline{toc}{subsection}{The Great Verizon Data Famine}


\noindent\emph{Posted: 16 Jan 2014 04:11:02}
\vspace{6pt}

The other day I visited my local Verizon store for the fourth freaking
time! My mission was simple: upgrade my goddamn phone and change our
account from my wife's name to mine. In sane retail environments
long-standing customers with impeccable payment histories get treated
like royalty. I know it will come as a shock to all you parasitic
socialists out there but \emph{it is the paying customer, and only the
paying customer, that is keeping civilization's lights on!} I understand
and appreciate the need for businesses to make profits and for the last
three years Verizon has profited from my patronage and I have benefited
from their excellent cell service. We had a mutually beneficial
relationship but now I'm wondering if this marriage can be saved.

I have no technical complaints about Verizon. The engineers at Verizon
clearly know what they are doing but it looks like the administrative
and sales division's model themselves on the
\href{http://www.urbandictionary.com/define.php?term=DMV}{DMV} or
Obama's \href{http://obamacaregov.us/}{healthcrap.gov}. I've seen this
before. Most software companies harbor competent to brilliant
programmers yet are often fronted by ethically challenged sales baboons.
My father, a retired petroleum engineer, used to say, ``It's a good
thing oil is so valuable and customers are beating down our doors
because head office couldn't sell shit to a house fly.'' I know it's not
my place, as a motivated shit seeking house fly, to question the sales
practices of multi-billion dollar enterprises but, to quote a very wise
old white guy, ``you've confused me with
\href{http://www.urbandictionary.com/define.php?term=call\%20someone\%20who\%20gives\%20a\%20shit}{someone
who gives a crap.}''

\medskip

When I first walked into the Verizon store I wanted an accurate answer
to this question:

\medskip

\textbf{How much will my monthly bill be if:}

\begin{enumerate}
\item
  \textbf{I pay the full retail cost of the phone upfront.} Old white
  guys do not buy on credit because old white guys have learned the hard
  way that \emph{buying anything on credit means you eventually pay
  more.} I am not interested in paying more. I have a very bad attitude
  when it comes to paying more. My butthole has been reamed often
  enough, long enough and hard enough that it's now operating on a
  strict cash upfront basis.
\item
  \textbf{And if I have an uncapped 4G data plan.} Cell providers
  constantly go on about their unlimited data plans yet down in the fine
  print --- old white guys always read the fine print --- you typically
  see ``limited to two gigabytes per month.'' Two gigabytes is not
  unlimited, four gigabytes is not unlimited, fifty
  \href{https://en.wikipedia.org/wiki/Yottabyte}{yottabytes} is not
  unlimited; unlimited means arbitrarily high.
\end{enumerate}

It took two trips to the same store to get a simple price quote. The
quoted rate was \$69.99 per month. This is close to my current rate and
since I'm burning another \$39.99 per month on Internet cable it looked
like I could cancel cable, divert all my residential Internet traffic
through an iPhone 4G hot spot and save about thirty bucks a month.

I realized I would have to go on a data diet. 4G connections are faster
than 3G but 4G is still \emph{much slower} than cable Internet. The
cable provider in St. Louis, Charter,\footnote{
\href{https://www.charter.com/}{Charter} Internet is a binary
operation. When it's working it works very well, but over that last
three years I've watched it go down more often than a cheap street
prostitute. Right now it's down. Charter outages are annoying but
they're usually quickly resolved.
} runs at 30 megabits per second. This is about five times faster than 4G.
4G is okay for blogging, modest sub-gigabyte downloads, uploading a few
dozen high-resolution pictures and normal web browsing. 4G is not up to
\emph{irritant free} HD streaming. You can stream but the image is often
downgraded to a blocky low resolution mess. I planned on giving up
streaming because TV, whether broadcast or streamed, is still mostly
time-wasting garbage. I was looking forward to reallocating my streaming
time to good old-fashioned paper\footnote{
  \href{http://online.wsj.com/news/articles/SB10001424052702304870304577490950051438304}{EBooks
  are developing nasty data mining habits.} I have no desire to expose
  the precise details of my reading to busy bodies. This doesn't mean I
  am giving up on eBooks but I am giving up on on-line eBooks. I now
  demand~complete control of the eBook file on a device that I can shut
  off logging and communication. \emph{If you don't control it you
  cannot trust it.}
} book reading.

After doing my research, considering the options and allocating funds I
returned to the same Verizon store I had visited three times with the
intention of plunking down the full cost of an iPhone 5s and signing
another two-year service contract at the price I was previously quoted.
Then things went horribly wrong. First, we had to call my wife to change
the name on our account from hers to mine. The simple act of changing
the account name voided my unlimited data. I went from an uncapped plan
to a two gigabyte plan. Then, as a final affront, it turns out that you
if you actually want to use your iPhone's hot spot you need to pay
another \$30.00 per month on top of your normal data plan. In other
words my bill would be a few cents shy of \$100.00 per month. So, I
would pay roughly the same as my current Verizon and Charter bills
combined and end up with a connection that is five times slower. Old
white guys are slow and stupid but not that stupid.

Instead of walking out of the store with a shiny new iPhone 5s and
another two-year contract I left with my old iPhone 4 and a downgraded,
but equally expensive data plan. I am now looking at other options. I
will probably retain cable and cut off all cell phone data. Most of my
cell phone data moves over Wi-Fi so why pay Verizon, or another
provider, \$30.00 bucks per month to keep up on Twitter tripe. Verizon's
sales did a bang up job here. They convinced a loyal and reasonably
happy customer that it's time to take a serious look at the competition.
I was planning on a data diet but not a data famine.
\href{https://www.youtube.com/watch?v=XMblePw7eJs}{Can you hear me now!}

%\begin{center}\rule{3in}{0.4pt}\end{center}
%
%\begin{enumerate}
%\item
%  \href{https://www.charter.com/}{Charter} Internet is a binary
%  operation. When it's working it works very well, but over that last
%  three years I've watched it go down more often than a cheap street
%  prostitute. Right now it's down. Charter outages are annoying but
%  they're usually quickly resolved.\hyperref[fnref1]{↩}
%\item
%  \href{http://online.wsj.com/news/articles/SB10001424052702304870304577490950051438304}{EBooks
%  are developing nasty data mining habits.} I have no desire to expose
%  the precise details of my reading too busy bodies. This doesn't mean I
%  am giving up on eBooks but I am giving up on on-line eBooks. I now
%  demand~complete control of the eBook file on a device that I can shut
%  off logging and communication. \emph{If you don't control it you
%  cannot trust it.}\hyperref[fnref2]{↩}
%\end{enumerate}



%\end{document}