%\input{bmamble.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2014/08/31/there-will-never-be-a-literature-of-reality/}{There will never be a Literature of Reality}}
\addcontentsline{toc}{subsection}{There will never be a Literature of Reality}


\noindent\emph{Posted: 31 Aug 2014 20:20:13}
\vspace{6pt}

The first job of the myth maker is to shrink the universe. The shrinkage
occurs along all~dimensions: time, space and mind. You see this
everywhere. Immortal vampires and wizards are, at most, a few
thousand~years old: younger than many \emph{real} trees. Grand science
fiction star empires seldom span a single galaxy~in a universe of
hundreds of billions. Time travelers never set their machines to zero or
infinity; they have no~interest in creation or ultimate ends. The
demigods, super AIs, and other transcendent beings
brood~unproductively, without original ideas, for millennia. Remember
when Elrond reminisced about ``being there'' when Sauron was~struck down
three thousand Middle Earth years ago. In all that time the great, wise,
and nearly~immortal, elves of Middle Earth did not move beyond simple
swords. How quickly the battle for Gondor would have~gone with a few
dozen
\href{http://www.marines.com/operating-forces/equipment/vehicles/m1a1-abrams-tank}{Abrams
tanks} and a couple squadrons of
\href{http://en.wikipedia.org/wiki/Fairchild_Republic_A-10_Thunderbolt_II}{Warthogs}.

It's hard to fault human authors for shrinking the universe. The real
universe, the utterly vast~and ancient universe slowly discovered by
modern science, is beyond all human scales. Imagine a~book that devoted
one word to every star in the observable universe. The number of stars
in the observable~universe is a unit that has a name. It's called a
\emph{Sagan} in honor of Carl Sagan.~The Sagan is currently estimated to
be around 7 x 10\textsuperscript{22}. ~Assuming there are one thousand
words per page our book would have 7 x 10\textsuperscript{19} pages.

If we read nonstop at a rate of one hundred pages per hour it would take
about~80 billion years, or six times the estimated age of the universe,
to read this book.~Yet, vast as this book is, it leaves out pretty much
everything.~There's no mention of the Earth or other planets: so many
pages and not~even a Hitchhiker's Guide to the Galaxy's
"\href{http://en.wikipedia.org/wiki/Mostly_Harmless}{mostly harmless.}"
Reality overwhelms imagination.~The magic of Harry Potter is piffle
compared to cosmic inflation.
\href{http://en.wikiquote.org/wiki/J._B._S._Haldane}{Haldane} was
right.~The universe is probably queerer than we can imagine and
certainly deeper than~we can grasp. Our meager fictions must float in
serene little bubbles lest they overrun~our short impatient lives.
\emph{There will never be a literature of reality.}



%\end{document}