%\input{bmamble.tex}

\subsection*{\href{https://analyzethedatanotthedrivel.org/2019/10/05/the-return-of-the-prodigal-blogger/}{The Return of the Prodigal Blogger}}
\addcontentsline{toc}{subsection}{The Return of the Prodigal Blogger}


\noindent\emph{Posted: 05 Oct 2019 20:07:35}
\vspace{6pt}

It's been ages since my last blog post. Yes, I've been a very, very bad
blogger. Lesser men would throw themselves on the metaphorical feet of
their readers and beg for forgiveness but if you're expecting apologies
you don't know me! I write for myself; if you choose to read my
ramblings, well that's on you.

Since my last entry I have:

\begin{enumerate}
%\tightlist
\item
  \textbf{Retired}. I finally pulled the plug on being a \emph{so-called
  productive member of society}. Now I'm an old Social Security
  draining parasite. \emph{Since I no longer pay net taxes I am
  effectively dead to the state and they would love it if I was actually
  dead.} Dead people are easier to finance. Unfortunately, I've always
  been on to the deep state and my new mission in life is to claw back
  every single tax dollar I ever paid with butt loads of interest. When
  I snuff off this mortal coil I am going stick you with a giant
  uncollectable I OWE FUCKING YOU! If you create financially
  unsustainable systems that encourage abuse, well guess what, you're
  going to get abused. God, I'm loving being a bitter old man; it's what
  I was born to be.
\item
  \href{https://conceptcontrol.smugmug.com/}{\textbf{\textbf{Continued
  to pursue my hobbies, especially photography.}}} This year (2019) I set
  the mini-goals of shooting, on average, one picture per day and
  scanning at least three hundred prints and slides. This may not sound
  like a lot but it takes \emph{me} time to select the best images,
  process RAW files, restore film scans, edit or hack pictures, write
  captions and
  \href{https://nbviewer.jupyter.org/github/bakerjd99/smugpyter/blob/master/notebooks/Setting\%20SmugMug\%20Print\%20Size\%20and\%20Geotag\%20Keywords\%20with\%20Jupyter\%20and\%20Python.ipynb}{compute
  keywords}. I treat every uploaded image as a
  \emph{milli}\emph{blogging} opportunity. Some of my image captions
  are longer than some of my blog posts. 
\item
  \textbf{Taken on some new family responsibilities and obligations}.
\item
  \textbf{Taken some trips}.
\item
  \href{https://github.com/bakerjd99/smugpyter}{\textbf{Worked on
  various personal software projects}.}
\end{enumerate}

\href{https://www.clarkefoundation.org/}{Arthur C. Clarke} once remarked
that only unimaginative people get bored. I've always had something on
my mind and I've always lived in my head. This has always been my
problem and my strength. With retirement, I am casting off my shriveled
shackles of pretense. I'm not even going to pretend to care about other
people's problems. I will think about what I find fascinating and do
what I find worthwhile.

\emph{Call it retirement privilege snowflakes!}

Now get back to work and pay your taxes you have old parasites to
support.



%\end{document}
 

