%\input{bmamble.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2022/06/12/the-techadent-internet-light-bulb-age/}{The \emph{Techadent} Internet Light Bulb Age}}
\addcontentsline{toc}{subsection}{The \emph{Techadent} Internet Light Bulb Age}


\noindent\emph{Posted: 12 Jun 2022 23:12:35}
\vspace{6pt}

Writing a blog that only spambots peruse affords unlimited editorial
freedom. Without readers to offend I am at liberty to blither on about
whatever holds my attention. And today, while sitting with pen in hand
and listening to soft rain fall, my attention is held, not by the war in
Ukraine, or the January 6th ``insurrection'' hearings, or the
interminable US gun control debate, or grotesque groomer travesties, or
rampaging
inflation\footnote{Hey Joe, you demented moron, Milton Friedman \href{https://www.wsj.com/articles/milton-friedman-biden-spending-inflation-free-market-carter-afghanistan-southern-border-11637014161}{is still very much in
  charge} when it comes to inflation!
}%\protect\hypertarget{fnref1}{\protect\hyperlink{fn1}{\textsuperscript{1}}},
or social, \emph{give me a frigging break}, justice! No, what's
commandeering my cortex is the Internet Light Bulb.

When I first saw Internet Light Bulbs a few pandemics ago I dismissed
them as another inane unnecessary frivolity: an LED
\emph{Twatter}\footnote{I don't refer to social network abominations by
  name.
}%\protect\hypertarget{fnref2}{\protect\hyperlink{fn2}{\textsuperscript{2}}}
if you will. Do we really need to control the color and intensity of our
light bulbs with a phone app? If you think the answer to this question
is ``Yes,'' please adjust your meds. Adding to their absurdity, early
Internet Light Bulbs were also ridiculously expensive. Two WiFi bulbs
could set you back one hundred bucks. WTF? Well, technology marches on,
(at least for the important things), and now you can pick up a pair of
WiFi bulbs for about ten bucks: not much more than ordinary LEDs.

In inflationary times it doesn't make sense to hold shrinking cash. So
I'm blaming Joe (Brandon) Biden and brown vagina Kamala Harris for my
inability to resist WiFi light
bulbs.\footnote{Blaming others for your bad choices isn't only for BIPOCs, POWs
  (People of White), can also play that
  game.
}%\protect\hypertarget{fnref3}{\protect\hyperlink{fn3}{\textsuperscript{3}}}
I traded a few ever-shrinking dollars for sparkly new Internet Light
Bulbs and they are easily the most useless things I own.

Not only are they magnificently useless they're also bringing old light
bulb jokes to life. Have you ever read a manual on light bulb
installation? Until yesterday I hadn't. While I was hooking the bulbs
into our home network, I couldn't believe I was providing tech support
for light bulbs! When my bulbs were configured, and all the necessary
software was installed, I was finally able to turn them on, and wait for
it, adjust their hue and intensity. If you've suspected that we are
living in a ``techadent age,''\footnote{\emph{Techadent:} the application of advanced technology to decadent
  and frivolous things.
}%'\protect\hypertarget{fnref4}{\protect\hyperlink{fn4}{\textsuperscript{4}}}
well, the Internet Light Bulb is its standard candle.

%\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

%\begin{enumerate}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn1}{}}%
%  Hey Joe, you demented moron, Milton Friedman is still very much in
%  charge when it comes to inflation!\protect\hyperlink{fnref1}{↩︎}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn2}{}}%
%  I don't refer to social network abominations by
%  name.\protect\hyperlink{fnref2}{↩︎}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn3}{}}%
%  Blaming others for your bad choices isn't only for BIPOCs, POWs
%  (People of White), can also play that
%  game.\protect\hyperlink{fnref3}{↩︎}
%\item
%  \leavevmode\vadjust pre{\hypertarget{fn4}{}}%
%  \emph{Techadent:} the application of advanced technology to decadent
%  and frivolous things.\protect\hyperlink{fnref4}{↩︎}
%\end{enumerate}



%\end{document}

