%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2021/06/25/the-zero-bullshit-sport-olympics/}{The Zero Bullshit Sport Olympics}}
\addcontentsline{toc}{subsection}{The Zero Bullshit Sport Olympics}


\noindent\emph{Posted: 25 Jun 2021 18:16:48}
\vspace{6pt}

We can thank the perpetually aggrieved and ever-complaining
``transgender community'' for the \emph{Zero Bullshit Sport Olympics}.
The ridiculous spectacle of huge male weightlifters, that conveniently
identified and competed as women, crushing smaller and weaker female
competitors on live global TV forced many to ask forbidden questions.

``Why are Olympic sports sexually segregated?''

``Does it really matter what the sex of a sprinter is?''

``Isn't the first \emph{human being}, male or female, to cross the
finish line the winner? That's how it works for horses; why not
humans?''

Once a forbidden question is widely asked and answers are earnestly
sought, unpredictable outcomes may ensue. The \emph{Zero Bullshit Sport
Olympics} was such an outcome. After the intolerable absurdity of
sexually segregated sports could no longer be countenanced it dawned on
many that the \emph{old} Olympics was chock full of bullshit sports in
dire need of elimination.

Bullshit sports were easy to identify. Any sport that depended on panels
of ``judges'' to determine winners was clearly bullshit. Figure skating,
flashy but bullshit, floor gymnastics, spectacular but bullshit,
synchronized swimming, waterlogged bullshit, rhythmic gymnastics,
bullshit's bullshit; any sport that could not be objectively counted,
timed, weighed, or precisely measured in SI units was deemed bullshit
and purged from the Olympic roster. So began the \emph{Zero Bullshit
Sport Olympics}.

Purging bullshit sports and sexually desegregating the remaining
provided a much need \emph{games enema}, but it didn't completely fix
the Olympics, \emph{only abolition could do that}! Yes, the \emph{Zero
Bullshit Sport Olympics} featured a \emph{reduced roster,} but many
ludicrous oddities survived: Motocross, WTF survived, bobsled, applied
ice friction physics, survived, javelin, so relevant to the
21\textsuperscript{st} century, survived, velodrome cycling, gay roller
derby, survived. And overall, the games remained a vast unnecessary,
obscenely overpriced, public-funded, drug saturated real estate orgy
overseen by that corrupt cabal of lecherous open-sored syphilitic whores
known as the IOC (International Olympic Committee).

The \emph{Zero Bullshit Sport Olympics}, while not perfect, did put an
end to whining about judges and gender. In particular, it fixed the
``transgender travesty.'' After sexual desegregation, no advantage could
be gleaned by identifying and competing as the opposite sex. A
transwoman weightlifter still faced male competitors. Oddly, in the
sexually desegregated era, the number of trans-athletes dropped to
almost zero. It's like trans-athletes had never been entirely sincere!

The \emph{Zero Bullshit Sport Olympics} also highlighted many
\emph{blatant realities} that the global garbage media had long
suppressed. For example, no female sprinter has ever qualified for the
100-meter dash. Male runners are simply too fast. Similarly, no female
weightlifter has ever competed in the super heavyweight class. Women
have fared equally poorly in the high, long, and triple jumps. Nor have
any ever thrown a winning hammer, shot put, or javelin. The sexually
desegregated Olympics hasn't been a complete rout for women. Female
fencers have held their own. Ultra-marathon winners are often women.
Mixed-sex bobsled teams, huge male pushers, and small women drivers
dominate that sport. Female sharpshooters hit their targets, as well as
men, and of course, female riders on female horses, win as often as
their male counterparts.

Looking back, the \emph{Zero Bullshit Sport Olympics} stripped away many
\emph{au courant} social delusions and returned the spotlight to simple
unfettered and unqualified human excellence. Instead of mocking Olympic
ideals, like the old Olympic obscenity, it sometimes upheld them!



%\end{document}
 