%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2022/02/04/to-do-twenty-twenty-two/}{To-do Twenty Twenty-Two}}
\addcontentsline{toc}{subsection}{To-do Twenty Twenty-Two}


\noindent\emph{Posted: 04 Feb 2022 18:38:56}
\vspace{6pt}

I'm so bad at making and keeping New Years Resolutions that I typically
put them off until February. I've always been a procrastinator and I've
always told myself that I'm going to change, but not today. Tossing
Calvinistic guilt aside procrastination isn't all bad, it gives you time
to mull over your plans before making them public. Well, my mulling is
done and my plans for 2022 are itching to embarrass me. Hang on
cowgirls, this is my agenda for 2022.

For 2022 I'm limiting my goals to one big \emph{job} and a handful of
smaller tasks. My big job: write the first draft of a short book that
uses \href{https://leanprover-community.github.io/}{LEAN} to
\emph{formally} prove some ancient geometric theorems. This is a
continuation of my LEAN studies from last year. I am fully aware that I
may be setting myself up for colossal failure as this may be utterly
beyond me! It will take a sustained effort to master an unfamiliar tool
and translate informal proofs into a strictly formal language. I'd say
it's comparable to assembling a hobby computer from component parts, and
then writing, from scratch, a new small OS in an unfamiliar assembly
language. I expect lots of hard slogging.

\emph{I don't slog well!}

This is where my smaller tasks come in. I'll use my little tasks to give
myself breaks from my big job's anticipated drudgery. Here they are:

\begin{enumerate}
\item
  Observe as many Messier and other objects as weather permits. I've
  seen 66 Messier objects. It's time to complete the list, (yeah I'm
  keeping track), and get my
  \href{https://www.rasc.ca/observing/messier-certificate}{RASC Messier
  Certificate}.
\item
  Learn more proper northern hemisphere star names. I live in a
  light-polluted suburban area. \emph{Light pollution is an abomination
  in dire need of elimination} but that's not going to happen. Light
  pollution, like plastic crap in the ocean, and global warming will be
  here long after I'm not. If you cannot eliminate an abomination work
  with it. Light polluted skies are what I call \emph{beginner skies}.
  All but the brighter stars are washed out and, to no one's surprise,
  it's the brighter, magnitude three and below stars,\footnote{The brightest objects 
have low or negative magnitude  numbers.
} that have proper
  names. Every night I go out on my little patio and attempt to call out
  all the properly named stars in view. It's a silly thing but it's
  amazing how much you see by simply looking.
\item
  Continue shooting and adding captioned images to
  \href{https://conceptcontrol.smugmug.com/}{my pictures site}. I should
  pass 5,000 online pictures this year.
\item
  Read at least ten books. This is about half the number of books I
  typically task myself with. My book reading rules are strict. I force
  myself to \emph{completely read} books before counting them. Sadly,
  this rule ignores much of my reading. Like everyone else on Earth, I
  spend hours reading my goddamn phone. This year I will be \emph{partly
  reading} many books in pursuit of my main goal; they will just have to
  go uncounted.
\item
  Blog more! I keep nagging myself to write more, maybe this year I'll
  listen to myself.
\end{enumerate}

In 2023 we'll gather here, at the old \emph{Drivel Dome,} to review my
accomplishments or lack thereof.



%\end{document}

