%\input{bmamble.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2015/07/04/turning-jod-dump-script-tricks/}{Turning JOD Dump Script Tricks}}
\addcontentsline{toc}{subsection}{Turning JOD Dump Script Tricks}


\noindent\emph{Posted: 04 Jul 2015 20:32:40}
\vspace{6pt}

\emph{Have you ever wondered how extremely prolific bloggers do it? How
is it possible to crank out thousands of blog entries per year without
creating a giant stinking pile of mediocre doo-doo? Like most deep
medium mysteries it's not very deep and there are no mysteries. The
spewers, people who post like teenage girls tweet, use two basic
strategies:}

\begin{enumerate}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \emph{\textbf{Multiple authors:} The heroic image of the lone blogger
  waging holy war against a sea of Internet idiocy is largely a myth.
  Many popular prolific blogs are the work of many hands. The editor at
  \href{https://bakerjd99.wordpress.com/}{Analyze the Data not the
  Drivel} eschews this tactic. Apparently he's an incontinent and
  argumentative prima donna that sane people steer clear of.}
\item
  \emph{\textbf{Content recycling:} In elementary school this was called
  copying. Now that we're all grown up we use terms like,
  ``excerpting'', ``abstracting'', and my favorite ``re-purposing.'' The
  basic idea is simple. Take something you've written elsewhere and
  repackage it as something new. Hey, all the cool kids are doing it!}
\end{enumerate}

\emph{The following is a slightly edited new appendix I have just added
to the JOD manual. I am working to properly publish the
\href{https://app.box.com/shared/gajfu50gc0}{JOD manual} mostly so I can
say that I've written a legitimate, albeit strange and queer, book.}

\emph{I created this post by running the} $\LaTeX$ \emph{code of the
manual appendix through the excellent utility
\href{http://pandoc.org/}{pandoc}, tweaking the resulting
\href{http://daringfireball.net/projects/markdown/syntax}{markdown}, and
then using pandoc again to generate html for this blog. pandoc is a
great ``re-purposing'' tool!}

\emph{Finally, re-purposing is not entirely cynical. The act of moving
material from one medium to another exposes problems. I found a few
editing errors while creating this post that eluded my}~$\LaTeX$
\emph{eyes. If you find more this is your chance to tell me what a moron
I am.}

%\subsection*{Turning JOD Dump Script Tricks}
\begin{center}\rule{3in}{0.4pt}\end{center}

Dump script generation is my favorite JOD feature. Dump scripts
serialize JOD dictionaries; they are mainly used to back up dictionaries
and interact with version control systems. However, dump scripts are
general J scripts and can do much more! Maintaining a stable of healthy
JOD dictionaries is easier if you can turn a few dump script
tricks.\footnote{Spicing up one's rhetoric with a double entendre like ``turning
  tricks'' may be construed as a
  \href{http://thefederalist.com/2015/03/24/microaggressions-and-trigger-warnings-meet-real-trauma/}{\emph{microaggression}}.
  The point of colored language is to memorably make a point. You are
  unlikely to forget \emph{turning dump script tricks.}
}
%\hyperref[fn1]{\textsuperscript{1}}

\begin{enumerate}
\item
  \textbf{Flattening reference paths:} Open JOD dictionaries define a
  \emph{reference path.} For example, if you open the following
  dictionaries:
  
% pipe characters | are a pain in lstlisting environments you must
% carefully escape them with a character that does appear in the verbatim text
% even when escaped with convolutions like:
%
% *\verb!!!*smugdev*\verb!!!*smug*\verb!!!*image*\verb!!!*utils*\verb!!!*
%
% The font selected by the interior \verb!!! does not match the outer font
% in all cases and things don't line up. My solution is to replace | with !
% until I can come up with a better way to display J boxes with general fonts
%
%\begin{lstlisting}[language=jdoc,escapechar=*,frame=single,framerule=0pt,label=lst:scr5077X1]

\begin{lstlisting}[language=jdoc,escapechar=*,frame=single,framerule=0pt,label=lst:scr5077X1]
   NB. open four dictionaries   
   od ;:'smugdev smug image utils'
+-+-----------------------+-------+----+-----+-----+
!1!opened (ro/ro/ro/ro) ->!smugdev!smug!image!utils!
+-+-----------------------+-------+----+-----+-----+
\end{lstlisting}

  the reference path is \texttt{/smugdev/smug/image/utils}.

  When objects are retrieved each dictionary on the path is searched in
  reference path order. If there are \emph{no compelling reasons} to
  maintain separate dictionaries you can improve JOD retrieval
  performance and simplify dictionary maintenance by flattening all or
  part of the path.

  To flatten the reference path do:

\begin{lstlisting}[language=jdoc, frame=single,framerule=0pt,label=lst:scr5077X2]
   NB. reopen the first three dictionaries on the path   
   od ;:'smugdev smug image' [ 3 od ''
+-+--------------------+-------+----+-----+
!1!opened (ro/ro/ro) ->!smugdev!smug!image!
+-+--------------------+-------+----+-----+



   NB. dump to a temporary file (df)   
   df=: {: showpass make jpath '~jodtemp/smugflat.ijs'
+-+---------------------------+-----------------------+
!1!object(s) on path dumped ->!c:/jodtemp/smugflat.ijs!
+-+---------------------------+-----------------------+

   NB. create a new flat dictionary   
   newd 'smugflat';jpath '~jodtemp/smugflat' [ 3 od ''
+-+---------------------+--------+--------------------+
!1!dictionary created ->!smugflat!c:/jodtemp/smugflat/!
+-+---------------------+--------+--------------------+

   NB. open the flat dictionary and (utils)   
   od ;:'smugflat utils'
+-+-----------------+--------+-----+
!1!opened (rw/ro) ->!smugflat!utils!
+-+-----------------+--------+-----+

   NB. reload dump script ... output not shown ...     
   0!:0 df
\end{lstlisting}

  The collapsed path \texttt{/smugflat/utils} will return the same
  objects as the longer path. It is important to understand that the
  collapsed dictionary \texttt{smugflat} does not necessarily contain
  the same objects found in the three original dictionaries
  \texttt{smugdev}, \texttt{smug} and \texttt{image}. If objects with
  the same name exist in the original dictionaries only the first one
  found will be in the collapsed dictionary.
\item
  \textbf{Merging dictionaries:} If two dictionaries \emph{contain no
  overlapping objects} it might make sense to merge them. This is easily
  achieved with dump scripts. To merge two or more dictionaries do:

\begin{lstlisting}[language=jdoc, frame=single,framerule=0pt,label=lst:scr5077X3]
   NB. open and dump first dictionary   
   od 'dict0' [ 3 od ''
+-+--------------+-----+
!1!opened (rw) ->!dict0!
+-+--------------+-----+   
   df0=: {: showpass make jpath '~jodtemp/dict0.ijs'
+-+---------------------------+--------------------+
!1!object(s) on path dumped ->!c:/jodtemp/dict0.ijs!
+-+---------------------------+--------------------+

   NB. open and dump second dictionary   
   od 'dict1' [ 3 od ''
+-+--------------+-----+
!1!opened (rw) ->!dict1!
+-+--------------+-----+   
   df1=: {: showpass make jpath '~jodtemp/dict1.ijs'
+-+---------------------------+--------------------+
!1!object(s) on path dumped ->!c:/jodtemp/dict1.ijs!
+-+---------------------------+--------------------+

   NB. create new merge dictionary   
   newd 'mergedict';jpath '~jodtemp/mergedict' [ 3 od ''
+-+---------------------+---------+---------------------+
!1!dictionary created ->!mergedict!c:/jodtemp/mergedict/!
+-+---------------------+---------+---------------------+

   NB. open merge dictionary and run dump scripts   
   od 'mergedict'
+-+--------------+---------+
!1!opened (rw) ->!mergedict!
+-+--------------+---------+

   NB. reload dump scripts ... output not shown ...     
   0!:0 df0     
   0!:0 df1
\end{lstlisting}

  Be careful when merging dictionaries. If there are common objects the
  last object loaded is the one retained in the merged dictionary.
\item
  \textbf{Updating master file parameters:} When a new parameter is
  added to \texttt{jodparms.ijs} it will not be available in existing
  dictionaries. With dump scripts you can rebuild existing dictionaries
  and update parameters. To rebuild a dictionary with new or custom
  parameters do:

\begin{lstlisting}[language=jdoc, frame=single,framerule=0pt,label=lst:scr5077X4]
   NB. save current dictionary registrations   
   (toHOST ; 1 { 5 od '') write_ajod_ jpath '~temp/jodregister.ijs'

   NB. open dictionary requiring parameter update    
   od 'dict0' [ 3 od ''
+-+--------------+-----+
!1!opened (rw) ->!dict0!
+-+--------------+-----+

   NB. dump dictionary and close   
   df=: {: showpass make jpath '~jodtemp/dict0.ijs'
+-+---------------------------+--------------------+
!1!object(s) on path dumped ->!c:/jodtemp/dict0.ijs!
+-+---------------------------+--------------------+

   3 od ''
+-+---------+-----+
!1!closed ->!dict0!
+-+---------+-----+

   NB. erase master file and JOD object id file   
   ferase jpath '~addons/general/jod/jmaster.ijf'
1   
   ferase jpath '~addons/general/jod/jod.ijn'
1

   NB. recycle JOD - this recreates (jmaster.ijf) and (jod.ijn)    
   NB. using the new dictionary parameters defined in (jodparms.ijs)      
   (jodon , jodoff) 1
1 1

   NB. re-register dictionaries   
   load jpath '~temp/jodregister.ijs'

   NB. create a new dictionary - it will have the new parameters   
   newd 'dict0new';jpath '~jodtemp/dict0new' [ 3 od ''
+-+---------------------+---------+-------------------+
!1!dictionary created ->!dict0new!c:/jodtemp/dict0new/!
+-+---------------------+---------+-------------------+

   od 'dict0new'
+-+--------------+--------+
!1!opened (rw) ->!dict0new!
+-+--------------+--------+

   NB. reload dump script ... output not shown ...   
   0!:0 df  
\end{lstlisting}

  Before executing complex dump script procedures \emph{back up your JOD
  dictionary folders} and play with dump scripts on test dictionaries.
  Dump scripts are essential JOD dictionary maintenance tools but like
  most powerful tools they must be used with care.
  
\end{enumerate}
%
%\begin{center}\rule{3in}{0.4pt}\end{center}
%
%\begin{enumerate}
%\itemsep1pt\parskip0pt\parsep0pt
%\item
%  Spicing up one's rhetoric with a double entendre like ``turning
%  tricks'' may be construed as a
%  \href{http://thefederalist.com/2015/03/24/microaggressions-and-trigger-warnings-meet-real-trauma/}{\emph{microaggression}}.
%  The point of colored language is to memorably make a point. You are
%  unlikely to forget \emph{turning dump script
%  tricks.}\hyperref[fnref1]{↩}


%\end{document}