%\input{bmamblenew.tex}

\subsection*{\href{http://analyzethedatanotthedrivel.org/2020/07/31/tweaking-jupyter-export-html-with-templates/}{Tweaking Jupyter export HTML with Templates}}
\addcontentsline{toc}{subsection}{Tweaking Jupyter export HTML with Templates}


\noindent\emph{Posted: 31 Jul 2020 22:34:35}
\vspace{6pt}
    
    
    In a
\href{https://analyzethedatanotthedrivel.org/2020/06/01/better-blogging-with-jupyter-notebooks-on-wordpress-com/}{previous
post}, I outlined some handy hacks for converting Jupyter notebooks to
WordPress.com oriented HTML. This addendum describes the use of
\href{https://www.datacamp.com/community/tutorials/jinja2-custom-export-templates-jupyter}{Jupyter
templates} and CSS edits to fine-tune exported HTML.

Jupyter exports notebooks in a variety of formats. I regularly export
notebooks as Markdown, HTML, and \(\LaTeX\). When blogging I mainly use
HTML and Markdown. Standard HTML output labels code blocks with numbered
prompts and indents text. The following
\href{https://www.rust-lang.org/}{Rust}
\href{https://en.wikipedia.org/wiki/\%22Hello,_World!\%22_program}{hello
world} program illustrates this layout.

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{2}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{// This is the main function}
\PY{k}{fn} \PY{n+nf}{main}\PY{p}{(}\PY{p}{)}\PY{+w}{ }\PY{p}{\PYZob{}}
\PY{+w}{    }\PY{c+c1}{// Statements here are executed when the compiled binary is called}

\PY{+w}{    }\PY{c+c1}{// Print text to the console}
\PY{+w}{    }\PY{n}{println}\PY{o}{!}\PY{p}{(}\PY{l+s}{\PYZdq{}}\PY{l+s}{Hello World!}\PY{l+s}{\PYZdq{}}\PY{p}{)}\PY{p}{;}
\PY{p}{\PYZcb{}}

\PY{n}{main}\PY{p}{(}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
Hello World!
    \end{Verbatim}

            \begin{tcolorbox}[breakable, size=fbox, boxrule=.5pt, pad at break*=1mm, opacityfill=0]
\prompt{Out}{outcolor}{2}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
()
\end{Verbatim}
\end{tcolorbox}
        
    For a few simple examples numbered indented blocks are fine but for
longer posts, the redundant numbering and space-wasting indents grow
tiresome. I used standard HTML output for
\href{https://analyzethedatanotthedrivel.org/2020/05/25/using-jodliterate/}{Using
jodliterate} and around prompt \texttt{In{[}7{]}:} I was irritated with
Jupyter's defaults.

Here's something you should know about me.

\textbf{\emph{I don't like being irritated!}}

In addition to indented numbered prompts the standard format suffers
from other
\href{https://www.dictionary.com/browse/boo-boo}{\emph{boo-boos}} when
run through \href{https://github.com/bennylp}{Benny's} Jupyter to
WordPress.com
\href{https://calvinandhobbes.fandom.com/wiki/Transmogrifier}{transmogrifier}.
Markdown source code like \texttt{source} code \texttt{McCodeyFace} is
set off in ugly blocks and any use of \(\LaTeX\) generates hideous
inline images with nontransparent backgrounds like:

%\begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\begin{tcolorbox}[breakable, width=9cm, center, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\[\varphi (u) = \int\_\{\Omega\} \left[
\dfrac{\|\nabla u\|^2}{2} +
\lambda\dfrac{u^2}{2} -
\dfrac{(u^+)^p}{p} \right] d\mu \]
\end{tcolorbox}

You can hack the background color of WordPress.com \(\LaTeX\) by bolting
in a HEX color code suffix. This blog's background color is
\emph{currently} set to \texttt{cfcdcd} so
\texttt{\textbackslash{}sqrt{[}n{]}\{1+x+x\^{}2+x\^{}3+\textbackslash{}dots+x\^{}n\}\&bg=cfcdcd}
yields:

\[ \sqrt[n]{1+x+x^2+x^3+\dots+x^n} \]

As far as I know, there is no global WordPress.com \(\LaTeX\) background
color setting. You are forced to hard code the suffix into every
expression and if you ever change your theme's background color you have
to do it all over again.

\textbf{\emph{Remember that bit about how I don't like being
irritated?}}

Hard coding is euphemistically called a
\href{https://www.codegrip.tech/productivity/everything-you-need-to-know-about-code-smells/}{``code
smell.''} In this case, it's a foul stench. This isn't Jupyter's fault.
Jupyter sensibly uses \href{https://www.mathjax.org/}{MathJaX} to render
mathematics with proper scaled outline fonts, but MathJax is an external
JavaScript library and WordPress.com does not allow cheap peons like
\emph{moi} to drag in alien JavaScript libraries.

\begin{quote}
Side note to WordPress.com. Make an exception to your no JavaScript rule
for MathJax. MathJax is a well established standard library and you're
being pigheaded by not allowing it.
\end{quote}

Some of these problems can be fixed with CSS tweaks, Jupyter templates,
and \texttt{nb2wp} edits.

    
    \hypertarget{tweaking-jupyter-export-formats}{%
\paragraph{Tweaking Jupyter export
formats}\label{tweaking-jupyter-export-formats}}

You can adjust Jupyter export formats with templates. Templates modify
how \href{https://nbconvert.readthedocs.io/en/latest/}{nbconvert}
transforms notebook JSON \texttt{.ipynb} files into HTML, Markdown, and
other formats. Here's a good basic
\href{https://nbconvert.readthedocs.io/en/latest/customizing.html}{introduction
to Jupyter templates}.

Jupyter templates are versatile and powerful but with ``\emph{great
formatting power comes extreme annoyance.}'' I don't want to learn yet
another programming language to tweak my fricking blog! Fortunately,
it's not necessary to get deep in the
\href{https://jinja.palletsprojects.com/en/2.11.x/}{jinja} weeds to
remove a few block labels. The following template \texttt{tpl} file
meets my meager needs.

\hypertarget{a-brain-dead-jupyter-template-blankfull.tpl}{%
\paragraph{A brain dead Jupyter template:
blankfull.tpl}\label{a-brain-dead-jupyter-template-blankfull.tpl}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{\{}\OperatorTok{%}\NormalTok{ extends }\StringTok{'full.tpl'}\OperatorTok{%}\NormalTok{\}}

\CommentTok{## change the appearance of execution count}
\NormalTok{\{}\OperatorTok{%}\NormalTok{ block in_prompt }\OperatorTok{%}\NormalTok{\}}
\OperatorTok{&}\NormalTok{nbsp}\OperatorTok{;&}\NormalTok{nbsp}\OperatorTok{;&}\NormalTok{nbsp}\OperatorTok{;&}\NormalTok{nbsp}\OperatorTok{;}
\NormalTok{\{}\OperatorTok{%}\NormalTok{ endblock in_prompt }\OperatorTok{%}\NormalTok{\}}

\NormalTok{\{}\OperatorTok{%}\NormalTok{ block prompt }\OperatorTok{%}\NormalTok{\}}
\NormalTok{\{}\OperatorTok{%}\NormalTok{ endblock prompt }\OperatorTok{%}\NormalTok{\}}

\NormalTok{\{}\OperatorTok{%}\NormalTok{ block output_area_prompt }\OperatorTok{%}\NormalTok{\}}
\OperatorTok{&}\NormalTok{nbsp}\OperatorTok{;&}\NormalTok{nbsp}\OperatorTok{;&}\NormalTok{nbsp}\OperatorTok{;&}\NormalTok{nbsp}\OperatorTok{;}
\NormalTok{\{}\OperatorTok{%}\NormalTok{ endblock output_area_prompt }\OperatorTok{%}\NormalTok{\}}

\NormalTok{\{}\OperatorTok{%}\NormalTok{ block output_area }\OperatorTok{%}\NormalTok{\}}
\NormalTok{\{}\OperatorTok{%}\NormalTok{ endblock output_area }\OperatorTok{%}\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

Save the preceding as UTF-8 text with extension \texttt{tpl} in
Jupyter's \texttt{nbconvert} share directory. The location of this
directory will vary for different systems. On this Windows 10 machine it
can be found here:

\begin{verbatim}
C:\Anaconda\share\jupyter\nbconvert\templates\html
\end{verbatim}

Refer to \texttt{nbconvert} documentation to determine where to save
\texttt{tpl} files on your system.

Stashing a custom template in the proper location removes block prompts
and indentation but it doesn't fix CSS issues. The
\href{https://github.com/bennylp/nb2wp/blob/master/style.css}{CSS style
file} distributed with \texttt{nb2wp} needs a few lines changed to
prevent \texttt{MarkdownText} from getting a white background. The
values after the line numbers on the left are the settings you need to
give \texttt{CodeyMcCodeFace} text \texttt{FRAGMENTS} transparent
backgrounds.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{ 1077}\InformationTok{:}\NormalTok{   background-color}\InformationTok{:}\NormalTok{ transparent;  background-color}\InformationTok{:} \PreprocessorTok{#fff}\NormalTok{;}
\NormalTok{ 1529}\InformationTok{:}\NormalTok{   background-color}\InformationTok{:}\NormalTok{ transparent;  background-color}\InformationTok{:} \PreprocessorTok{#f9f2f4}\NormalTok{;}
\NormalTok{10126}\InformationTok{:}\NormalTok{   background-color}\InformationTok{:}\NormalTok{ transparent;  background-color}\InformationTok{:} \PreprocessorTok{#fff}\NormalTok{;}
\end{Highlighting}
\end{Shaded}

Finally, to control annoying \(\LaTeX\) color backgrounds add another
argument \texttt{bg\_color\_hex=\textquotesingle{}\textquotesingle{}} to
the Python function \texttt{nb2wp}.

    \hypertarget{running-nb2wp-with-adjustments}{%
\paragraph{Running nb2wp with
adjustments}\label{running-nb2wp-with-adjustments}}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
%\prompt{In}{incolor}{1}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k+kn}{import} \PY{n+nn}{os}
\PY{k+kn}{import} \PY{n+nn}{sys}

\PY{c+c1}{\PYZsh{} append nb2* script directory to system path}
\PY{n}{sys}\PY{o}{.}\PY{n}{path}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{l+s+sa}{r}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{C:}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{temp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{nb2wp}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}

\PY{k+kn}{import} \PY{n+nn}{nb2wput} \PY{k}{as} \PY{n+nn}{nbu}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
%\prompt{In}{incolor}{2}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} set notebook files \PYZhy{} the source for this blog post}
\PY{n}{nb\PYZus{}file\PYZus{}0} \PY{o}{=} \PY{l+s+sa}{r}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{C:}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{temp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{nb2wp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{TweakingJupyterExportTemplates0.ipynb}\PY{l+s+s1}{\PYZsq{}}
\PY{n}{nb\PYZus{}file\PYZus{}1} \PY{o}{=} \PY{l+s+sa}{r}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{C:}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{temp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{nb2wp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{TweakingJupyterExportTemplates1.ipynb}\PY{l+s+s1}{\PYZsq{}}
\end{Verbatim}
\end{tcolorbox}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
%\prompt{In}{incolor}{3}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} convert notebook with (nb2wp) using}
\PY{c+c1}{\PYZsh{} defaults for unspecified arguments}
\PY{n}{nbu}\PY{o}{.}\PY{n}{nb2wp}\PY{p}{(}\PY{n}{nb\PYZus{}file\PYZus{}0}\PY{p}{,} \PY{n}{out\PYZus{}dir}\PY{o}{=}\PY{l+s+sa}{r}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{C:}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{temp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{nb2wp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{tmp}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}
    \PY{n}{css\PYZus{}files}\PY{o}{=}\PY{p}{[}\PY{l+s+sa}{r}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{C:}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{temp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{nb2wp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{style.css}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{save\PYZus{}css}\PY{o}{=}\PY{k+kc}{True}\PY{p}{,} 
    \PY{n}{remove\PYZus{}attrs}\PY{o}{=}\PY{k+kc}{True}\PY{p}{,} \PY{n}{template}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{full}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{latex}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{wp}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,}
    \PY{n}{img\PYZus{}dir}\PY{o}{=}\PY{l+s+sa}{r}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{C:}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{temp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{nb2wp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{tmp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{img}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{footer}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
Using template: full
Using CSS files ['C:\textbackslash{}\textbackslash{}temp\textbackslash{}\textbackslash{}nb2wp\textbackslash{}\textbackslash{}style.css']
Saving CSS to C:\textbackslash{}temp\textbackslash{}nb2wp\textbackslash{}tmp\textbackslash{}style.css
C:\textbackslash{}temp\textbackslash{}nb2wp\textbackslash{}tmp\textbackslash{}TweakingJupyterExportTemplates0.html: 23132 bytes written in
7.650s
    \end{Verbatim}

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
%\prompt{In}{incolor}{4}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} convert notebook using tweaked CSS and custom template}
\PY{n}{nbu}\PY{o}{.}\PY{n}{nb2wp}\PY{p}{(}\PY{n}{nb\PYZus{}file\PYZus{}1}\PY{p}{,} \PY{n}{out\PYZus{}dir}\PY{o}{=}\PY{l+s+sa}{r}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{C:}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{temp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{nb2wp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{tmp}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}
    \PY{n}{css\PYZus{}files}\PY{o}{=}\PY{p}{[}\PY{l+s+sa}{r}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{C:}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{temp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{nb2wp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{my\PYZus{}nb2wp\PYZus{}style.css}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{,} \PY{n}{save\PYZus{}css}\PY{o}{=}\PY{k+kc}{True}\PY{p}{,} 
    \PY{n}{remove\PYZus{}attrs}\PY{o}{=}\PY{k+kc}{True}\PY{p}{,} \PY{n}{template}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{blankfull}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{latex}\PY{o}{=}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{wp}\PY{l+s+s2}{\PYZdq{}}\PY{p}{,} \PY{n}{bg\PYZus{}color\PYZus{}hex}\PY{o}{=}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{cfcdcd}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,}
    \PY{n}{img\PYZus{}dir}\PY{o}{=}\PY{l+s+sa}{r}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{C:}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{temp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{nb2wp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{tmp}\PY{l+s+s1}{\PYZbs{}}\PY{l+s+s1}{img}\PY{l+s+s1}{\PYZsq{}}\PY{p}{,} \PY{n}{footer}\PY{o}{=}\PY{k+kc}{False}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

    \begin{Verbatim}[commandchars=\\\{\}]
Using template: blankfull
Using CSS files ['C:\textbackslash{}\textbackslash{}temp\textbackslash{}\textbackslash{}nb2wp\textbackslash{}\textbackslash{}my\_nb2wp\_style.css']
Saving CSS to C:\textbackslash{}temp\textbackslash{}nb2wp\textbackslash{}tmp\textbackslash{}style.css
C:\textbackslash{}temp\textbackslash{}nb2wp\textbackslash{}tmp\textbackslash{}TweakingJupyterExportTemplates1.html: 57127 bytes written in
12.055s
    \end{Verbatim}



    % Add a bibliography block to the postdoc
    
    
    
%\end{document}
