%\input{bmamble.tex}

\subsection*{\href{https://analyzethedatanotthedrivel.org/2017/03/25/what-is-required-hybrid-books/}{What is Required: Hybrid Books}}
\addcontentsline{toc}{subsection}{What is Required: Hybrid Books}


\noindent\emph{Posted: 25 Mar 2017 17:15:25}
\vspace{6pt}

It's time for another product suggestion. Last year I threw out the need
for
\href{https://analyzethedatanotthedrivel.org/2015/09/07/what-is-required-print-captions-on-the-back-of-photographs/}{caption
printing on the back of photographs}. It's an obvious thing to do but
only a few vendors \emph{partly support} backside caption printing.
Eventually, the masses will notice this glaring deficiency, grab their
pitchforks, and demand backside captions. We're not a very smart species
but we can learn; especially if we're motivated by fear. Today's
suggestion is little more esoteric and lacks the ``aha-ness'' of
backside captions.

\medskip
\textbf{The world needs a way to combine the virtues of Books and
eBooks.}
\medskip

If you read at all I don't need to convince you that books are nearly
perfect. The near perfection of the printed book was brilliantly
highlighted in Isaac Asimov's famous 1973 essay \emph{The Ancient and
the Ultimate}.
\href{https://www.jstor.org/stable/40009789?seq=1\#page_scan_tab_contents}{Asimov's
essay} is not readily available on-line and that's too damn bad because
he completely nailed it. \emph{The Ancient and the Ultimate} should be
required reading in English classes worldwide; it's that good!

Plain old printed books are nearly perfect but nearly perfect is not
perfect! eBooks do three things better than printed books.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  \textbf{Duplication}: It's easy to copy
  eBooks.\footnote{This only applies to non-DRM'ed eBooks.
  \href{https://en.wikipedia.org/wiki/Digital_rights_management}{DRM}'ed
  eBooks are broken. They should be avoided at all costs and their
  publishers should be tarred and feathered and stuffed head first into
  septic tanks.}\ %\protect\hyperlink{fn1}{\textsuperscript{1}}
\item
  \textbf{Portability}: You can carry entire eBook libraries around on
  your phone.
\item
  \textbf{Multimedia}: eBooks can easily embed sound recordings and
  video.
\end{enumerate}

\noindent Printed books reign supreme when it comes to:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
%\tightlist
\item
  \textbf{Durability}: There are printed books that are hundreds of
  years old that are still \emph{human-readable}. Binary formats and
  media are infuriatingly unstable. I've
  \href{https://analyzethedatanotthedrivel.org/2010/12/06/soon-we-will-all-be-software-archeologists/}{complained
  about this in the past} and I will continue bitching until the
  long-term binary storage problem is solved.
\item
  \textbf{Privacy and Security}: eBook readers, cell phones, tablets,
  and laptops can be hacked. Plain old printed books do not spy on you
  or mutate while you're reading them. They also don't bombard you with
  hard to ignore advertisements.
\item
  \textbf{Aesthetics and Beauty}: Great printed books are extremely
  valuable works of art. It's going to be a long time before eBooks
  command such respect.
\end{enumerate}

Given that eBooks have a few virtues that printed books do not the
obvious question is, ``Can we combine the two and form a more perfect
book?'' Of course, the answer is yes but, like I warned you with
backside captions, don't hold your breath!

A proper Hybrid Book, or \emph{hyBook}, will look, smell, and taste like
a printed book. It will have all the glorious heft of a thick well-bound
tome but embedded within it's covers will be a machine readable version
of the book. Ideally, the embedded digital version would be something
like an
\href{https://en.wikipedia.org/wiki/Radio-frequency_identification}{RFID}
capable of storing a few gigabytes of data for at least two centuries
without bit rot.\footnote{Currently, (March 2017), there is no cost-effective \emph{durable and
passive} technology that can store a digital image of a book within
its covers for two centuries.}\ %\protect\hyperlink{fn2}{\textsuperscript{2}} 
  To maintain
a high level of privacy and security the digital version must be
completely off-line, passive, battery-free, immutable, and hashed with
the hash prominently printed on a number of pages of the printed
version. Such a hyBook would combine the virtues of the printed and
digital worlds.

hyBooks, like their conventional printed cousins, would be durable and
\emph{human-readable} over long periods. This sharply contrasts with
eBooks. \emph{eBooks, with their lamentable DRM policies, geographic
restrictions, user monitoring, oligopolistic pricing, and built in
obsolescence are essentially self-burning books.} You cannot depend on
eBook longevity because you don't control them; they can be conveniently
\href{https://en.wikipedia.org/wiki/Memory_hole}{memory-holed} without
warning. With hyBooks you are in control.

Finally, hyBooks mitigate the most important limitation of printed
works: duplication difficulty. As we move into an increasing DRM'ed and
censored future with every aggrieved party screaming for limitations on
free speech it will become more important to preserve,
duplicate, and distribute offensive, blasphemous, pornographic, and
opprobrious \emph{wrongthink}! With well-distributed and hidden hyBooks
functioning as highly redundant off-line backups it will be extremely
difficult for authorities to suppress ideas. Whenever some
\emph{twad}\footnote{\textbf{Tw}it \textbf{a}sshole and \textbf{d}olt: pejorative invention
 is one of my many specialties.}\ %\protect\hyperlink{fn3}{\textsuperscript{3}}
  forces the content of a
hyBook off-line it will pop up again somewhere else. To memory-holing
censors everywhere hyBooks will be like floating turds; one flush will
never suffice. Is there any better recommendation than that?

%
%\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
%
%\begin{enumerate}
%\item
%  \hypertarget{fn1}{}
%
%  This only applies to non-DRM'ed eBooks.
%  \href{https://en.wikipedia.org/wiki/Digital_rights_management}{DRM}'ed
%  eBooks are broken. They should be avoided at all costs and their
%  publishers should be tarred and feathered and stuffed head first into
%  septic tanks.\protect\hyperlink{fnref1}{↩}
%\item
%  \hypertarget{fn2}{}
%
%  Currently, (March 2017), there is no cost-effective \emph{durable and
%  passive} technology that can store a digital image of a book within
%  its covers for two centuries.\protect\hyperlink{fnref2}{↩}
%\item
%  \hypertarget{fn3}{}
%
%  Twit asshole and dolt: pejorative invention is one of my many
%  specialties.\protect\hyperlink{fnref3}{↩}
%\end{enumerate}



%\end{document}