%\input{bmamble.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2010/01/28/why-code-when-you-can-steal/}{Why Code when you can Steal}}
\addcontentsline{toc}{subsection}{Why Code when you can Steal}


\noindent\emph{Posted: 28 Jan 2010 15:33:30}
\vspace{6pt}

I am learning C\#.

Two years ago I swore a blood oath not to learn anymore programming
languages. It's been obvious for decades that you seldom find any
\emph{new and important ideas} in programming languages. What you
typically find are old ideas renamed and wrapped in a new syntax.
Virtually all
\href{http://www.cse.lehigh.edu/~gtan/historyOfFP/historyOfFP.html}{key
concepts} in programming are
\href{http://www.exforsys.com/tutorials/oops/the-history-of-object-oriented-programming.html}{over
twenty years} old and
\href{http://mathworld.wolfram.com/TuringMachine.html}{many are far
older.} My disgust with new languages started with a single word:
\href{http://c2.com/cgi/wiki?WhatIsRefactoring}{refactoring!}

When I met refactoring it seduced me with its sleek geeky'ness. What
could this wonderful word mean and what thrilling concept did it clothe?
Well it basically means cleaning up your abhorrent code so that you can
make some freaking sense of it! All competent programmers, dating back
to \href{http://www.sdsc.edu/ScienceWomen/lovelace.html}{Ada Lovelace}
(1815-1852), have been refactoring all their goddamn coding lives.
\emph{Refactoring is geek marketing: the same old shit in a glistening
new package.}

C\# is as free of new concepts as I expected but the language has its
strengths. C\# has managed to inherit most of its predecessors gifts
without introducing untested features. C\#'s designers restrained
themselves and it shows. The language is clean, easy to learn, and
integrates elegantly with .Net libraries.

This is all good but what makes it better is that you can steal tons of
C\# code. Google and Bing are my accomplices. When I want to find out
what a
\href{http://msdn.microsoft.com/en-us/library/system.data.dataset.aspx}{DataSet}
does I just pop a query and dredge up nuggets like:
\href{http://rhondatipton.net/2008/01/12/creating-a-data-set-from-scratch-in-c/}{Creating
A Data Set From Scratch in C\#.} In the old days you had to read dense
language documents like the
\href{http://www.jsoftware.com/help/dictionary/title.htm}{J Dictionary}
and think for yourself.

Thinking for yourself is so 20\textsuperscript{th} century; why code when you can steal!


%\end{document}
