%\input{bmamble.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2010/04/12/wordpress-to-latex-hack/}{WordPress to \LaTeX\ Hack}}
\addcontentsline{toc}{subsection}{WordPress to \LaTeX\ Hack}


\noindent\emph{Posted: 12 Apr 2010 16:48:58}
\vspace{6pt}

I have stumbled on another coding nuisance. Last weekend I spent a few
moments exploring ways to export and print this blog in a nice typeset
fashion. I first tried
\href{http://www.blurb.com/?ce=google\_brand\_blurb\&gclid=CPWP3fHHgaECFQhinAodnw-Twg}{Blurb's}
book making software. It has a nice feature that automatically downloads
blog posts and formats them as ready to print books. Sounds great ehh?
Download your precious blog rants, press a few buttons, generate a slick
PDF, upload it to a site like \href{http://www.lulu.com/}{Lulu} and then
wait a few days for your blog to appear in hardcover. As usual the devil
is in the details.

Blurb's book making software makes a mess of:

\begin{enumerate}
\item
  Any \LaTeX\ inclusions. All \LaTeX\ code is echoed
  verbatim as ASCII. I suppose we should be grateful that it's not
  deleted.
\item
  Source code listings are mangled beyond repair. Your elegantly
  formatted code comes out worse than HEX dumps.
\item
  Embedded images are improperly placed. When it comes to blogs
  restricting image inclusions to \emph{simple center of the page
  layouts} pays big dividends. Wrapping text around images may
  \emph{look ok on your blog} but RSS software like Google Reader will
  wreck it. Apparently simple center of the page layouts is too much for
  Blurb. The default layout stuffs square thumbnails in the margins:
  \emph{arghhhh\ldots{}\ldots{}}
\item
  Web Links are inserted as verbatim footnotes at the end of each
  posting. The link footnotes often sprawl onto extra pages that have
  only one or two lines. I can see why book publishers might not care
  about efficient page allocation (\$\$\$) but I certainly do.
\end{enumerate}
After hitting all these shortcomings on my first test I abandoned Blurb
and started searching for ways to export WordPress blogs as
\LaTeX. There are a number of useful tools for converting
\LaTeX\ to WordPress. Some of these tools are used by
\href{http://mathworld.wolfram.com/FieldsMedal.html}{Fields Medal}
winners: see \href{http://terrytao.wordpress.com/}{Terence Tao's blog}.
Unfortunately going the other way does not appear to be well supported.
Damn!

After failing to come up with an acceptable WordPress to \LaTeX\
freebie I downloaded this blog in WordPress's XML export format and took
a look. To my surprise WordPress XML is what I call \emph{good XML.} Good
XML is designed to be read and understood by human beings! This
contrasts with \emph{bad XML.} Bad XML is essentially a binary format
that some idiot decided should be rendered as XML. Bad XML is useful
when you want to slow down computers.

Converting WordPress XML to \LaTeX\ looks simple enough to make a
nice C\# coding exercise. When I have hacked up a converter that panders
to my idiosyncratic tastes I will post the source code.



%\end{document}