%\input{bmamble.tex}

\subsection*{\href{https://bakerjd99.wordpress.com/2014/06/07/your-bitcoins-are-now-welcome/}{Your Bitcoins are Now Welcome!}}
\addcontentsline{toc}{subsection}{Your Bitcoins are Now Welcome!}


\noindent\emph{Posted: 07 Jun 2014 21:06:28}
\vspace{6pt}

Recently \href{https://coinbase.com/}{Coinbase} introduced payment
pages. \href{https://coinbase.com/bakerjd99}{Here's my page}. Payment
pages simplify the process of paying with Bitcoins. In the last six
months more and more businesses have started accepting Bitcoins. Once
people get~cryptocurrencies they inevitably start questioning the
legitimacy of national currencies. This is all good. National currencies
are part of the past. It's embarrassing~to trade \emph{debased
presidents} or \emph{unnecessary~queens} for goods.

I now pay online fees with Bitcoins when I can. I am doing this for
three reasons.

\begin{enumerate}
\item
  \textbf{Bitcoin payments are orders of magnitude more secure than
  credit cards, PayPal or other online payment methods.} When you pay
  with Bitcoins you don't spread personal information around. Bitcoin is
  a nightmare for identity thieves.
\item
  \textbf{I want to encourage the widespread adoption of Bitcoin as a
  payment technology.} The entire parasitic financial class must be
  reformed or destroyed. A good way to kill something is to cut off its
  air supply. When you use credit cards a big~cut goes
  to banks. Why enrich what you hate? Bitcoin, and its brethren, will
  help suffocate traditional banks and their despicable government
  cronies.
\item
  \textbf{The era of government backed legal tender is drawing to an
  end.} Money is way to important to allow governments to control it.
  Abominations like the Federal Reserve are as obsolete and morally
  repugnant as slavery.
\end{enumerate}

To help bring about the glorious day when shitheads in government no
longer \emph{create money out of thin fucking nothing} and give it to their
bum buddies I am encouraging all of you to start using~cryptocurrencies.
\href{https://coinbase.com/bakerjd99}{You can start by
tipping \emph{moi}!}



%\end{document}